\documentclass[leqno,12pt]{amsart} %
% \documentclass[leqno]{amsart}
% AMS packages:
\usepackage{amscd}
%\usepackage{tikz}
%\usepackage{tikz-cd}
%\usepackage{booktabs}
\usepackage[T1]{fontenc}
% Author's extra math macros and changes to existing macros:
\usepackage{blaom}
\usepackage{hyperref}
% to increase height of rows in tables:
\renewcommand{\arraystretch}{1.2}

% for each new GitHub version, edit the dates in the next line and in the BibTex just
% below "\begin{document}". Tag a new version as "2026.11" etc,
\newcommand\disclaimer{{\tiny\sffamily ---~Work in progress. November 2026 version~---}}
%
\usepackage{rotating}

% DRAFTING OPTIONS
\iftrue % make true for drafts
  \usepackage[twoside=false,top=15mm,bottom=30mm,right=50mm,left=15mm]{geometry}
  \usepackage[right]{showlabels}
  \renewcommand{\showlabelfont}{\footnotesize\color{cyan}}
  \renewcommand{\showlabelsetlabel}[1]
  {\begin{turn}{20}\showlabelfont #1\end{turn}}
  \newcommand\refreshpage{\newpage}
%  \showlabels{cite}
\fi
\iffalse % make false for drafts
  \newcommand\refreshpage{}
  \usepackage[margin=35mm]{geometry}
\fi
% Uncomment the following two lines to display reference labels:
% Macros just for this paper:
\newcommand{\interior}{\lrcorner}
\newcommand{\equivalent}[1]{{\overset{#1}{\,\sim\,}}}
\newcommand{\varcheck}[1]{{#1^\wedge}}
\newcommand{\model}{\automorphism({TM},A)}
\newcommand{\leftpartial}[1]{\xleftarrow{\partial^{#1}}}
\newcommand{\rightpartial}[1]{\xrightarrow{\partial^{#1}}}
% \renewcommand{\contentsname}{\vspace{-\baselineskip}}
%
\begin{document}

\noindent%
These notes are a work in progress. Please cite this version like this:
\vspace{\baselineskip}

{\ttfamily
\noindent%
@unpublished\{\\
\mbox{~~~}BlaomParabolicNotes,\\
\mbox{~~~}author=\{Anthony D. Blaom\},\\
\mbox{~~~}title=\{\{Filtered Lie algebroids and parabolic geometry\}\},\\
\mbox{~~~}note=\{In preparation\},\\
\mbox{~~~}year=\{\{2026\}\},\\
\mbox{~~~}month=\{\{November\}\},\\
\mbox{~~~}url=\{https://github.com/ablaom/FilteredAlgebroids/blob/2026.11/blaom.pdf\},\\
\}
}
\newpage

\bibliographystyle{plain}
%
\vspace{\baselineskip}
\title%
[\disclaimer]%
{Filtered Lie algebroids\\ and parabolic geometry}
\author{Anthony D.~Blaom}
\address{E-mail: {\tt anthony.blaom@gmail.com}}%
% \keywords{Lie algebroid, Cartan algebroid, equivalence, geometric
% structure, Cartan connection, deformation, pseudogroup,
% prolongation}%
% \subjclass{Primary
% 53C15, % General geometric structures on manifolds
% 58H15% Deformations of structure
% ; Secondary 53B15, % Other connections
% 53C07, % Special connections and metrics on vector bundles
% 53C05, % Connections, general theory
% 58H05, % Pseudogroups and differential groupoids
% 53A55, % Differential invariants (local theory), geometric objects
% 53A30, % Conformal differential geometry
% 58A15% Exterior differential systems (Cartan theory)
% }
\thispagestyle{empty}
\begin{center}
  \disclaimer
  \vspace{\baselineskip}
\end{center}
\begin{abstract}
  This work is an exposition of parabolic geometry with some notable novelties. The
  filtered Lie algebroids introduced here generalize the filtered manifolds in Tohru
  Morimoto's study of (what are now called) parabolic geometries, a rich class of finite type
  structures generalizing conformal and projective structures. We propose a new
  abstraction of parabolic geometry based on Lie groupoids whose associated Lie algebroids
  are filtered. In particular, we present a new prolongation procedure to recover the
  abstraction from its ``underlying geometric structure'', using semi-direct products in
  the Lie groupoid category. The construction is predicated on the observation that Lie
  groupoids with filtered Lie algebroids admit a semi-direct product structure whenever
  they also admit a Weyl gauge, an ``oid'' version of lifts of grading elements of a Lie
  algebra. Our approach allows for the parallel treatment of infinitesimal and global
  aspects, the simpler infinitesimal apsect typically informing global constructions.

  A parabolic geometry is essentially a deformed generalized flag manifold $G/H$ where, in
  previous formulations, $G$ is assumed to have a semisimple Lie algebra. Here we show, with
  little additional effort, that it is suffices to suppose the Lie algebra is reductive.
\end{abstract}
\maketitle
%\vspace{-1\baselineskip}\tableofcontents

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Body starts
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% here %%%%%%%%%%%%%%%%%%%%%%%
\refreshpage
\section{Introduction}
Parabolic geometry is an abstract framework that unifies a rich collection of finite-type
geometric structures, such as conformal, projective, contact projective,
CR,\footnote{non-degenerate and partially integrable \cite[p.414]{Cap_Slovak_09}.} almost
Grassmannian, almost quaternionic, conformal Lorenzian, almost Lagrangean, Lagrangean
contact, Lie contact structures, finite-type $n$-plane fields, and many others
\cite[Chapter 4]{Cap_Slovak_09}. In the first place, it provides for a unified treatment
and interpretation of ``curvature'', and among its important applications is the
systematic derivation of invariant differential operators
\cite{Cap_etal_01,Calderbank_Diemer_01,Cap_Soucek_07,Cap_Soucek_12}.

These notes are an outgrowth of our attempts to tame some of the theory's more technical
aspects by approaching it from new points of view.  We prove the basic existence,
normalization and uniqueness theorems, culminating in a solution to the equivalence
problem for a large subclass of parabolic geometries. This treatment is suitable for
non-experts well versed in Lie groupoids and Lie algebroids, but we also flag points of
difference and novelty for parabolic geometry experts. Our results on firmly filtered Lie
groupoids/algebroids and our version of prolongation are new.

\subsection{The main new ideas}\label{firstfirst}
According to Cartan's generalization of Klein's Elrangen program \cite{Sharpe_97},
geometric structures of finite type are viewed as ``symmetries deformed by curvature''. In
the contemporary formulation, the object deformed is the principal bundle associated with
some homogeneous space, $G/H$, as we describe further in \ref{contemporary} below.  The
parabolic geometries arise when $H \subset G$ is a parabolic subgroup and $G$ is
semisimple (or even reductive, as we will show here). Such homogeneous spaces, known as
generalized flag manifolds, are in rich supply. The alternative approach promoted here is
to consider deformations of action groupoids, which in the transitive case have the form
$G \times M$, $M \cong G/H$. In this approach, the key concept of {\em prolongation}
manifests, we believe, more a more natural way.

For the sake of concreteness, consider the conformal sphere $S^n$, a generalized flag
manifold with action groupoid $\SO(n + 1, n) \times S^n$. Now, differentiating conformal
automorphisms, i.e., elements of $\SO(n + 1, n)$, we obtain a Lie groupoid
morphism $$\SO(n + 1, n) \times S^n \rightarrow \CO[TS^n]$$ onto the frame groupoid
$\CO[TS^n]$, consisting of conformal isomorphisms between tangent spaces. The kernel of
this morphism is a Lie group bundle with commutative, simply-connected fibres. By
arguments recalled later, it has a natural identification with $T^*\!S^n$. A fundamental
observation, not immediately obvious, but following from the general results presented
here, is that the morphism above splits (non-canonically), delivering an identification of
$\SO(n + 1, n) \times S^n$ with the Lie groupoid semi-direct product
$\CO[TS^n] \times T^*\!S^n$. This is significant, for in the ``curved'' case of an
arbitrary conformal manifold $M$, where the action groupoid is gone, {\em a proxy for the
  action groupoid persists}, namely the semi-direct product $\CO[TM] \times T^*\!M$. This
is what we call the {\df prolongation} of the conformal structure.

In the flat case, we can give the kernel $T^*\!S^n$ the interpretation of all $2$-jets of
conformal automorphisms vanishing to first order. Relevant arguments can be found in
\cite{Abadoglu_etal_08}. This connects prolongation to the usual idea of introducing
derivatives as new variables. The reader is warned, however, that prolongations appearing
in the Cartan geometry literature, and prolongations in the naive sense of PDE's,
generally diverge in the {\em curved} case, and this is true here also.

To make the prolongation $\CO[TS^n] \times T^*\!S^n$ a formal parabolic geometry, it
suffices to equip its Lie algebroid $A$ with a suitable $\so(n + 1, n)$-bundle structure,
and this structure, which we call {\df model data}, is identifiable with the trivial
$\so(n + 1, n)$-bundle structure of the action algebroid $\so(n + 1, n) \times S^n\cong A$
in the flat case. As we will see in \ref{conformal}, the Lie algebroid $A$ of
$\CO[TM] \times T^*\!M $ has a natural filtration
$A = A^{-1} \supset A^0 \supset A^1=T^*\!M$, and while the Lie algebra bundle structure on
the associated graded $\graded(A)$ determined by the bracket on $A$ is {\em not} modeled
on $\so(n + 1, n)$, there is a second, related Lie algebra bundle structure that {\em
  is}. Model data on $A$ is constructed by finding a canonical way to lift this latter Lie
algebra bundle structure from $\graded(A)$ to $A$. A ``canonical'' lift is one that
normalizes the corresponding {\df model curvature}, whose direct analogue in the standard
approach is known simply as ``curvature''.

More generally, prolongation allows us to recover, in the typical case, an abstract
parabolic geometry from it's ``underlying geometric structure'', such as the conformal
structure above, which manifests in the standard theory as an ``infinitesimal flag
structure'' \cite[Definition 3.1.6, p.~248]{Cap_Slovak_09}. For reasons explained at the
end of \ref{levi_}, we prefer to call the Lie groupoid version of these objects {\df Levi
structures}.

Our version of prolongation is anticipated by the observation that natural candidates for
parabolic geometries are certain Lie groupoids that {\em always} admit a semi-direct
product structure. Indeed, splittings like the one above exist for a large class of Lie
groupoids, even intransitive ones, provided they admit what we call a Weyl gauge. As
a special case, we can show that the action groupoid of any generalized flag manifold is a
semi-direct product (\ref{all}, Corollary C), a fact that does not seem to have
been noticed before. Weyl gauges are discussed further in \ref{intro_prolong} below.

Various algebraic prolongation techniques leading to the solution of the equivalence
problem for parabolic geometries, which have a long and complicated history \cite[Appendix
A]{Cap_Slovak_09}, were discovered by Tanaka \cite{Tanaka_79}, Morimoto \cite{Morimoto_93}
and Cap and Schichl \cite{Cap_Schichl_00}. The conceptually simple approach sketched above
is probably the most noteworthy novelty of the present exposition. The idea, in the
present context, of replacing principal bundles with Lie groupoids, dates back to
Ehresmann's 1959 paper \cite{Ehresmann_59}.\footnote{At this time the infinitesimal
  concept of a Lie algebroid had not been formalized, and this concept did not mature
  substantially until Jean Pradines' work in the late 1960's. This may explain why the
  groupoid approach did not immediately gain traction.}  Our work is strongly guided by
{\v{C}}ap and Slov{\'a}k's seminal monograph \cite{Cap_Slovak_09} and our debt to that
work necessarily extends beyond those places explicitly noted.

\subsection{The contemporary point of view}\label{contemporary}%
In the principal bundle formulation, which originates in Ehresmann's earlier 1951 paper
\cite{Ehresmann_51}, a Cartan geometry, modeled on some homogeneous space $G/H$, is
a smooth manifold $M$ and a principal $H$-bundle $P$ over $M$, equipped with: (i) A
parallelism, understood as a $V$-valued one-form $\omega$ on $P$ (the {\df connection}),
required to be suitably compatible with the principal bundle structure; and (ii) A
compatible identification of the vector space $V$ with the infinitesimalization
${\mathfrak g}$ of $G$ (the {\df model data}). Combining (i) and (ii), we can view
$\omega $ as ${\mathfrak g} $-valued one-form, which is the object commonly known as a
{\df Cartan connection}. The precise definition is recalled in
\ref{cartan_geometries_defined}.

In the case of a principal $H$-bundle $G \rightarrow G/H$, the Maurer-Cartan form $\omega$
is a Cartan connection, and in the general case there is a notion of curvature,
$d \omega - [\omega,\omega]_{\mathfrak g}$, which vanishes in the homogeneous case, by
virtue of the Maurer-Cartan equations for $G$. Since it depends on the choice of model
data (it involves the bracket on the Lie algebra ${\mathfrak g} $ of $G$) we refer to this
as the {\df model curvature}; it's significance is that $M$ is locally identifiable with
the model $G/H$ whenever the model curvature vanishes. (As explained later, an alternative
notion of curvature, which does not depend on model data, but is nevertheless an
obstruction to symmetry, will play an ancillary role in the present exposition.)

The connection and model data allow one to transfer certain structures from the model
space, such as a $G$-invariant quadratic form on ${\mathfrak g} /{\mathfrak h} $, to
structures on the underlying manifold $M$, for example a Riemannian metric, and this
latter constitutes the ``underlying geometric structure'' of the Cartan geometry. In the
parabolic case, the Lie algebra ${\mathfrak h} $ of $H$ defines a filtration of
${\mathfrak g} $ which, among other things, implies that $TM$ is non-trivially filtered in
the typical case. A simple example is CR-geometry, where this filtration is defined by the
contact structure ${\mathcal H} $, namely
$0=:T^0M \subset T^{-1}M:={\mathcal H} \subset T^{-2}M:=TM$.

Different choices of $\omega $ may lead to the same underlying geometric structure, which
leads to the first fundamental problem of the theory, how to choose $\omega $ so as to
``normalize'' the model curvature, for then $\omega$ (and its curvature, for example)
encode basic invariants of the underlying geometry. The second fundamental problem is how
to reconstruct an abstract Cartan geometry from the underlying geometric structure.  Where
this is possible one obtains a one-to-one correspondence between (isomorphism classes) of
normalized Cartan geometries and the concrete geometries of interest, solving the
``equivalence problem'' for those structures. The technical tool for making this
reconstruction is known as prolongation, because of its roots in the procedure in the
theory of PDE's of the same name.

\subsection{The new approach}
In \cite{Morimoto_93} Tohru Morimoto introduced a novel prolongation technique to prove
existence and normalization results for Cartan connections in parabolic geometry. In it he
formulates the notion of filtered manifolds, now a part of the contemporary formalism
\cite{Cap_Slovak_09}. The filtration of $TM$ for CR-geometry above is a simple
example. Morimoto also demonstrates the usefulness of separating the notions of connection
and model data, a theme of our own work cited shortly, and the present exposition, but not
emphasized more generally.

Rather than pursuing Morimito's original strategy, however, we synthesize an approach
based on a new analysis of ``firmly'' filtered Lie algebroids, a natural generalization of
Morimoto's filtered manifolds. In this recounting, Lie groupoids, whose corresponding
infinitesimalization are filtered Lie algebroids, replace the principal bundles of the
conventional approach, along the lines intimated in \ref{firstfirst}. Previous work of
ours, reviewed in Section \ref{cartan_section}, shows how to view Lie algebroids or Lie
groupoids as (possibly intransitive) ``symmetries deformed by curvature'', by equipping
them with connections {\em without} model data
\cite{Blaom_06,Blaom_12,Blaom_13,Blaom_16,Blaom_16b} (but nevertheless called Cartan
  connections). In the groupoid case, the connection is a multiplicatively closed
horizontal $n$-plane field, $D$, and in the infinitesimal case, it is a Koszul connection,
$\nabla $, suitably compatible with the Lie algebroid structure. The type of symmetry, if
it exists, is not specified {\em a priori}, and the natural definition of curvature (the
usual one for $\nabla $) does not depend on a notion of model data. Here we introduce, for
the first time in the ``oid'' context, a notion of compatible model data, and of model
curvature, in which the model {\em is} specified ahead of time, as in the standard
approach. With these basic ingredients we can imitate the standard theory, with some
further novelties discussed below,

\subsection{Weyl gauges and semi-direct products}\label{intro_prolong}
The general considerations leading to the Lie groupoid splittings alluded to in
\ref{firstfirst} can be previewed here by considering the special Lie {\em algebra} case
of our Theorem \ref{weyl}:
\begin{theorem}
  Let
  $\cdots \supset {\mathfrak a}^{-1} \supset {\mathfrak a}^0 \supset {\mathfrak a}^1
  \supset {\mathfrak a}^2 \supset \cdots$ be a filtration\footnote{See \ref{filtered} for
    precisely what we mean here.} of some finite-dimensional Lie algebra ${\mathfrak a} $,
  and assume the graded Lie algebra $\graded({\mathfrak a}^0)$, associated with
  ${\mathfrak a}^0$, admits a grading element $E$, necessarily lying in
  $\graded({\mathfrak a})_0$.  Moreover, assume that $E $ has a lift
  $\epsilon \in {\mathfrak a}^0$ such that
  \begin{equation}
    [{\mathfrak a}, \epsilon] \subset {\mathfrak a}^1.\label{invariance}
  \end{equation}
  Then ${\mathfrak a}^j\subset {\mathfrak a}$ is an ideal for all $j \ge 0$ and
  ${\mathfrak a}$ is isomorphic to the semi-direct product
  ${\mathfrak a}/{\mathfrak a}^1 \oplus_{\adjoint}\graded({\mathfrak a}^1)$, the
  isomorphism depending on the choice of $\epsilon $.
\end{theorem}
\noindent%
Recall here that an element $E$ of a graded Lie algebra
${\mathfrak g}=\oplus_j {\mathfrak g}_j $ is a {\df grading element} if $[E , X] = j X$,
whenever $X \in {\mathfrak g}_j$. Note that the theorem requires only a grading element of
$\graded({\mathfrak a}^0)$ and not $\graded({\mathfrak a})$. When the additional
``invariance'' condition \eqref{invariance} is satisfied, we call $\epsilon $ a {\df Weyl
  gauge}.

If ${\mathfrak a} $ is filtered and the condition about ideals is also satisfied,
necessary for the existence of a Weyl gauge, we say that ${\mathfrak a} $ is {\df firmly
  filtered}. This is a strong condition, but the right one for our general setting, as we
shall see already for homogeneous spaces $G/H$ and other examples in Section
\ref{introduction}. The theorem above has the following corollary:
\begin{aside}
  A filtered Lie algebra ${\mathfrak a}$ admits a Weyl gauge if and only if it is firmly
  filtered and $\graded({\mathfrak a}^0)$ admits an ${\mathfrak a}$-invariant grading
  element $E$.
\end{aside}

The above theorem does {\em not} apply to the canonical filtrations associated with the
parabolic subalgebras of a reductive (or semisimple) Lie algebra (see
\ref{canonical_filtrations_}), as these cannot be firmly filtered. The point is, rather,
that Weyl gauges have generalizations to filtered Lie algebroids and Lie groupoids (even
intransitive ones), including the action algebroids/groupoids of generalized flag
manifolds. For us, a parabolic geometry is a firmly filtered, transitive Lie groupoid,
together with suitably compatible model data (Definition \ref{parabolic_defined}). This
model data identifies each tangent space $T_mM$ (non-canonically) with a Lie algebra
quotient ${\mathfrak g}/{\mathfrak p} $, where $\mathfrak g$ is reductive and
${\mathfrak p} \subset {\mathfrak g} $ is parabolic. These assumptions on
${\mathfrak g}/{\mathfrak p} $ guarantee the existence of Weyl gauges, by a generalization
of the italicized statement above. In the above super-simplification of the general
scenario, ${\mathfrak a}/{\mathfrak a}^1$, together with its representation
$\graded({\mathfrak a}^1)$, play the role of the corresponding Levi structure.

% An immediate application of our results in the general setting (specifically, our Theorems
% \ref{weyl2} and \ref{all}) is the following:
% \begin{aside}
%   Every action groupoid ${\mathcal G} = G \times G/H$ associated with a generalized flag
%   manifold $G/H$ is a semi-direct product ${\mathcal H} \times \exp(N)$, where
%   ${\mathcal H}$ is a certain transitive Lie groupoid with reductive vertex group (the
%   reductive Levi quotient of the parabolic subgroup $H\subset G$) and $N$ a nilpotent Lie
%   algebra bundle (modeled on the nilradical of the Lie algebra of $H$).
% \end{aside}
% Our results may be viewed as a generalization of this one to the ``curved'', possibly
% intransitive case.  In the case of the conformal sphere, the result is that
% $\SO(n + 1, 1) \times S^n$ is the semi-direct product $\CO[TS^n]\times T^*\!S^n$, where
%  Conformal automorphisms are determined by their jets to second order, and we have
% the following interpretation: $\CO[TS^n]$ encodes is the zeroeth and first order parts,
% while $T^*S^n$ encodes the second order part.

The name ``Weyl gauge'' comes from the Weyl structures/connections in the standard theory
of parabolic geometry \cite{Cap_Slovak_09}, which generalize Weyl's own connections in
conformal geometry.  It may be there exists a correspondence between the new semi-direct
product description and the constructions in \cite{Cap_Slovak_09} but this is not obvious
to us. In any case, Weyl gauges ground the entire theory developed here (and make sense
before introducing any assumptions about model data, such as semisimplicity) while in
\cite{Cap_Slovak_09} prolongation is first developed without Weyl structures.  Here the
semi-direct product structure leads to perhaps the most explicit description of parabolic
geometries to date --- in fact, of all transitive filtered Cartan geometries, a mild
generalization (Theorem \ref{abstract_levi_}).

\subsection{Infinitesimal geometry} An obvious advantage of the Lie groupoid approach is a
direct relationship between global and infinitesimal representations of the geometry,
namely a natural generalization of the relationship between Lie groups and Lie
algebras. Indeed, our development generally begins at the infinitesimal level, where
constructions are easier to understand (and how we generally discovered them) and we only
globalize them later. There is even the possibility, not pursued here, of completely
reducing the global theory to the infinitesimal one, using the Lie groupoid versions of
Lie I and Lie II \cite{Crainic_Fernandes_11}, provided one is happy to ignore certain
topological distinctions between geometries blurred by restricting to the case of
source-simply-connected Lie groupoids.

In the principal bundle approach, it is conventional to view something called the the
  adjoint tractor bundle ${\mathcal A}$, as the corresponding infinitesimal object. For
example, the model curvature of a parabolic geometry is there understood as an
${\mathcal A}$-valued two-form. This seems natural because tractor bundles are associated
bundles. In the Lie groupoid point-of-view the analogue of associated bundles are Lie
groupoid representations, but there is no canonical representation of a Lie groupoid on
its Lie algebroid. Stated differently, the Atiyah Lie algebroid of a principal bundle is
not an associated bundle; it only becomes one (is identifiable with ${\mathcal A}$) {\em
  after} choosing a Cartan connection. This essential difference between the two
approaches has a related manifestation. As we recall in Section \ref{cartan_section}, a
Cartan connection $D$ on a Lie groupoid immediately infinitesimalizes to a Koszul
connection $\nabla $ on the corresponding Lie algebroid, without model data playing any
role, but it seems this connection does not appear in \cite{Cap_Slovak_09}, at least not
explicitly; rather the focus is on the so-called tractor connection on ${\mathcal A}$,
which depends on its associated bundle structure. While the tractor connection has an
analogue in the present approach, the infinitesimal Cartan connection $\nabla $ and the
adjoint tractor connection are different, except in the flat case. See
\eqrefs{tractors}{tractor1}.

\subsection{Model data}\label{role}
Important ingredients of the present approach are the ``oid'' versions of classical Cartan
connections, $D$ and $\nabla $ mentioned above. In \cite{Blaom_12} we outlined an
ambitious program for constructing such Cartan connections for general geometric
structures of finite type, without the need to prescribe a flat model {\em a priori},
using a direct PDE prolongation procedure. While some simple structures are amenable to
this approach, the program has largely been unsuccessful. In the case of parabolic
geometries, the specification of model data {\em a priori} appears to be essential: It
provides a hook into the rich structure theory of reductive and semisimple Lie algebras,
simplifying the normalization process, which seems intractable in the earlier PDE
approach.

The notion of model data in the Lie groupoid case is different from the classical notion
because it makes sense without reference to the Cartan connection $D$ (which corresponds
to the parallelism in Ehresmann's definition). Model data identifies each tangent space
$T_mM$ (non-canonically) with a Lie algebra quotient ${\mathfrak g}/{\mathfrak h}$, and if
${\mathfrak h} \subset {\mathfrak g} $ is a {\em separating} Lie subalgebra (true for all
parabolic subalgebras when ${\mathfrak g} $ is reductive) then {\em any compatible Cartan
  connection is completely determined by the model data}. So, in a sense, the model data
``is'' also the connection in such cases, but unlike the connection $D$, it is a purely
infinitesimal object! That said, given model data, the question of existence of a
compatible Cartan connection $D$, which we require, is a subtle one. The notion of a
separating Lie algebra is recalled in \ref{separating}.

% \subsection{Extensions} While not pursued here at all, the present work lays the
% foundations for the possible extension of parabolic geometry to {\em intransitive}
% geometries of finite type. Already the problem of existence of Cartan connections on
% intransitive Lie groupoids is a subtle problem, but one in which some progress is being
% made \cite{Trentinaglia_18,Trentinaglia_23}.

\subsection{Outline}
Section \ref{introduction} introduces filtered Lie algebroids and the firmly filtered
special case, and gives examples pertinent to the application to parabolic
geometry. Section \ref{cartan_geometries} generalizes the classical notion of a Cartan
geometry to the intransitive case, by formulating the notion using Lie groupoid
language. In \ref{separating} we recall the notion of separating Lie algebras, and show
that Cartan geometries with ``separating'' model data (which include parabolic geometries)
have some nice properties. Section \ref{parabolic_summary} formulates the Lie groupoid
abstraction of parabolic geometries, and their reductions, Levi structures, and states the
main theorems on existence, normalization, uniqueness, and equivalence, whose proofs are
laid out in the remaining sections.

Section \ref{semi-direct} generalizes the notion of Weyl gauges and the the semi-direct
product structure theorem stated in \ref{intro_prolong} above. Ambiguities in the choice of
gauge lead to the notion of Weyl gauge transformations, relevant to the uniqueness
theorem for parabolic geometry, but these transformations are introduced in Section
\ref{parabolic_summary} under the guise of Lie groupoid conjugations, which are more
concrete. So Section \ref{semi-direct} concludes with a proof that these amount to same
thing.

Section \ref{cartan_section}, which is logically independent of the preceding section, is
mostly a summary of our aforementioned work on Cartan connections on Lie groupoids and
algebroids, in the absence of model data. Model data in the ``oid'' context is introduced
in Section \ref{modeldata}. A crucial technical result established in Section
\ref{modeldata} is a method for constructing model data compatible with a given Cartan
connection (Proposition \ref{constructing}).

Section \ref{filtered_cartan} applies the semi-direct product theorems of Section
\ref{semi-direct} to give a characterization of transitive filtered Cartan geometries, a
certain generalization of parabolic geometries: All such geometries are obtained by
prolonging a Levi structure and making use of the following additional data: a splitting
of the underlying filtered manifold, a splitting of the anchor of the Levi structure's Lie
algebroid, and a Rho tensor, which will be familiar from the standard theory.

Section \ref{deform} introduces $\psi$-deformations, which are a natural collection
of transformations of a Lie groupoid or Lie algebroid which we can use to relate different
choices of model data, via push-forward. Unlike Weyl gauge transformations, these are
necessarily {\em not} morphisms. They are defined by objects $\psi$ which we view as
sections of the kernel of $J^1 {\mathcal G} \rightarrow {\mathcal G} $, where
$J^1 {\mathcal G} $ is the groupoid of one-jets of the underlying Lie groupoid
${\mathcal G} $ of the parabolic geometry, an interpretation that helped us to see how a
compatible Cartan connection should transform to ensure compatibility with the
$\psi$-deformed model data. This section concludes by establishing a relationship between
$\psi$-deformations and Weyl gauge transformations that we need for uniqueness results.

Section \ref{modelcurvature} derives various properties of curvature, such as invariance
under Lie algebroid automorphisms, and Bianchi's identity, and lays out the algebraic
machinery of Kostant \cite{Kostant_61} regarding the adjoint representation of a parabolic
subalgebra's reductive Levi subalgebra on the graded reductive Lie algebra that contains
it. Actually, Kostant's work applies in the semisimple case, but what we need from it
readily generalizes to reductive Lie algebras. This is the crucial algebraic
ingredient for normalizing model curvature, which can be viewed as a $2$-chain in a
related complex of vector bundles. Subsection \ref{homology} onwards is mostly a reworking
of parts of \cite[\S3.1]{Cap_Slovak_09}. The main point is Proposition \ref{curv_deform},
expressing the change in model curvature upon $\psi $-deforming the model data, in terms
of a cochain complex differential. We conclude with a brief discussion of tractor bundles,
so as to relate our Cartan connections on Lie algebroids with adjoint tractor connections.

In Section \ref{parabolic_proofs} we provide the remaining details needed to prove the
results stated in Section \ref{introduction}.

\subsection*{Audience} We assume readers are familiar with Lie groupoid/algebroid basics
--- say, what is briskly summarized in the first two lectures of
\cite{Crainic_Fernandes_11}. Other sources include
\cite{CannasdaSilva_Weinstein_99,Moerdijk_Mrcun_03,Dufour_Nguyen_05} and the book
\cite{Mackenzie_05}. In addition, parts of \cite{Blaom_16b} describing the generalization
of the adjoint action to Lie groupoids, may be helpful.

We circumvent a lot of Lie algebra structure theory, and obtain our generalizations to the
reductive case, by adopting the very nice point of view of parabolic subalgebras in
\cite{Calderbank_Noppakaew_16}. Essential parts of this description are outlined in
Appendix \ref{lie_algebra_facts}.

\subsection*{Blanket assumptions}
All manifolds are smooth, which means $C^\infty$ or real-analytic, and have connected
components sharing a common dimension. With the exception of Lie groupoids, manifolds are
Hausdorff. All manifolds are second countable. In particular, all transitive
Lie groupoids are automatically locally trivial (source maps are both surjective and
submersive) \cite[Proposition A.3]{Trentinaglia_15} and so are gauge groupoids (groupoids
defined by a principal bundle).

The kernel of the anchor of a Lie algebroid, which is variously known as the isotropy,
vertex bundle, or adjoint bundle, is here called the {\df anchor kernel}.

\subsection*{Acknowledgements} The author is indebted to Jan Slov\'ak and Andreas \v{C}ap
for clarifying several arguments in \cite{Cap_Slovak_09}. He thanks David Calderbank for
many helpful discussions, for walking the author through \cite{Calderbank_Noppakaew_16} in
detail, and for invaluable encouragement. The proof of Proposition \ref{separating_}
is largely due to Professor Calderbank.

\refreshpage
\section{Filtered Lie algebroids}\label{introduction}
In this section we introduce filtered Lie algebroids and the important special case of
{\em firmly} filtered Lie algebroids, and give examples which include observations
foreshadowing aspects of parabolic geometry to be presented in Section
\ref{parabolic_summary}.

\subsection{Definition}\label{filtered}
Here a filtration $$\cdots A^{-1}\supset A^0 \supset A^1 \supset A^2 \supset\cdots $$ of
some vector space or vector bundle $A$ will always be understood to satisfy
$\cap_j A^j =0$ and $\cup_j A^j = A$. All filtrations are descending.  If $A$ is a vector
bundle, then we call the filtration a {\df Lie algebroid filtration} if $A$ is a Lie
algebroid and:

\begin{conditions}
\item[\bf F1.] The induced filtration
  $\cdots \Gamma(A^{-1})\supset \Gamma(A^0) \supset \Gamma(A^1) \supset \Gamma(A^2)
  \supset\cdots $ of the section space $\Gamma(A)$ is a filtration of Lie algebras,
  meaning $[X, Y] \in \Gamma(A^{j+k})$ for $X \in \Gamma(A^j)$ and $Y \in \Gamma(A^k)$.
\item[\bf F2.] The kernel of the anchor contains $A^0$.\label{fa2}
\end{conditions}

A filtered Lie algebroid $A$ is {\df firmly filtered} if $A^0$ and the filtration of $A^0$
are invariant under the canonical representation of $A$ on its anchor kernel, i.e., if
$\Gamma(A^j) \subset \Gamma(A)$ is an ideal for all $j \ge 0$.

\begin{proposition} Let $A$ be a filtered Lie algebroid. Then:
  \begin{conditions}
  \item The associated graded vector bundle $\graded(A)$ is a bundle of graded Lie
    algebras (a smooth field of graded Lie brackets). \label{b1}
  \item If $A$ is firmly filtered, then $\graded(A)$ is, fibre-wise, the Lie algebra
    direct sum of its negative and non-negative parts, i.e., $\oplus_{i<0}\graded(A)_i$
    and $\oplus_{i\ge 0}\graded(A)_i$ are fibre-wise ideals of $\graded(A)$. \label{rt2}
    \end{conditions}
\end{proposition}
%
\begin{remark}
  If the fibres of $\graded(A)$ are pairwise isomorphic Lie algebras, then $\graded(A)$ is
  a bona fide Lie algebra bundle, by, e.g., \cite[Theorem 6.4.5]{Mackenzie_05}; this will
  be the case in all the examples discussed here.\footnote{If $A$ is firmly filtered,
  transitive, and {\em integrable}, then $\graded(A^0)$ must be a Lie algebra bundle,
  because the canonical representation of $A$ on $A^0$ will drop to a representation of
  $A$ on $\graded(A^0)$, and the latter integrates to a representation of the transitive
  (and so locally trivial) integrating Lie groupoid ${\mathcal G} $ having
  simply-connected source fibres.}
\end{remark}

\begin{proof}
  Let $X \in \Gamma(A^j) $ and $Y \in \Gamma(A^k)$ be given. To prove \eqref{b1}, it
  suffices to show that
  $$ [fX, Y] \equiv f[X, Y] \mod \Gamma(A^{j+k+1})$$
  for any smooth function $f$ on the base manifold. If $\#$ denotes
  the anchor, then the necessary and sufficient condition is
  that
  $$df(\#Y)X \in \Gamma(A^{j + k + 1}).$$
  If $k \ge 0$ then this is holds by F2. If instead $k \le -1 $, then $j + k + 1 \le j$,
  implying $A^j \subset A^{j + k + 1}$ and the condition is still satisfied.

  Suppose $A$ is firmly filtered. Then it is clear that $\oplus_{i<0}\graded(A)_i$ and
  $\oplus_{i\ge 0}\graded(A)_i$ are fibre-wise subalgebras of $\graded(A)$. To prove
  \eqref{rt2}, it suffices to show that sections of one of these commute with sections of
  the other. To this end, suppose $X \in \Gamma(A^k)$ and $Y \in \Gamma(A^j)$, with $k<0$
  and $j\ge 0$. Then $j + k + 1 \le j$, which implies $A^j \subset A^{j+k+1}$. Since $A$
  is firmly filtered, $\Gamma(A^j) \subset \Gamma(A)$ is an ideal, so that
  $[X, Y] \in \Gamma(A^j) \subset \Gamma(A^{j + k + 1})$. It follows that
  $[\graded_j(X), \graded_k(Y)]=0$.
\end{proof}


\begin{notation}[Bounds on degree]
  Suppose $A$ is a {\em graded} vector space or vector bundle. Then, we write $k \le A$ if
  $A_i=0$ for all $i < k$ and $A \le k$ if $A_i=0$ for all $i > k$. For example, if
  $A = A_{-2}\oplus A_{-1} \oplus A_0$, then we write $-2 \le A \le 0$. We write
  $|A| = k $ if $-k \le A \le k$ and $A_{-k} \ne 0 \ne A_k$.

  If $A$ is merely {\em filtered}, then we write $A \le k$ if $\graded(A) \le k$, etc. For
  example, for filtered $A$, we write $|A| = 1$ if
  $\graded(A) = \graded(A)_{-1} \oplus \graded(A)_0 \oplus \graded(A)_1$ with
  $\graded(A)_{\pm 1} \ne 0$.
\end{notation}

The remainder of the section is devoted to examples of filtered Lie algebroids. All but
the first class of examples are always firm.

\subsection{ Filtered Lie algebras and Lie algebra bundles} Evidently, every filtered
Lie algebra, and more generally every filtered Lie algebra bundle, is a filtered Lie
algebroid.

\subsection{ Filtered manifolds} For any Lie algebroid filtration of a tangent bundle
$TM$, we have $TM \le -1$, by Axiom F2.  These filtrations are trivially firm. A smooth
manifold $M$ whose tangent bundle is so structured is called a {\df filtered manifold}, a
notion introduced by Morimoto \cite{Morimoto_93}, and appearing prominently in
\cite{Cap_Slovak_09}.  The anchor $\# \colon A \rightarrow M$ of any {\em transitive}
filtered Lie algebroid $A$ pushes the filtration down to a filtration of $TM$. That is,
the base of any transitive filtered Lie algebroid is a filtered manifold.\footnote{One can
  drop the requirement of transitivity, but only at the expense of dropping our
  requirement $\cap_jA_j=0$ in the definition of a filtration.} \label{yt}

\subsection{Trivial filtrations}\label{trivial} Suppose $A$ is any Lie algebroid whose anchor kernel has
constant rank (e.g., is transitive). Choosing $A^0$ to be this kernel, and defining
$A^j=A$ for $j<0$ and $A^j = 0$ for $j>0$, we get a firm Lie algebroid filtration with
$-1 \le A \le 0 $ that we call the {\df trivial filtration} of $A$.

\subsection{ Filtered Klein geometries}\label{eg2}
For a more interesting class of examples, let $G$ be a Lie group with Lie algebra
${\mathfrak g}$ and $P \subset G$ a closed subgroup. Furthermore, suppose that
${\mathfrak g} $ admits a $P$-invariant filtration such that ${\mathfrak g}^0$ is the Lie
algebra of $P$. In particular, as recalled in \ref{canonical_filtrations_}, a canonical
filtration of this kind exists whenever $G/P$ is a generalized flag manifold.  Write
$M =G/P$ and let $A={\mathfrak g} \times M$ be the action algebroid. Then we obtain a
filtration of $A$, as a vector bundle, by defining
$A^j(m) = \Adjoint_g({\mathfrak g}^j)\times \{m\}$, where $g \in G$ is any element
satisfying $m = g \cdot m_0$ and $m_0$ is the left coset of $P $ containing the identity
of $G$. It is not hard to see (Proposition \ref{homogeneous}) that $A$ is a firmly
filtered Lie algebroid (irrespective of whether ${\mathfrak g}_j \subset {\mathfrak g} $
is an ideal for any $j$!).


Significantly, $\graded(A)$, which will be a graded Lie algebra bundle, is {\em not}
modeled on $\graded({\mathfrak g})$ but modeled on the ordinary direct sum of the graded
Lie algebras $\oplus_{i<0}\graded({\mathfrak g})_i$, re-equipped with {\em negative}
bracket, and $\oplus_{i\ge 0}\graded({\mathfrak g})_i$. So $\graded(A)$ has {\em two}
different, although related, Lie algebra bundle structures: the one inherited from the
filtered Lie algebroid, and a ``flat'' one inherited from ${\mathfrak g} $. On $A^0$ they
coincide.

\subsection{ Projective structures.}\label{projective} Let $A \subset J^2(TM)$ be the
abstract homogeneous PDE you solve to find the infinitesimal isometries of some projective
structure on $M$. Then $A$ is a subalgebroid mapped surjectively onto $J^1(TM)$ by the
projection $J^2(TM) \rightarrow J^1(TM)$, whose kernel intersects $A$ in the image $A^1$
of the natural injection $j \colon T^*\!M \rightarrow S^2(T^*\!M)\otimes TM$ defined by
$$j(\alpha)(V_1, V_2) = \alpha(V_1)V_2 + \alpha(V_2)V_1.$$ See \cite[\S5.9]{Blaom_12}. If we define
$A^0$ to be the anchor kernel of $A$, and $A^{-1}=A$, we get a firm Lie algebroid
filtration of $A$ with $|A|=1$. The corresponding graded Lie algebra bundle is
$$\graded(A) = TM \oplus \gl(TM) \oplus T^*\!M,$$
where $TM$ and $T^*\!M $ are commutative, $\gl(TM) \oplus T^*\!M $ is the Lie algebra
bundle semi-direct product, and $TM$ and $\gl(TM) \oplus T^*\!M $ are ideals, by
Proposition \eqrefs{filtered}{rt2}.

While not immediately obvious, $\graded(A)$ has a second, natural, {\em semisimple,} Lie
algebra bundle structure, modeled on $\speciallinear(n + 1, {\mathbb R})$,
$n= \dimension(M)$, and compatible with the grading. The bracket for this structure, which
we will denote $T$, extends the existing bracket on $\graded(A^0)=\gl(TM) \oplus T^*\!M $
with the new relations
\begin{equation}
  T(C, V) = C V, \quad
    T(V, \alpha) = j(\alpha)V, \label{projective_bracket}
\end{equation}
for sections $C$, $V$ and $\alpha $ of $\gl(TM)$, $TM$ and $T^*\!M $ respectively.
Significantly, this bracket coincides with the flat one referenced in \ref{eg2}, when $M$
is the projective sphere, viewed as a homogeneous
$\operatorname{SL}(n + 1, {\mathbb R})$-space.

The fact that the Lie algebra $\speciallinear(n + 1, {\mathbb R})$ for the full symmetry
of the homogeneous model persists in some form in the ``curved'' case is somewhat surprising but
crucial, and is shared by every concrete geometric structure underlying a parabolic
geometry.

\subsection{Conformal structures}\label{conformal}
Let $B \subset J^1(TM)$ be the abstract homogeneous PDE you solve to find the
infinitesimal isometries of a conformal structure on $M$ \cite[Section
12]{Blaom_12}.\footnote{Alternatively, we may identify $B$ with the Lie algebroid of the
  Lie groupoid of all relative conformal frames.} Then $B$ is a transitive subalgebroid
whose anchor kernel $\co(TM)\subset \gl(TM)$ consists of the infinitesimal conformal
automorphisms of tangent spaces. Now $B$ acts on $TM$ via restricted adjoint action, and
so acts on $T^*\!M $. Regarding $T^*\!M $ as a commutative Lie algebra bundle, we
construct, in the category of Lie algebroids, the semi-direct product
$A = B \oplus_{\adjoint} T^*\!M $ (what we shall come to call the {\df prolongation} of
$B$). Then, if we put $A^1 = T^*\!M $, $A^0 = \co(TM) \oplus T^*\!M$ (the anchor kernel of
$A$), and $A^{-1}=A$, then $A$ becomes a firmly filtered Lie algebroid with $|A| = 1$. The
corresponding graded Lie algebra bundle is
$$\graded(A)=TM \oplus \co(TM) \oplus T^*\!M,$$ where $\co(TM) \oplus T^*\!M $ is the
semi-direct product, and $TM$ and $\co(TM) \oplus T^*\!M $ are ideals.

Again, there is also a semisimple Lie algebra bundle structure on $\graded(A)$ compatible
with the grading, in this case modeled on $\so(n + 1, 1)$, and coinciding with the flat
one of \ref{eg2} when $M$ is the conformal sphere, viewed as a homogeneous
$\operatorname{SO}(n + 1, 1)$-space. After redefining the injection $j$ above,
\begin{equation*}
  j(\alpha)(V_1, V_2) = \alpha(V_1) V_2 + \alpha(V_2)V_1 -
  \sigma(V_1,V_2)\sigma^{-1}(\alpha),
\end{equation*}
now a map
$j \colon T^*\!M\rightarrow (S^2(T^*\!M)\otimes TM) \cap (T^*\!M \otimes \co(TM)) $, the
semisimple bracket $T$ extends the existing bracket on
$\graded(A^0)=\co(TM) \oplus T^*\!M$, with the same additional relations
\eqref{projective_bracket}.  Here $\sigma $ is any metric in the conformal class.

\vspace{\baselineskip} The semisimple Lie algebra bundles $TM \oplus \gl(TM)\oplus T^*\!M$
and $TM \oplus \co(TM)\oplus T^*\!M$ above are examples of infinitesimal Levi structures,
defined in \ref{levi_}.

\refreshpage
\section{Cartan geometries \`a la Lie groupoids}\label{cartan_geometries}
In this section we define Cartan geometries using the language of Lie groupoids,
recovering Ehresmann's principal bundle notion as a special case. Our definitions rest on:
(i) the notion of a Cartan connection on a Lie groupoid, reviewed in more detail in
Section \ref{cartan_section}; and (ii) the new notion of compatible model data on the
corresponding Lie algebroid. Mild, verifiable, sufficient conditions for the Cartan
connection to be {\em uniquely} determined by compatible model data are then established in the
transitive case (Proposition \ref{separating}). Model curvature is defined, and related
to the curvature of the Lie algebroid connection.

\subsection{Definitions}\label{preview}
Suppose that $G$ is a Lie group acting smoothly on a manifold $M$, possibly in a
non-transitive fashion.  We are interested in ``deformed'' versions of the action groupoid
${\mathcal G} := G \times M$, and its Lie algebroid $A := {\mathfrak g} \times M$, and to
that end we identify two structures: (i) The canonical horizontal $n$-plane field $D$ on
${\mathcal G} $, tangent to the foliation $G \times \{m\}$, $m \in M$ --- an example of a
Lie groupoid Cartan connection; and (ii) The trivial Lie algebra bundle structure on the
infinitesimalization $A = {\mathfrak g} \times M$ of ${\mathcal G} $ --- an example of
model data.

If ${\mathcal G} $ is arbitrary Lie groupoid, then a horizontal $n$-plane field $D$ on
${\mathcal G} $ is a {\df Cartan connection} if it is suitably compatible with the Lie
groupoid structure. It's
infinitesimalization may be regarded as a Koszul connection $\nabla $ on $A$, and will be
suitably compatible with the Lie algebroid structure, making it an {\df (infinitesimal)
  Cartan connection} on $A$. The curvature of $\nabla $ is an obstruction to
symmetry: When $\nabla $ is flat, $A$ is a (possibly twisted) action algebroid and, under
certain technical conditions, ${\mathcal G} $ is a (possibly twisted) action groupoid. For
details and variations on these results, see Section \ref{cartan_section}.

Associated with any Cartan connection $D$ is a representation $\bar D$ of ${\mathcal G} $
on $A$, extending the canonical action $\Adjoint$ of ${\mathcal G} $ on the anchor kernel
of $A$. Conversely, in the transitive case, every such extension is $\bar D$ for some
uniquely determined Cartan connection $D$ (Proposition \ref{cartan}). One may view
$\bar D$ as a kind of proxy for the adjoint representation of ${\mathcal G} $ on its Lie
algebroid (which does not generally exist, unless ${\mathcal G} $ is a Lie {\em group}).

Similarly, there is associated with any infinitesimal Cartan connection $\nabla$, a
representation $\bar\nabla $ of $A $ on itself, extending the canonical representation of
$A $ on the anchor kernel. In the transitive case, every such extension is $\bar \nabla$
for some uniquely determined Cartan connection $\nabla$ (Proposition \ref{hsd}). If
$(A, \nabla)$ is the infinitesimalization of some $({\mathcal G}, D)$ as above, then
$\bar\nabla$ is the infinitesimalization of the preceding global representation $\bar
D$. In any case, it is related to $\nabla $ by a simple formula,
\begin{equation}
  \label{horse}
  \bar\nabla_XY = \nabla_{\#Y}X +[X, Y],
\end{equation}
useful in computations. Here $\#$ denotes the anchor. One may similarly view $\bar\nabla $
as a proxy for the infinitesimal adjoint representation of $A$ on itself.

A smooth field $\tau $ of Lie brackets on a Lie algebroid $A$ is {\df model data} if
$\tau(X,Y) = [X, Y]$ whenever $X$ and $Y$ both lie in the kernel of the anchor of $A$. In
particular, if $A$ is transitive, any Lie algebra bundle structure on $A$ extending the
canonical Lie algebra bundle structure of the anchor kernel will be model data, and
without further comment, in transitive cases model data will always be assumed to be of
this type. We say that $\tau $ {\df has Lie algebra model} ${\mathfrak g} $ if every fibre
of $A$, with the Lie algebra structure defined by restricting $\tau $, is isomorphic to
${\mathfrak g} $.

An {\df infinitesimal Cartan geometry} on $M$ will be a Lie algebroid $A$ over $M$,
equipped with an infinitesimal Cartan connection $\nabla $ and model data $\tau $ that are
{\df compatible} in the sense that both these conditions hold:
\begin{conditions}
  \item[{\bf c1.}] $\tau $ is $\bar\nabla$-invariant.
  \item[{\bf c2.}] $\bar\nabla_ZX = \tau(Z, X)$ whenever $\#Z=0$, $X \in A$.
\end{conditions}
Here $\# \colon A \rightarrow TM $ denotes the anchor. A {\df Cartan geometry} will be a
Lie groupoid ${\mathcal G} $ over $M$, equipped with a Cartan connection $D$ and model
data $\tau$ on its Lie algebroid $A$ that are {\df compatible}, in the sense that
\begin{conditions}
      \item[{\bf C1.}] $\tau $ is $\bar D$-invariant,
\end{conditions}
and c2 holds, where $\nabla $ is the infinitesimalization of $D$.

Evidently, the infinitesimalization $(A, \nabla, \tau)$ of any Cartan geometry
$({\mathcal G}, D, \tau)$ is an infinitesimal Cartan geometry. Also, it is readily
verified that action groupoids are Cartan geometries and infinitesimal action algebroids
are infinitesimal Cartan geometries. We refer to these geometries as the {\df flat
  models}.

If only c1 (or C1) is known to hold, then $\tau $ is {\df weakly compatible} with $\nabla$
(resp., $D$). For emphasis, we sometimes use ``strongly compatible'' as a synonym of
``compatible''.

\subsection{Compatibility}
We now elaborate on condition c2, whose relevance is less obvious than c1 and C1. Notice
first that when a Lie algebroid $A$ is equipped with model data $\tau $ and an
infinitesimal Cartan connection $\nabla$, then $A$ acts on itself in {\em two} distinct
ways: first, we have the the Lie algebroid representation $\bar\nabla$; second we have the
representation $X \mapsto \adjoint^\tau_X = \tau(X,\,\cdot\,)$ of $A$ on itself as a
bundle of Lie algebras. Condition c2 is simply the assertion that every element of the
anchor kernel of $A$ acts the same way in both these cases. (Elements of the kernel act on
{\em elements} of $A$, not merely on sections.) As already noted, c2 holds in the flat models,
which is some justification for including it. However, also:
\begin{conditions}
\item Both C1 and c2 hold for classical Cartan geometries (Proposition
  \ref{cartan_geometries_defined}).
\item In the transitive case, we need c2 for model curvature to be a two-form on $M$
  (see \ref{model_curvature_general}).
\item For so-called {\em separating} model data, C1 already implies c2 (Proposition
  \eqrefs{separating}{nuf1}) and this will apply in many interesting examples, including
  parabolic geometries (Proposition \ref{separating_}).
\end{conditions}
This last observation notwithstanding, we have the following counterexample:
\begin{example}[Weak compatibility without strong compatibility]
  Let $M$ be a copy of ${\mathbb R} $ and $G$ the mutliplicative group $(0, \infty)$. Then
  we have the trivial, transitive Lie groupoid ${\mathcal G} := M \times G \times M$
  \cite[Example 1.1.7]{Mackenzie_05}, with Lie algebroid $A := TM \times {\mathfrak g} $,
  ${\mathfrak g} = {\mathbb R} $. If $\frac{\partial}{\partial m}$ denotes the constant
  vector field on $M$, then, by the transitivity, a Cartan connection $D$ on
  ${\mathcal G} $ is defined implicitly by
  $\bar D_{(m_2, g, m_1)}(\frac{\partial}{\partial m} (m_1), \xi) =
  (\frac{\partial}{\partial m} (m_2), \xi)$. Viewing a section of $A$ as a pair $(u, X)$
  of functions, $u \colon M \rightarrow {\mathbb R}$, and
  $X \colon M \rightarrow {\mathfrak g}$, we have
  $\bar\nabla_{(u, X)}(v, Y) = (u \frac{\partial v}{\partial m}, u\frac{\partial
    Y}{\partial m})$, and define $\bar D$-invariant model data $\tau $ by
  $\tau((u, X), (v, Y)) = (0, uY - vX)$. For any ${\mathfrak g}$-valued function $X$ on
  $M$, $(0, X)$ is a section of the anchor kernel.  But
  $\bar\nabla_{(0, X)}(u, Y) = \tau((0, X), (v, Y)) $ only if $vX = 0$, which shows
  that c2 fails.
\end{example}

\subsection{Classical Cartan geometries}\label{cartan_geometries_defined}
We next show that our Cartan geometries include classical Cartan geometries as
a special case (a fact we will not use elsewhere).

Let $G$ be a Lie group with Lie subgroup $H$ and let $\pi \colon P \rightarrow M$ be a
left principal $H$-bundle. Let $\omega $ be a ${\mathfrak g}$-valued one-form on $P$
satisfying: (i) $\omega \colon {T_mM} \rightarrow {\mathfrak g}$ is an isorphism at every
$m \in M$ ($\omega $ is a parallism); (ii) For each $X \in {\mathfrak g} $,
$\omega^{-1}(X)$ is the corresponding infinitesimal generator for the action of $H$ on
$P$; and (iii) $\omega(v \cdot h) = \Adjoint_{h^{-1}} \omega(v)$, for all $v \in TM$,
$h \in H$ ($\omega$ is $H$-equivariant). Then $\omega $ a Cartan connection in the sense
of Ehresmann \cite{Ehresmann_51}.

Take ${\mathcal G} $ to be gauge groupoid $(P \times P)/H$, which has $A = TP /H$ as
Lie algebroid. On account of transitivity, and the $H$-equivariance of $\omega$, a Cartan
connection $D$ on ${\mathcal G} $ is defined implicitly by
$\bar D_{[p_2, p_1]_H}[v_1]_H = [(\omega(p_2)^{-1}\circ\omega(p_1))(v_1)]_H$, for
$v_1 \in T_{p_1}P$ and $p_1, p_2 \in P $. Here $[\,\cdot\,]_H$ denotes equivalence
modulo $H$.\footnote{For a construction that avoids reference to $\bar D$, see
  \cite{Blaom_16b}, which already establishes a one-to-one correspondence between Cartan
  connections on transitive Lie groupoids and classical Cartan connections {\em stripped
    of model data}.}

The $H$-equivariance of $\omega $ shows that model data $\tau $ on $A$ is well-defined by
\begin{equation}
  \label{defmodel}
  \tau([u]_H, [v]_H) = \omega(p^{-1})[\omega(p)(u), \omega(p)(v)]_{\mathfrak g}; \qquad u, v \in T_p P.
\end{equation}
It follows immediately from the definition that $\tau $ is weakly compatible with $D$
(condition C1).

The following is just a basic fact about Ehresmann-Cartan connections:
\begin{lemma}
  For any $H$-invariant vector field $U$ on $P$, and vertical vector field $V $ on
  $P $, one has
  ${\mathcal L}_V(\omega(U)) = [\omega(V), \omega(U)]_{\mathfrak g}$.
\end{lemma}
\begin{proof}
  Since ${\mathcal L}_{fV}(\omega(fU)) = f {\mathcal L}_V(\omega(U))$, for any smooth
  function $f$, it suffices to suppose $V$ is an infinitesimal generator for the action of
  $H$. The result now follows easily from the $H$-equivariance of $\omega $.
\end{proof}
%
\begin{proposition}
  In the scenario just described for classical Cartan geometries, the model data $\tau $
  is compatible with $D$.
\end{proposition}

\begin{proof}[Proof of proposition]
  It remains to prove compatibility condition c2. For a section $X$ of $A = T P /H$, let
  $\hat X$ denote the corresponding $H$-invariant vector field on $P$, so that
  $[\hat X(p)]_H=X(\pi(p))$. Then we may express \eqref{defmodel} as
  $\omega(\widehat{\tau(Z, X)}) = [\omega(\hat Z), \omega(\hat X)]_{\mathfrak g}$, for
  $X, Z \in \Gamma(A)$. On the other hand, it is not too difficult to compute the
  infinitesimalization $\bar\nabla $ of $\bar D$: it is characterized by the identity
  $\omega(\widehat{\bar\nabla_ZX}) = {\mathcal L}_{\hat Z}\omega(\hat X)$. Supposing
  $Z \in \Gamma(A)$ lies in the anchor kernel, $\hat Z$ will be
  vertical, and the lemma delivers
  ${\mathcal L}_{\hat Z}(\omega(\hat X))=[\omega(\hat Z), \omega(\hat X)]_{\mathfrak
    g}$. Combining all these observations shows that
  $\omega(\widehat{\bar\nabla_ZX}) = \omega(\widehat{\tau(Z, X)})$, which establishes c2.
\end{proof}

\subsection{Separating model data}\label{separating}
We call a subalgebra ${\mathfrak h} \subset {\mathfrak g} $ {\df separating} if it is
separating for the automorphism group $\automorphism({\mathfrak g})$, which is to say,
that if any two automorphisms agree on ${\mathfrak h} $, then they must agree on all of
${\mathfrak g}$. Equivalently, the requirement is that the only automorphism restricting
to the identity on ${\mathfrak h} $ is the identity.

Similarly, we say that ${\mathfrak h} \subset {\mathfrak g} $ is {\df infinitesimally
  separating} if the only derivation vanishing on ${\mathfrak h} $ is the trivial
derivation. Any separating subalgebra is automatically infinitesimally
separating. Parabolic subalgebras of reductive Lie algebras are always separating
(Proposition \ref{separating_}).

\begin{example}[Model data for Riemannian geometry]
  Let ${\mathfrak g} $ be the semidirect product
  ${\mathfrak g} = \so(n) \times {\mathbb R}^n$. Then $\so(n) \subset {\mathfrak g} $ is
  separating.
\end{example}

Model data $\tau $ on $A$ will be {\df separating} if at every point $m \in M$, the anchor
kernel of $A$ sitting over $m$ is a separating subalgebra of $A|_m$, for the Lie bracket
defined by $\tau $.

\begin{proposition}
  Let $\tau $ be separating model data on a Lie algebroid $A$. Then:
  \begin{conditions}
  \item If $\tau$ is weakly compatible with an infinitesimal Cartan connection $\nabla$
    then it is strongly compatible. Similarly, if $D$ is a Cartan connection on a Lie
    groupoid ${\mathcal G} $ integrating $A$, then weak compatibility of $\tau$ with $D$
    implies strong compatibility. \label{nuf1}
  \item If $A$ is transitive, there can exist at most one infinitesimal or global Cartan
    connection compatible with $\tau $.\label{nuf2}
  \end{conditions}
\end{proposition}

\begin{proof}
  \eqref{nuf1}: If $A$ is integrated by a Lie groupoid ${\mathcal G} $ and $\tau$ is
  weakly compatible with $D$, then it is weakly compatible with its infinitesimalization
  $\nabla $. So to prove \eqref{nuf1}, it suffices to consider the infinitesimal case. Fix
  some $Z$ lying in the kernel ${\mathfrak h}$ of $\# \colon A|_m \rightarrow T_mM$. Then
  we may view $\bar\nabla_Z$ as a linear map $A|_m \rightarrow A|_m$. In fact, with
  respect to the bracket $\tau $, this is a Lie algebra derivation, because $\tau $ is
  $\bar\nabla $-invariant, assuming weak compatibility. But $\adjoint_Z^\tau$ is also a
  derviation of $A|_m$, and on ${\mathfrak h} $ these two derivations coincide, by
  \eqrefs{preview}{horse} and the definition of model data. Since $\tau $ is separating,
  ${\mathfrak h} \subset A|_m$ is a separating subalgebra, with respect to the bracket
  defined by $\tau $, and so infinitesimally separating. It follows that the derivations
  agree on $A|_m$, which proves compatibility condition c2, and hence strong compatbility.

  \eqref{nuf2}: Suppose that $\nabla^1$ and $\nabla^2$ are Cartan connections weakly
  compatible with model data $\tau$ on $A$, and write
  $\delta_XY = \bar\nabla^1_XY - \bar\nabla^2_XY$. For each $X \in A|_m$, $m \in M$, we
  may regard $\delta_X$ as a linear map $A|_m \rightarrow A|_m$ and, because $\tau $ is
  both $\bar\nabla^1$ and $\bar\nabla^2$-invariant (weak compatibility) it follows that
  $\delta_X$ is even a Lie algebra derivation, with respect to the bracket $\tau $. Since
  $\bar\nabla^1$ and $\bar\nabla^2$ both extend the canonical representation of $A$ on its
  anchor kernel, $\delta_X$ vanishes on ${\mathfrak h} \subset A|_m$ defined as above. By
  the same argument as before, $\bar\nabla^1$ and $\bar\nabla^2$ must coincide. In the
  transitive case, an infinitesimal Cartan connection $\nabla$ is determined uniquely by
  the corresponding representation $\bar\nabla$, so $\nabla^1 = \nabla^2$.

  Turning to the global case, suppose $ D^1$ and $D^2$ are Cartan connections weakly
  compatible with model data $\tau $ and write
  $\Delta_gY = \bar D^1_{g^{-1}} \bar D^2_g Y$. For each arrow $g \in {\mathcal G} $
  beginning at some $m \in M$, we may regard $\Delta_g$ as a vector space automorphism
  $A|_m \rightarrow A|_m$ and, because $\tau $ is both $\bar D^1$ and $\bar D^2$-invariant
  (weak compatibility) it follows that $\Delta_g$ is a Lie algebra automorphism, with
  respect to the bracket $\tau$. Since both $\bar D^1$ and $\bar D^2$ both extend the
  canonical representation of $\mathcal G$ on the anchor kernel, $\Delta_gZ = Z$ for all
  $Z$ in ${\mathfrak h} \subset A|_m$ defined as above. Since $\tau $ is separating,
  $\Delta_g$ must be the identity on $A|_m$, proving $\bar D^1 = \bar D^2$. In the
  transitive case, a Cartan connection $D$ is determined uniquely by the corresponding
  representation $\bar D$, so $D^1 = D^2$.
\end{proof}

\subsection{Model curvature}\label{model_curvature_general}
Consider an infinitesimal Cartan geometry $(A, \nabla)$, such as the
infinitesimalization of some global Cartan geometry. While the curvature of the
infinitesimal Cartan connection $\nabla$ is an obstruction to symmetry, and makes sense
without the prescription of any model data, {\df model curvature} is more amenable to
normalization, as we shall see concretely in the case of parabolic geometry.

In the general case the model curvature is a section of $\wedge^2{\mathcal D}^*\otimes A$,
where ${\mathcal D} \subset TM$ is the image of the anchor. However, for simplicity, we
only define it here in the case that $A$ is {\em transitive}: it is then the section
$\kappa$ of $\wedge^2 T^*\!M \otimes A$ defined by
\begin{equation*}
  \kappa(\#X, \#Y) = \torsion \bar\nabla (X, Y) - \tau(X, Y); \qquad X, Y \in \Gamma(A).
\end{equation*}
Here $\#$ is the anchor and
$$\torsion \bar\nabla(X, Y) = \bar\nabla_XY - \bar\nabla_XY - [X, Y] = \nabla_{\#Y} X -
\nabla_{\# X} Y + [X, Y].$$ That $\kappa $ is well defined follows from
\eqrefs{preview}{horse} and compatability condition c2.

Basic properties of curvature, such as a
transformation rule and the Bianchi identity, are established in Section
\ref{modelcurvature}; see also Theorem \ref{transform_}.

The model curvature is the Lie algebroid analogue of ``curvature'', as that term is
generally understood in the Cartan geometry literature.

\begin{proposition}
  The model curvature $\kappa $ of a transitive infinitesimal Cartan geometry
  $(A, \nabla)$ determines the curvature of $\nabla $ according to
  \begin{equation*}
    \curvature \nabla (U, V)X = (\bar\nabla_X \kappa)(U, V).
  \end{equation*}
  In particular, if $\kappa =0$, then $\curvature \nabla =0$ and
  $\torsion \bar\nabla =\tau $.
\end{proposition}
\noindent The consequences of $\curvature \nabla =0$ will be briefly reviewed in
\ref{curvature}.

According to the proposition, $\kappa $ is also an obstruction to symmetry, but of the
kind prescribed {\em a priori} by the choice of the Lie algebra model for $\tau $. As
Theorem \ref{curvature} will show, the model curvature measures the difference between a
``deformed'' Lie bracket $\torsion \bar\nabla$, defined by the Cartan connection, and a
bona fide Lie bracket, prescribed by the model data $\tau$. This nice interpretation is
obscured in the standard principal bundle approach.

\begin{proof}[Proof of proposition]
  For any Cartan connection $\nabla $ on a transitive Lie algebroid, one has the easily
  derived identity,
  \begin{equation}
    \label{solidarity}
    \curvature\nabla(\#X, \#Y)Z =  \bar\nabla_Z\torsion \bar\nabla (X, Y).
  \end{equation}
  See, for example, \cite[\S5.4]{Blaom_06}. From the definition of $\kappa $,
  \begin{equation}
    \label{poland}
    (\bar\nabla_Z\kappa)(\#X, \#Y) = (\bar\nabla_Z\torsion \bar\nabla)(X, Y) -
    (\bar\nabla_Z \tau)(X, Y).
  \end{equation}
  The stated identity follows from \eqref{solidarity}, \eqref{poland} and the
  compatability condition c1.
\end{proof}

\section{Parabolic geometries. Part I}\label{parabolic_summary}
In this section we define parabolic geometries,
certain reductions thereof, called Levi structures, and outline our main results about
them. Proofs appear after various restatements given in Section \ref{parabolic_proofs}.

\subsection{Parabolic subalgebras and parabolic filtrations}\label{canonical_filtrations_}
Following \cite{Calderbank_Noppakaew_16}, we call a Lie subalgebra
${\mathfrak p} \subset {\mathfrak g} $ {\df parabolic} if it contains the normalizer of a
maximial nil subalgebra. Facts about parabolic subalgebras stated below without proof are
detailed in Appendix \ref{lie_algebra_facts}. In this section, ${\mathfrak g} $ is always
a finite-dimensional Lie algebra over a field of characteristic zero, such as
${\mathbb R} $ or ${\mathbb C} $.

\begin{theorem}[Theorem \ref{parabolic_characterizations}] Suppose ${\mathfrak g} $ is
  reductive and fix a non-degenerate trace-form, which always exists. Then
  ${\mathfrak p} \subset {\mathfrak g} $ is parabolic if and only if its polar
  ${\mathfrak p}^\perp$, which does not depend on the choice of form, is nilpotent and
  lies in the semisimple part $[{\mathfrak g}, {\mathfrak g}]$ of ${\mathfrak g}$. In that
  case ${\mathfrak p} $ is self-normalizing, ${\mathfrak p}^\perp $ is an ideal of
  ${\mathfrak p} $, and ${\mathfrak p}/{\mathfrak p}^\perp $ is reductive.
\end{theorem}
\noindent%
See \eqref{qq4} below and Theorem \ref{parabolic_characterizations} for other
characterizations of parabolic subalgebras.
\begin{remark}
  In fact, ${\mathfrak p}^\perp$ will be the so-called nilpotent radical of
  ${\mathfrak p}$ (see \ref{nilpotency}), and ${\mathfrak p}/{\mathfrak p}^\perp$ is
  known as the {\df reductive Levi quotient} of ${\mathfrak p}$. We won't need this here,
  but it explains the name ``Levi structure'' introduced later.
\end{remark}

To connect parabolic subalgebras with filtrations and gradings, we recall a general method
for constructing Lie algebra filtrations from more primitive data. For a subalgebra
${\mathfrak n} \subset {\mathfrak g} $, the map
${\mathfrak s} \mapsto \adjoint_{\mathfrak n}({\mathfrak s}):=[{\mathfrak n}, {\mathfrak
  s}]$ on subspaces ${\mathfrak s} \subset {\mathfrak g} $ has a right-inverse,
${\mathfrak s} \mapsto \{X \in {\mathfrak g} \suchthat [{\mathfrak n}, X] \subset
{\mathfrak s}\}$. This motivates the construction in the following lemma:

\begin{lemma}[Proposition 2.4 of \cite{Calderbank_Noppakaew_16}]
  Let ${\mathfrak g} $ be an arbitrary Lie algebra and
  ${\mathfrak g}^0, {\mathfrak g}^1 \subset {\mathfrak g}$ subalgebras. Define two
  sequences of subspaces
  $$ \cdots {\mathfrak g}^{-3} \supset {\mathfrak g}^{-2} \supset {\mathfrak g}^{-1}
  \supset {\mathfrak g}^0\quad\text{and}\quad {\mathfrak g}^1 \supset {\mathfrak
    g}^2\supset {\mathfrak g}^3 \supset \cdots$$ by inductively defining
  ${\mathfrak g}^j = [{\mathfrak g}^1, {\mathfrak g}^{j-1}]$ for $j\ge 2$ and
  ${\mathfrak g}^j = \{X \in {\mathfrak g}\suchthat [{\mathfrak g}^1, X] \subset
  {\mathfrak g}^{j+1}\}$ for $j \le -1$.
  % defining
  % ${\mathfrak g}^{-j} := \adjoint^{-j}_{{\mathfrak g}^1}({\mathfrak g}^0)$ for
  % $-j \le -1$, and ${\mathfrak g}^j := \adjoint^{j-1}_{{\mathfrak g}^1}({\mathfrak g}^1)$,
  % for $j \ge 2$.
  We do not require ${\mathfrak g}^0\supset {\mathfrak g}^1$. However, if
  ${\mathfrak g}^1 \subset N_{\mathfrak g}({\mathfrak g}^0)$, then
  $[{\mathfrak g}^j, {\mathfrak g}^k] \subset {\mathfrak g}^{j+k}$ for all
  $j,k \in {\mathbb Z}$.
\end{lemma}
\noindent%
In particular, if ${\mathfrak g}^1$ is an ideal of ${\mathfrak g}^0$, then the proposition
applies and we call the sequence
$\cdots {\mathfrak g}^{-3} \supset {\mathfrak g}^{-2} \supset {\mathfrak g}^{-1} \supset
{\mathfrak g}^0\supset{\mathfrak g}^1 \supset {\mathfrak g}^2\supset {\mathfrak g}^3
\supset \cdots$ the {\df pre-filtration} associated with
$({\mathfrak g}^0, {\mathfrak g}^1)$.

\begin{proposition}[Proposition \ref{can}, Corollary \ref{can}, Proposition \ref{in_terms_of_gradings}, Proposition \ref{separating_}]
  Fix a non-degenerate trace-form on a reductive Lie algebra ${\mathfrak g}$. Then:
  \begin{conditions}
  \item\label{qq1} For any parabolic subalgebra ${\mathfrak p} \subset {\mathfrak g} $,
    the pre-filtration of ${\mathfrak g} $ associated with
    $({\mathfrak p},{\mathfrak p}^\perp) $, which is independent of the choice of form, is
    a bone fide Lie algebra filtration (it ascends to $0$ and descends to ${\mathfrak g}$)
    with $|{\mathfrak g}| = m $ for some $m\ge 0$ (see Notation \ref{filtered}). This is
    the {\df canonical filtration} associated with ${\mathfrak p}$.
  \item\label{qq1b} The associated graded $\graded({\mathfrak g})$ admits a unique grading
    element $E \in [\graded({\mathfrak g}), \graded({\mathfrak g})]$. In particular,
    ${\mathfrak g} $ and $\graded({\mathfrak g}) $ are isomorphic Lie algebras (by
    arguments recalled in \ref{splittings}).
  \item Every parabolic subalgebra of ${\mathfrak g}$ is separating and contains
    $Z({\mathfrak g})$.\label{cando}
  \item\label{qq4} A subalgebra ${\mathfrak p} $ is parabolic if and only if there exists
    a grading of ${\mathfrak g} $ such that $Z({\mathfrak g}) \subset {\mathfrak g}_0$ and
    ${\mathfrak p} = \oplus_{j\ge 0} {\mathfrak g}_j$. In that case the corresponding
    filtration, defined by ${\mathfrak g}^j:=\oplus_{i\ge j}{\mathfrak g}_i$, is the
    canonical filtration associated with ${\mathfrak p} $ if and only if ${\mathfrak g}_1$
    generates ${\mathfrak g}^1$, or equivalently, if
    ${\mathfrak g}^1 \supset {\mathfrak g}^2 \supset {\mathfrak g}^3 \supset \cdots $ is
    the lower central series of ${\mathfrak g}^1$.
  \end{conditions}
\end{proposition}
\noindent%
The condition $Z({\mathfrak g}) \subset {\mathfrak g}_0$ is necessary: Define a grading of
${\mathfrak g} =\gl({\mathbb C}, 2)$ by declaring ${\mathfrak g}$ to have, as the
non-trivial components, the one-dimensional subspaces ${\mathfrak g}_{-2}$,
${\mathfrak g}_{-1}$, ${\mathfrak g}_0$ and ${\mathfrak g}_1$, spanned respectively by
\begin{equation*}
 \begin{bmatrix} 1 & 0\\0 & 1\end{bmatrix}, \quad
 \begin{bmatrix} 0 & 0\\-1 & 0\end{bmatrix}, \quad
 \begin{bmatrix} 1 & 0\\0 & -1\end{bmatrix} \quad\text{and}\quad
 \begin{bmatrix} 0 & 1\\0 & 0\end{bmatrix}.
\end{equation*}
Then ${\mathfrak g}_0 \oplus {\mathfrak g}_1$ cannot be parabolic, because it does not
contain the centre of $\gl({\mathbb C}, 2)$, violating \eqref{cando}.  In a filtered
reductive (even semisimple) Lie algebra $\mathfrak g$, the subalgebra ${\mathfrak g}^0$
need not be parabolic: Take ${\mathfrak g}$ to be $\speciallinear(2, {\mathbb C})$,
${\mathfrak g}^{-1}={\mathfrak g} $, ${\mathfrak g}^1=0$, and ${\mathfrak g}^0$ to be the
one-dimensional subalgebra of diagonal matrices.

\begin{definition}
  An arbitrary filtration of a reductive Lie algebra ${\mathfrak g} $ will be called {\df
    parabolic} if ${\mathfrak p}:={\mathfrak g}^0$ is parabolic, and the filtration is the
  canonical filtration associated with ${\mathfrak p} $.
\end{definition}

\subsection{Filtered Lie groupoids}\label{filtered_groupoids}
We will call a Lie groupoid ${\mathcal G} $ over $M$ {\df filtered} if its associated Lie
algebroid $A$ is filtered. Now ${\mathcal G} $ acts on elements of the anchor kernel of
$A$, and so on elements of $A^0$; if $A$ is firmly filtered then this action of
$\mathcal G$, denoted $\Adjoint$, will {\em infinitesimally} preserve $A^0$ and its
filtration, but need not do so globally. However, if it does, then $\mathcal G$ is said to
be {\df firmly filtered}.

\subsection{Generalized flag manifolds}\label{parabolic_}
Suppose that $G$ is a reductive Lie group and $P \subset G$ a parabolic subgroup. By
definition, this means $P$ has a parabolic Lie algebra
${\mathfrak p} \subset {\mathfrak g} $ and that the associated canonical filtration of
${\mathfrak g} $ is $P$-invariant under $\Adjoint$ (it is automatically
${\mathfrak p} $-invariant under $\adjoint$). The quotient $M=G/P$ is known as a {\df
  generalized flag manifold}. The projective and conformal spheres are
examples. Generalized flag manifolds constitute the flat models of parabolic geometries.

The $P$-invariance of the canonical filtration leads to a firm filtering of the action
algebroid $A := {\mathfrak g} \times M$, as described in \ref{eg2}. It is easy to see that
the action groupoid ${\mathcal G} := G \times M $ is also firmly filtered.

\subsection{Parabolic geometries defined}\label{parabolic_defined}
Suppose $A$ is a filtered Lie algebroid. Then model data $\tau$ on $A$ is {\df compatible}
with the filtration if this is also a filtration with respect to $\tau$, i.e.,
$\tau(X, Y) \in A^{j+k}$ whenever, $X \in A^j$ and $Y \in A^k$ have a common base
point. An (infinitesimal) Cartan connection $D$ (resp., $\nabla)$ is {\df compatible} with
the filtration if the filtration is $\bar D$-invariant (resp., $\bar\nabla$-invariant).

A {\df parabolic geometry} is a transitive, firmly filtered, Lie groupoid ${\mathcal G} $
over some smooth manifold $M$, with associated Lie algebroid denoted $A$, and
filtration-compatible model data $\tau $ on $A$, such that:
\begin{conditions}
    \item[{\bf P1.}] The Lie algebra model for $\tau $ is reductive.\label{parabolic2}
    \item[{\bf P2.}] $A^0$ is the kernel of the anchor of $A$. \label{parabolic0}
    \item[{\bf P3.}] With respect to $\tau $, the filtration of $A$ is fibre-wise
      parabolic, in the sense of Definition
      \ref{canonical_filtrations_}. \label{parabolic1}
    \item[{\bf P4.}] There exists a Cartan connection $D$ on ${\mathcal G} $
      compatible with $\tau $.\label{parabolic4}
\end{conditions}
\noindent%
In particular, a parabolic geometry is a Cartan geometry in the sense of \ref{preview}.
\begin{proposition}%
  \mbox{}
  \begin{conditions}
  \item Assuming $M$ is connected, it suffices to check P3 holds over
    a single point $m \in M$.\label{soot1}
  \item $D$ is necessarily compatible with the filtration of $A$.\label{soot3}
  \item It suffices there exists a Cartan connection $D$ that is {\em weakly}
    compatible with $D$.\label{soot2}
  \item $D$ is unique. \label{soot4}
  \end{conditions}
\end{proposition}
\begin{proof}
  For \eqref{soot1}, see \ref{parabolic}, and for \eqref{soot3}, see Corollary A,
  subsection \ref{all}. By P1, P2, and P3, and Proposition
  \eqrefs{canonical_filtrations_}{cando}, the model data $\tau $ is separating. So
  \eqref{soot2} and \eqref{soot4} follow from Proposition \ref{separating}.
\end{proof}

An {\df infinitesimal parabolic geometry} consists of a transitive, firmly filtered Lie
algebroid $A$, and filtration-compatible model data $\tau $, satisfying the same
conditions given above, but with the Cartan connection $D$ in P4 replaced with an
infinitesimal Cartan connection $\nabla$. An analogue of the proposition holds except that
for \eqref{soot1} we need to assume $A$ is integrable. Evidently, every parabolic geometry
has a corresponding infinitesimalization.

Parabolic geometries are generalized by {\df filtered Cartan geometries}, introduced in
Section \ref{filtered_cartan}.

\subsection{Regularity}\label{regularity_}
Let $A$ be any {\em transitive} filtered Lie algebroid. In that case the anchor
$\# \colon A \rightarrow TM$ induces an isomorphism
$\oplus_{i<0}\graded(A)_i \cong \graded(TM)$, and model data $\tau $ compatible with the
filtration is said to be {\df regular} if the induced bracket on $\graded(TM)$ is minus
one times the canonical bracket (the one induced by the Jacobi-Lie bracket on vector
fields).\footnote{The minus sign is connected to the convention adopted here,
  and often in the Lie groupoid literature, that brackets on the Lie algebras of Lie groups are
  defined by {\em right}-invariant vector fields; most of the parabolic geometry literature, including \cite{Cap_Slovak_09}, adopts the opposite convention.} It is not too hard to show that the
canonical model data associated with any filtered Klein geometry, and in particular the
canonical model data associated with a generalized flag manifold, is regular (Proposition
\ref{homogeneous}).

A parabolic geometry is {\df regular} if the associated model data $\tau $ is regular.

\subsection{Reduction}\label{reduction_}
The concrete manifestations of parabolic geometries (their ``underlying geometric
structures'') are typically obtained by a applying a reduction procedure.  Let
$({\mathcal G}, \tau)$ be a parabolic geometry and $D$ the compatible Cartan connection.

\begin{proposition}[Proposition \ref{subgroups}]
  In a parabolic geometry $({\mathcal G}, \tau)$ let
  ${\mathcal G}^1 \subset {\mathcal G} $ denote the source-connected subgroupoid
  integrating $A^1$.  Then ${\mathcal G}^1 $ is a bundle of simply-connected nilpotent Lie
  groups; it is also a normal subgroupoid of ${\mathcal G}$, so that
  ${\mathcal G}/{\mathcal G}^1$ is a Lie groupoid, also transitive.
\end{proposition}

\begin{remark}
  It follows from Remark \ref{canonical_filtrations_} that that $A^0/A^1$ is fibre-wise
  reductive, so that ${\mathcal G}/{\mathcal G}^1$ has reductive vertex groups.
\end{remark}

Since we suppose ${\mathcal G} $ is firmly filtered, we have a grading-preserving
representation, $\Adjoint$, of ${\mathcal G} $ on $\graded(A^0)$.  Moreover, it is easy to
see that ${\mathcal G}^1$ acts trivially here (Proposition \eqrefs{weyl2}{xerox1}).  So
$\Adjoint$ descends to a representation of ${\mathcal H} := {\mathcal G}/{\mathcal G}^1$
on $\graded(A^0)$. This canonical representation extends to a representation of
${\mathcal H}$ on $\graded(A)$, which we denote by $R^D$, induced by the
filtration-preserving representation $\bar D$ of ${\mathcal G} $ on $A$.

The observations of the preceding paragraph carry over to the canonical, infinitesimal
representation, $\adjoint$, of $A$ on $A^0$, delivering a canonical representation of
$B := A/A^1$ on $\graded(A^0)$ and an extension $R^\nabla $ of this representation to one
of $B$ on $\graded(A)$, which are simply infinitesimalizations of the global ones:
$R^\nabla =dR^D$.

If we write $T := \graded_0(\tau)$, then $(\graded(A), T)$ is a graded Lie algebra bundle
with the same reductive Lie algebra model as $(A, \tau )$, by Proposition
\eqrefs{canonical_filtrations_}{qq1b}, which shows, moreover, that
$\graded(A^1)=\oplus_{i\ge 1}\graded(A)_i$ must be orthogonal to the parabolic
$\graded(A^0)=\oplus_{i\ge 0}\graded(A)_i$, for any non-degenerate trace-form for $T$. By
transitivity, we have $\oplus_{i\le -1}\graded(A)_i \cong \graded(TM)$, so we obtain a
representation of ${\mathcal H} $ on $\graded(TM)$. On the other hand, we can use a
non-degenerate trace-form for $T$ to identify $\graded(A^1)$ with
$(\oplus_{i\le -1}\graded(A)_i)^*\cong \graded(TM)^*\cong\graded(T^*\!M)$. Under this
identification, the representation $R^D$ of ${\mathcal H} $ on $\graded(T^*\!M)$ will be
the dual of the one on $\graded(TM)$, if we suppose that the trace-form is
$R^D$-invariant, which (with the help of transitivity) can always be arranged, on account
of the $R^D$-invariance of $T$, which follows from the $\bar D$-invariance of
$\tau$. Finally, we notice that $A^0/A^1 = B^0$, where $B^0$ is the anchor kernel of $B$.

In summary, we have
\begin{equation}
  \graded(A) \cong \graded(TM) \oplus B^0 \oplus \graded(T^*\!M),\label{soldering}
\end{equation}
supporting the reductive Lie algebra bundle structure $T$ (c.f.~Examples \ref{projective}
and \ref{conformal}) and with ${\mathcal H}$ acting on each component.

\begin{remark}
  By our preceding Remark, $B^0$ is a fibre-wise reductive Levi subalgebra of the
  parabolic $B^0 \oplus \graded(T^*\!M)$.
\end{remark}

\subsection{Levi structures}\label{levi_}
A {\df Levi structure} consists of a filtered, transitive, Lie groupoid ${\mathcal H}$,
whose Lie algebroid $B$ has anchor kernel $B^0$ and satisfies $B \le 0$ (see Notation
\ref{filtered}), together with a reductive Lie algebra bundle structure $T$ on
  \begin{equation}
    \graded(TM) \oplus B^0 \oplus \graded(T^*\!M)\label{fug_}
  \end{equation}
  and a representation $R$ of ${\mathcal H}$ on the same, such that:
  \begin{conditions}
      \item $R$ preserves the obvious grading of \eqref{fug_}.
      \item $R$ extends the canonical representation of ${\mathcal H} $ on the anchor
        $B^0$ of its infinitesimalization $B$, while its restrictions to representations
        on $\graded(TM)$ and $\graded(T^*\!M)$ are dual.
      \item $T$ is $R$-invariant. \label{tai}
      \item\label{levi3_} $T$ extends the canonical Lie algebra bundle structure on $B^0$,
        i.e., $T(C, C') = [C, C']$, while $T $ and $R$ are compatible, in the sense that
        $T(C, X) = dR_C X$ and $T(C, Z) = -(dR_C)^*Z$. Here $C, C' \in \Gamma(B^0)$,
        $X \in \Gamma(\graded(TM))$, and $Z\in \Gamma(\graded(T^*\!M))$.

      \item The grading of \eqref{fug_} is compatible with $T$, and, under
        iterations of the bracket $T$, $\graded(T^*\!M)$ is fibre-wise generated by
        $\graded(T^*\!M)_1$.\label{levi6}
      \item The natural pairing of $\graded(TM)$ and $\graded(T^*\!M)$ coincides with that
        induced by some non-degenerate $R$-invariant trace-form form for
        $T$.\label{killing_duality}
      \item\label{hust} With respect to $T$, the fibre-wise centre of \eqref{fug_} lies in
        $B^0$.
\end{conditions}
\noindent Notice that \eqref{hust} and Proposition \eqrefs{canonical_filtrations_}{qq4}
ensure that $B^0 \oplus \graded(T^*\!M) $ is fibre-wise $T$-parabolic; \eqref{levi6}
ensures that the filtration defined by the obvious grading of \eqref{fug_} is the
associated canonical filtration associated with $B^0 \oplus \graded(T^*\!M) $. (By Remark
\ref{canonical_filtrations_}, $B^0$ is a fibre-wise reductive Levi subalgebra, and in
particular, the vertex groups of ${\mathcal H} $ are necessarily reductive.)  By
Proposition \eqrefs{canonical_filtrations_}{qq1b} there will be a unique fibre-wise
grading element $E \in \Gamma(B^0)$; the uniqueness and \eqref{tai} ensure that $E$ is
${\mathcal H}$-invariant.

It is not required that $T$ restrict to the canonical Lie algebra bundle structure on
$\graded(TM)$ (here $TM$ is getting the filtration pushed down by the anchor of
$B$). However, if this restriction is the {\em negative} of the canonical one, then the
geometry is {\df regular}.

\begin{proposition}
  Let ${\mathcal {\mathcal H}}$, $T$ and $B$ assume the meanings of \ref{reduction_}, and
  let $R:= R^D$ be the grading-preserving representation of ${\mathcal H}$ on
  $\graded(TM) \oplus B^0 \oplus \graded(T^*\!M)$ described there. Then
  $({\mathcal H}, T, R)$ is a Levi structure called the {\df Levi reduction} of
  $({\mathcal G}, \tau)$.
\end{proposition}
\begin{proof}
  Our observations under \ref{reduction_} establish everything that is not obvious, with
  the exception of property \eqref{levi3_}, which follows from the strong
  compatibility of $\tau $ and $D$.
\end{proof}

If $B$ in the definition of a Levi structure is an arbitrary Lie algebroid (not
necessarily integrated by some Lie groupoid ${\mathcal H} $) and $R$ now denotes some {\em
  infinitesimal} action of $B$ on \eqref{fug_}, and we replace $dR$ in \eqref{levi3_} with
$R$, then the preceding conditions define an {\df infinitesimal Levi structure} and, as we
will see later, the immediately preceding proposition has an infinitesimal analogue. We
have already encountered simple examples of an infinitesimal Levi structures, namely for
projective and conformal geometry. It is easy to see these examples
globalize.\footnote{However, these two examples prove ultimately to be of different
  character. The uniqueness Theorem \ref{uniqueness} stated later applies in the conformal
  case but not in the projective case. This is reflected in the fact that the Levi
  structure for projective geometry is the same {\em for every choice of projective
    connection}.} For example we have:
\begin{example}[Conformal structures]
  Define $B \subset J^1 (TM) $ and $T$ as in \ref{conformal} and filter $B$ trivially (see
  \ref{trivial}). If we let ${\mathcal H} \subset J^1 (M \times M)$ denote the Lie
  groupoid of one-jets of local diffeomorphisms preserving the conformal structure to
  first order, which has $B$ as its Lie algebroid, and let ${\mathcal H} $ act on
  $\graded(TM)=TM$ by restricted adjoint action, and extend this to a grading-preserving
  action $R$ on \eqref{fug_} in the obvious way, then $({\mathcal H}, T, R) $ becomes a
  Levi structure.
\end{example}
\noindent%
In the next example the base manifold $M$ is non-trivially filtered:
\begin{example}[$n$-plane fields with growth vector $(n, n(n +1)/2)$] Consider, on a
  smooth manifold of dimension $n(n + 1)/2$, an $n$-plane field ${\mathcal D} \subset TM$
  that is maximally non-integrable. That is, at every $m \in M$, local sections of
  ${\mathcal D} $ and their iterated Jacobi-Lie brackets, generate $T_mM$. Unlike contact
  structures, such an $n$-plane field is a geometric structure of finite type, admitting a
  classical normalized Cartan connection, as Bryant already showed
  when $n=3$ \cite{bryant_79,bryant_2006}.

  The quotient $TM/{\mathcal D}$ and $\wedge^2 {\mathcal D}$ have the same rank, and, by
  the assumption of maximal non-integrability, the morphism
  $V_1\wedge V_2 \mapsto [V_1, V_2] \modulo {\mathcal D} \colon \wedge^2 {\mathcal D}
  \rightarrow TM/{\mathcal D}$ is surjective, and whence an isomorphism.  Taking
  $T^{-1}M = {\mathcal D} $ and $T^{-2}M=TM$, we make $TM$ into a filtered Lie algebroid
  with $ -2 \le TM \le -1$ and, on account of the isomorphism, have the identification
  $\graded(TM) \cong \wedge^2 {\mathcal D} \oplus {\mathcal D} $ with grading-compatible
  bracket characterized by
  \begin{equation}
  [X_1, X_2] = X_1\wedge X_2;\qquad  X_1, X_2 \in \Gamma({\mathcal D}).\label{brillig}
  \end{equation}

  To construct a Levi structure from this data, equip
  ${\mathcal D} \oplus ({\mathbb R} \times M) \oplus {\mathcal D}^*$ with a real quadratic
  form $(\,\cdot\,,\,\cdot\,)$, of signature $(n+1, n)$, by declaring ${\mathcal D} $ and
  ${\mathcal D}^*$ to be isotropic,
  ${\mathcal D} \perp ({\mathbb R} \times M) \perp {\mathcal D}^*$, $(X, Z) = X(Z)$, and
  $(f_1, f_2) = f_1f_2$; here $X$ lies in ${\mathcal D} $, $Z$ in ${\mathcal D}^*$ and
  $f_1, f_2$ are smooth real functions. Next, define a linear  vector bundle isomorphism
  $\rho$, from
  \begin{equation}
    \label{lab}
     \wedge^2 {\mathcal D} \oplus {\mathcal D} \oplus \gl({\mathcal D}) \oplus {\mathcal
      D}^* \wedge^2 {\mathcal D}^* \cong \graded(TM) \oplus \gl({\mathcal D}) \oplus \graded
      (T^*\!M)
  \end{equation}
  onto $\so({\mathcal D} \oplus ({\mathbb R} \times M) \oplus {\mathcal D}^*)$, the
  $\so(n + 1, n)$-bundle of fibre-wise isometries of $(\,\cdot\,,\,\cdot\,)$, by declaring
  \begin{align*}
     \rho(C)(Y, f, W) &= \big(CY, 0, -C^*W\big)\\
     \rho(X)(Y, f, W) &= \big(fX, -W(X), 0\big)\\
     \rho(X_1\wedge X_2)(Y, f, W) &= \big(W(X_2)X_1-W(X_1)X_1, 0, 0\big)\\
     \rho(Z)(Y, f, W) &= \big(0, Z(Y), -fZ\big)\\
     \rho(Z_1\wedge Z_2)(Y, f, W) &= \big(0, 0, Z_1(Y)Z_2-Z_2(Y)Z_1\big).
  \end{align*}
  Here $C$ is a section of $\gl({\mathcal D})$, $X, X_1, X_2, Y$ are sections of
  ${\mathcal D} $ and $Z, Z_1, Z_2, W$ are sections of ${\mathcal D}^*$.  In
   matrix notion we can write this as
  \begin{equation*}
    \rho(X_1\wedge X_2, X, C, Z, Z_1\wedge Z_2)=
    \begin{bmatrix}
      C & X & -X_1\wedge X_2\\ Z & 0 & -X^{**}\\ Z_1\wedge Z_2 & -Z^{**} & -C^*.
    \end{bmatrix},
  \end{equation*}
  where on the right, $X_1\wedge X_2$, $Z_1\wedge Z_2$, $X^{**}$ and $Z^{**}$ are
  interpreted, in the obvious way, as sections of
  $\homomorphism({\mathcal D}^*, {\mathcal D})$,
  $\homomorphism({\mathcal D}, {\mathcal D}^*)$,
  $\homomorphism({\mathcal D}^*, ({\mathbb R} \times M))$ and
  $\homomorphism(({\mathbb R} \times M), {\mathcal D}^*)$ respectively.  We equip
  \eqref{lab} with the obvious grading and make $\rho $ into a representation of
  \eqref{lab} on ${\mathcal D} \otimes ({\mathbb R} \times M) \otimes {\mathcal D}^*$ by
  introducing the grading-compatible bracket $T$ on \eqref{lab} generated by the relations
  \begin{gather*}
    T(X_1, X_2) = - X_1\wedge X_2, \qquad  T(C, X) = R_CX := CX,\\
    T(C, X_1 \wedge X_2) = R_CX_1, \wedge X_2 + X_1 \wedge R_CX_2 = R_C(X_1 \wedge X_2), \\
    T(Z_1, Z_2) = Z_1 \wedge Z_2, \qquad  T(C, Z) = R_CZ := -C^*Z,\\
    T(C, Z_1 \wedge Z_2) = R_CZ_1 \wedge Z_2 + Z_1 \wedge R_C Z_2 = R_C(Z_1 \wedge Z_2),\\
    T(X, Z) = Z \otimes X,\\
    T(X_1 \wedge X_2, Z_1 \wedge Z_2) = Z_1(X_1)Z_2 \otimes X_2 + Z_2(X_2)Z_1\otimes X_1\\ -Z_2(X_1)Z_1 \otimes X_2 - Z_1(X_2)Z_2 \otimes X_1,\\
    T(X_1 \wedge X_2, Z) = Z(X_1)X_2 - Z(X_2)X_1, \enspace
    T(Z_1 \wedge Z_2, X) = Z_2(X)Z_1 - Z_1(X)Z_2.
  \end{gather*}
  This makes \eqref{lab} into a $\so(n + 1, n)$-bundle. In passing, we note that
  $\gl({\mathcal D}) \oplus {\mathcal D}^* \oplus \wedge^2 {\mathcal D}^*$ is the
  stabilizer of the maximally isotropic subbundle
  ${\mathcal D}^* \subset {\mathcal D} \oplus ({\mathbb R} \times M) \oplus {\mathcal D}^*
  $.

  Since grading components of index $i$ and $j$ are necessarily $B_\rho$-orthogonal if
  $i + j \ne 0$ (Proposition \eqrefs{par}{ira1}) the following sufficiently describes the
  trace-form $B_\rho $
  \begin{align*}
    B_\rho(C_1, C_2) &= 2\trace(C_1C_2)\\
    B_\rho(Z, X) &= 2Z(X)\\
    B_\rho(Z_1 \wedge Z_2, X_1\wedge X_2) &= 2Z_1(X_1)Z_2(X_2) - 2Z_1(X_2)Z_2(X_1),
  \end{align*}
  as is readily computed. This shows that $B_\rho$ is non-degenerate. To satsify
  \eqref{killing_duality}, we instead adopt the trace-form $B_{\rho/\sqrt{2}}=B_\rho/2$.

  The frame groupoid ${\mathcal H} $ of ${\mathcal D} $ acts on each summand in
  \eqref{lab} in an obvious way, and hence on \eqref{lab} in a grading-preserving way ---
  we denote this representation by $R$. The filtration of $TM$ pulls back, via anchor, to
  a trivially firm filtration of the Lie algebroid $B$ of ${\mathcal H} $, with the
  additional understanding that $B^0$ is the anchor kernel, and $B^j=0 $ for positive
  $j$. The triple $({\mathcal H}, R, T)$ is now easily seen to be Levi structure. Note we
  have made choices in the definition of $\rho$ that ensure the sign in the first relation
  for $T$ is opposite to that in \eqref{brillig}, to ensure regularity.
\end{example}

Unfortunately for us, the analogue of a {\em global} Levi structure is called an
``infinitesimal flag structure'' in \cite{Cap_Slovak_09}. Moreover, from the present point
of view, ``infinitesimal flag structure'' seems a name more apt for the action algebroids
described in \ref{eg2}, specialized to the parabolic case. To avoid confusion, we
eschew the term altogether.

\subsection{Prolonging a Levi structure to a parabolic geometry}\label{existence}
Our proof of the following basic existence theorem is new:
\begin{theorem}[Theorem \ref{existence_}]
  Every Levi structure $({\mathcal H}, T, R)$ is, up to isomorphism, the reduction of some
  parabolic geometry $({\mathcal G}, \tau)$. If the Levi structure is regular, then the
  parabolic geometry can be chosen to be regular.
\end{theorem}
\noindent%
Morphisms of Levi structures are defined in \ref{functor}.

The model data $\tau $ is not uniquely defined by the Levi structure, but determined up to
choices of a suitable tensor
${\mathsf P} \in \Gamma(\graded(T^*\!M)\otimes \graded(T^*\!M))$ called the {\df Rho
  tensor}, splitting of the anchor $\# \colon B \rightarrow TM $, and splitting of the
filtration of $TM$. Here $B$ is the Lie algebroid of ${\mathcal H}$. Suitable
normalization of this data is addressed in \ref{normalization} below.

The key idea in the theorem's proof is to observe that every parabolic geometry
$({\mathcal G}, \tau)$ has a semi-direct product structure, which follows from the
guaranteed existence of Weyl gauges, a notion introduced in Section
\ref{semi-direct}. Specifically, the representation $R^D$ of ${\mathcal G}/{\mathcal G}^1$
on $\graded(T^*\!M)$, defined by the $\tau $-compatible Cartan connection $D$, integrates
to an action of ${\mathcal G}/{\mathcal G}^1$ on $\exp(\graded(T^*\!M))$, the Lie group
bundle with simply-connected nilpotent model that integrates the nilpotent Lie algebra
bundle $\graded(T^*\!M)$; and one obtains, after fixing a gauge, an isomorphism
\begin{equation*}
    {\mathcal G} \cong {\mathcal G}/{\mathcal G}^1 \times_{R^D} \exp(\graded(T^*\!M)),
\end{equation*}
where $\times_{R^D}$ indicates semi-direct product. This follows from Theorem \ref{weyl2},
given later.

To recover the underlying Lie groupoid $\mathcal G$ associated with some parabolic
geometry having $({\mathcal H}, T, R)$ as reduction, we accordingly define
${\mathcal G} = {\mathcal H} \times_R \exp(\graded(T^*\!M)) $, which we call the {\df
  prolongation} of the Levi structure. The more technical task is to reconstruct
suitable model data $\tau $ such that $\graded_0(\tau) = T$. In fact, we state and prove a
more general result, Theorem \ref{abstract_levi_}, characterizing arbitrary transitive
filtered Cartan geometries. This result includes an explicit description of $\tau $
and a compatible Cartan connection $D$, in terms of the aforementioned Rho tensor
${\mathsf P}$ and splittings.

\subsection{Normalization of curvature}\label{normalization}
As we have observed, while subject to the constraint $\graded_0(\tau) = T$, there is
considerable freedom in the choice of model data $\tau $ appearing in the existence
Theorem \ref{existence}. We want to choose $\tau $ so as to ``normalize'' the model
curvature $\kappa$.  This curvature, defined in \ref{model_curvature_general}, is a
section of $\wedge^2 T^*\!M \otimes A$. However, from the point of view of normalization,
there is a more convenient representation.  Since the filtration of $A$ is parabolic
(Axiom P3), we have $A^1 = (A^0)^\perp$, where $\perp$ is with respect to any
non-degenerate trace-form for $\tau $. The $\bar D$-invariance of $\tau $ means we can
always find a $\bar D$-invariant such trace-form, and such forms are completely determined
by their restriction to a single fibre of $A$. Fixing such a form, we use it to identify
$(A/A^0)^*$ with $A^1$. But, by transitivity, $A/A^0\cong TM $, because $A^0$ is the
anchor kernel (Axiom P2), and we conclude $T^*\!M \cong A^1$. In this way, we may view
$\kappa$ as a section of $\wedge^2 A^1 \otimes A$. This representation is ambiguous only
up to the choice of a non-degenerate trace-form on some fixed fibre $(A_{m_0}, \tau)$.

As the bracket $\tau $ makes the vector bundle $A$ into a representation of the Lie
algebra bundle $A^1$, $\wedge^2 A^1 \otimes A $ appears in a natural chain complex
\begin{equation}
  \label{chain1_} 0 \leftpartial{\tau} A \leftpartial{\tau} A^1 \otimes A
\leftpartial{\tau} \wedge^2 A^1 \otimes A \leftpartial{\tau} \cdots.
\end{equation} Over each point $m \in M$, this is the classical chain complex associated
with the representation $\adjoint^\tau$ of the Lie algebra $A^1|_m$ on $A|_m$.
Following \cite{Cap_Slovak_09},
we will refer to $\partial^\tau $ as the {\df Kostant codifferential}.
Basic facts about such complexes immediately carry
over to the case of Lie algebra bundle representations and we use such facts without
further comment. By definition (c.f.,
\cite[p.~262]{Cap_Slovak_09}),
%
\begin{multline}
  \label{form1}
  \partial^\tau(Y_0 \wedge \cdots \wedge Y_n \otimes X) =
  \sum_{i=0}^n(-1)^{i+1} Y_0 \wedge \cdots \wedge \widehat{Y_i} \wedge \cdots \wedge Y_n
  \otimes \tau(Y_i,X)\\ +\sum_{i<j}(-1)^{i+j}\tau(Y_i,Y_j) \wedge Y_0 \wedge \cdots \wedge
  \widehat{Y_i} \wedge \cdots \widehat{Y_j} \wedge \cdots \wedge Y_n \otimes X.
\end{multline}
%
For example,
$\partial^\tau(Y_0\wedge Y_1 \otimes X) = Y_0 \otimes \tau(Y_1, X) - Y_1 \otimes \tau(Y_0,
X) -\tau(Y_0, Y_1)\otimes X$. Incidentally, appealing to compatibility Axiom c2 (see
\ref{preview}), we can express $\partial^\tau $ in terms of the representation $\bar\nabla$ instead,
\begin{multline*} \partial^\tau(Y_0 \wedge \cdots \wedge Y_n \otimes X) =
\sum_{i=0}^n(-1)^{i+1} Y_0 \wedge \cdots \wedge \widehat{Y_i} \wedge \cdots \wedge Y_n
\otimes \bar\nabla_{Y_i}X\\ +\sum_{i<j}(-1)^{i+j}[Y_i,Y_j] \wedge Y_0 \wedge \cdots \wedge
\widehat{Y_i} \wedge \cdots \widehat{Y_j} \wedge \cdots \wedge Y_n \otimes X,\label{form1}
\end{multline*}
but emphasize $\partial^\tau $ is not a differential operator, only an algebraic one.

We say model data $\tau $ in a parabolic geometry is {\df normal} if
$\partial^\tau \kappa =0$.  Our proof of the following is an adaption of that of
\cite[Propositions 3.1.10, 3.1.13]{Cap_Slovak_09}:

\begin{theorem}[Theorem \ref{normalization_}]
  Let $({\mathcal G}, \tau)$ be a regular parabolic
  geometry. Then there exists {\bfseries normal}, model data $\tau'$ such that
  $({\mathcal G} , \tau')$ is a regular parabolic geometry with the same Levi reduction.
\end{theorem}

\subsection{Harmonic curvature}\label{harmonic}
In a regular parabolic geometry with normal model data $\tau $, the homology class
$\kappa_{\mathrm H} := [\kappa] \in H_2(A^1, A)$ is called the {\df harmonic
  curvature}. While it seems the harmonic curvature contains less information, it
  is nevertheless a complete obstruction to flatness, as the corollary below shows.

It is not too hard to see that the filtration of $A$ induces a filtration of
$H_k(A^1, A)$. However, according to \eqref{poker2} below, something much stronger and
useful is true:

\begin{theorem}[Proposition \ref{homology}, Proposition \ref{top_curvature}]
  Let $\kappa $ be the model curvature of a regular and normal parabolic geometry
  $({\mathcal G} , \tau)$, and let $k \ge 0$ be any integer. Then:
  \begin{conditions}
     \item In a natural representation of ${\mathcal G} $ on $H_k(A^1, A)$ defined by the
    compatible connection $D$, the subgroupoid ${\mathcal G}^1$ acts trivially, i.e.,
    $H_k(A^1, A)$ is a representation of ${\mathcal G}/{\mathcal G}^1$.\label{poker1}
  \item $H_k(A^1, A)$ admits a canonical {\bfseries grading} compatible with it's natural filtration,
    allowing harmonic curvature to be unambiguously split into grading components,
    $\kappa_{\mathrm H} = \sum_{i\ge 1}(\kappa_{\mathrm H})_i$.\label{poker2}
  \item If $\kappa $ is homogeneous of degree $l \ge 1$ and $(\kappa_{\mathrm H})_l = 0$,
    then $\kappa $ is homogeneous of degree $l + 1$.\label{poker3}
  \end{conditions}
\end{theorem}
\noindent%
One says {\df $\kappa$ is homogeneous of degree $l$} if $\kappa$ can be written as a
finite sum of terms of the form $X\wedge Y \otimes Z$ where $X$, $Y$, $Z$ lie in $A^j$,
$A^k$, $A^m$, respectively, with $j+k+m \le l$; equivalently, if we view $\kappa $ as a
section of $\wedge^2 T^*\!M \otimes A$, if $\kappa(X, Y)$ lies in $A^{j+k+l}$ whenever $X$
and $Y$ lie in $A^j$ and $A^k$ respectively. See also \cite[\S3.1.1,
p.~235]{Cap_Slovak_09}.

We obtain the following by applying \eqref{poker3} inductively:
\begin{corollary}[c.f.~Theorem 3.1.12, p.~265, \cite{Cap_Slovak_09}]
  In a normal, regular parabolic geometry, $\kappa_{\mathrm H} =0$ implies $\kappa =0$
  (and hence also $\curvature \nabla =0$).
\end{corollary}

The harmonic curvature $\kappa_{\mathrm H}$ is a section of $H_2(A^1, A)$, which is a
representation of a transitive groupoid, and can accordingly be understood as an
associated bundle; it's splitting into grading components can be understood by studying a
single fibre, which will be a representation of the (reductive) vertex group of
${\mathcal G}/{\mathcal G}^1$. More generally, each fibre of $H_j(A^1, A)$, $j \ge 0$, is
of the form $H_j({\mathfrak g}^1, {\mathfrak g})$, where ${\mathfrak g} $ is the reductive
Lie algebra model for the Lie algebra bundle structure $\tau $, which gets a canonical
filtration, because $A$ is parabolically filtered; the subalgebra ${\mathfrak g}^0$ will
be parabolic, its orthogonal (with respect to any non-degenerate trace-form) is
${\mathfrak g}^1$. Fixing a lift $\epsilon $ of the unique grading element
$E \in \graded({\mathfrak g})$, we can write ${\mathfrak g}$ as a graded Lie algebra,
${\mathfrak g}_{-k} \oplus \cdots \oplus {\mathfrak g}_k$, $k\ge 0$ (Proposition
\eqrefs{canonical_filtrations_}{qq1b}). This allows us to introduce the {\em co}homology
$H^j({\mathfrak g}_-, {\mathfrak g})$, where
${\mathfrak g}_- = {\mathfrak g}_{-k}\oplus \cdots \oplus {\mathfrak g}_{-1}$. (This
space, in turn, is the model for the bundle of cohomologies for a cochain complex
$\wedge^\bullet \graded(T^*\!M)\otimes \graded(A)$ that will enter in the proof of the
uniqueness result described next.) According to (a mild generalization) of Kostant's
version of Hodge theory in this setting \cite{Kostant_61} (see also Proposition
\ref{hodge}), there is an identification
$H_j({\mathfrak g}^1, {\mathfrak g}) \cong H^j({\mathfrak g}_-, {\mathfrak g})$, which
does not depend on the choice of $\epsilon $, and the grading of the space on the right
gives a filtration-compatible grading of the space on the left, corresponding exactly to
the grading in \eqref{poker2} (but for which we will give a direct argument).  In the
semisimple case, Kostant's theorem, restated in \cite[Theorem 3.3.5,
p.~351]{Cap_Slovak_09}, computes the cohomology $H^j({\mathfrak g}_-, {\mathfrak g})_l$,
for each $l \in {\mathbb Z} $, for complex ${\mathfrak g} $; some additional arguments
extend the result to the real case. We refer the reader to \cite{Cap_Slovak_09} for
extensive details. It seems one ought to be able to generalize these results to the
reductive case, but we have not attempted to do that here.

\subsection{Uniqueness up to Weyl gauge transformations}\label{uniqueness}
The inner automorphisms of an arbitrary Lie groupoid are those given by conjugation by
bisections. When ${\mathcal G} $ is firmly filtered, a special role is played by those
inner automorphisms generated by bisections of ${\mathcal G}^1 \subset {\mathcal G}$, the
bundle of simply-connected nilpotent Lie groups integrating the totally intransitive Lie
subalgebroid $A^1 \subset A$, where a bisection is the same thing as a section. We call
such automorphisms {\df Weyl gauge transformations}, for reasons explained in
\ref{gauge_transformations}. By Proposition \ref{reduction_}, there is, for each such
transformation, some $Z \in \Gamma(A^1)$ such that each arrow $g \in {\mathcal G} $,
beginning at some $m \in M$, is mapped to $\exp(Z(gm))g\exp(-Z(m))$. This conjugation has
derivative
$$X \mapsto e^{-\adjoint_Z}X:=X - [Z, X] + \frac{1}{2!}[Z, [Z, X]] - \cdots\enspace,$$
and morphisms of a filtered Lie algebroid $A$ of this form will be called {\df
  infinitesimal Weyl transformations}.\footnote{The minus sign enters here because of our
  convention that right-invariant vector fields define the Lie bracket on the Lie algebra
  of a Lie group.} Both global and infinitesimal Weyl gauge transformations cover the
identity of the base $M$, and $e^{-\adjoint_Z}$ is filtration-preserving, by F1. Evidently,
in a global parabolic geometry, every infinitesimal Weyl transformation is integrated by
a unique global Weyl gauge transformation.

\begin{example}
  Let $A$ be a filtered Lie algebroid with $|A| = 1$. Then the infinitesimal Weyl gauge
  transformations have the form $X \mapsto X + [Z, X]$, for some $Z \in \Gamma(A^1)$.
\end{example}

\begin{proposition}[Corollary of Proposition \ref{transform}]%
  If $({\mathcal G}, \tau)$ is a (regular) parabolic geometry, and $\tau'$ the
  push-forward of $\tau $ under a Weyl gauge transformation, then $({\mathcal G}, \tau')$
  is another (regular) parabolic geometry with the same Levi reduction.
\end{proposition}

According to the next result, normal model data is uniquely determined, up to Weyl gauge
transformations, provided a Lie cohomological condition is satisfied. Our proof of the
following is an adaption of that of \cite[Proposition 3.1.14]{Cap_Slovak_09}:

\begin{theorem}[Theorem \ref{un}] Let $({\mathcal G}, \tau)$ be a regular parabolic
  geometry and let ${\mathfrak g} $ be Lie algebra model for $\tau $, identified with a
  graded reductive Lie algebra, as detailed at the end of \ref{harmonic}. Assume
  $H^1({\mathfrak g}_-, {\mathfrak g})^1=0$.  Then if $({\mathcal G}, \tau')$ is second
  parabolic geometry with $\graded_0(\tau')=\graded_0(\tau)$, then if both $\tau $ and
  $\tau'$ are normal, then $\tau' = q_*\tau$ for some infinitesimal Weyl gauge
  transformation $q$.
\end{theorem}
\noindent%
Here
$H^1({\mathfrak g}_-, {\mathfrak g})^1=\oplus_{l \ge 1}H^1({\mathfrak g}_-, {\mathfrak
  g})_l$.

\subsection{The equivalence problem}\label{equivalence}
The parabolic geometries over $M$ form a category if we define a morphism of parabolic
geometries $({\mathcal G}, \tau)$ and $(\tilde {\mathcal G} , \tilde \tau)$ over $M$ to be
a Lie groupoid morphism $Q \colon {\mathcal G} \rightarrow \tilde {\mathcal G} $ covering
the identity, whose infinitesimalization $q=dQ \colon A \rightarrow \tilde A$ is
filtration-preserving and pushes $\tau $ to $\tilde \tau$. One can similarly make the
collection of Levi structures over $M$ into a category; for details see \ref{functor}.  As
for parabolic geometries, we can similarly identify a graded reductive Lie algebra model
${\mathfrak g} $ for the Lie algebra bundle structure $T$ of a Levi geometry
$({\mathcal H}, R, T)$. The Lie algebra ${\mathfrak g} $ we associate with a Levi
reduction can be taken to be as the same Lie algebra ${\mathfrak g} $ we use for the
parabolic geometry that we are reducing. In a parabolic geometry the condition
\begin{equation}
  \label{coarse}
H^1({\mathfrak g}_-, {\mathfrak g})^1=0
\end{equation}
holds if and only if it holds for every geometry in the same isomorphism class, and the
same is true for Levi structures.

Combining Theorems \ref{existence}, \ref{normalization} and \ref{un}, and appealing to the
fact that prolongation is a functor (Theorem \ref{functor}), we establish the following
solution to the equivalence problem for certain Levi structures:

\begin{theorem}[Theorem \ref{equivalence_}]
  The map that sends a regular normal parabolic geometry over $M$
  to its corresponding Levi reduction, induces a bijection between: (i) isomorphism classes
  of regular normal parabolic geometries over $M$ satisfying \eqref{coarse}; and (ii)
  isomorphism classes of regular Levi structures over $M$ satisfying \eqref{coarse}.
\end{theorem}

\refreshpage
\section{Weyl gauges and semi-direct product structure}\label{semi-direct}
We now return to the general study of filtered Lie algebroids introduced in Section
\ref{introduction}, our main goal being the generalization of Theorem \ref{intro_prolong}
to Lie algebroids and Lie groupoids. The idea of the proof of Theorem \ref{intro_prolong}
is to show that the stabilizer $B \subset {\mathfrak a}$ of $\epsilon $ is a complement
for ${\mathfrak a}^1 $ in ${\mathfrak a} $, and that $B$ preserves the grading of
${\mathfrak a^1} $ determined by $\epsilon $, under the adjoint representation. We
suppress details, as we will provide them for the generalizations.

\vspace{0.5\baselineskip} The groupoids and algebroids in this section are not required to
be transitive and the only class of Lie groups or algebras playing any role are nilpotent ones.

\subsection{Splittings of a filtered Lie algebra}
\label{splittings}
If ${\mathfrak g}$ is a finite-dimensional filtered Lie algebra, then the existence of a
grading element $E \in \graded({\mathfrak g})$ has strong consequences for the Lie
algebra. For, choosing any $\epsilon \in {\mathfrak g}^0$ such that
$\graded_0(\epsilon) = E$, one can show, using induction and $\cap_j {\mathfrak g}^j=0$,
that the maps
$$ X \mapsto  [\epsilon, X] - jX \colon {\mathfrak g}^j \rightarrow {\mathfrak g}^{j+1}$$
are well-defined projections, whose kernels constitute a grading of ${\mathfrak g} $ for
which $\epsilon$ is a grading element; this in turn gives rise to an isomorphism
$\Phi_\epsilon\colon \graded({\mathfrak g}) \rightarrow {\mathfrak g}$ which must in fact be a
Lie algebra isomorphism. When we alter the choice of $\epsilon$, the isomorphism $\Phi_\epsilon$ changes
in a way made precise in \eqref{splittings2} below.

We call $\Phi_\epsilon \colon \graded({\mathfrak g}) \rightarrow {\mathfrak g} $ an {\em
  $E$-splitting} of the filtration. With $E$ and $\epsilon$ fixed as above, there is evidently a
one-to-one correspondence between $E$-splittings and the affine space
$\epsilon + {\mathfrak g}^1$, because $\Phi_{\epsilon'}(E) = \epsilon'$ for all $\epsilon' \in \epsilon + {\mathfrak g}^1$.

Now ${\mathfrak g}^1$ is a nilpotent Lie algebra, integrated by a simply connected
nilpotent Lie group, which we denote by $\exp({\mathfrak g}^1)$; nilpotency ensures the
exponential map is a diffeomorphism. Part \eqref{splittings1} of the lemma below shows
that $\exp({\mathfrak g}^1)$ acts freely and transitively on the set of $E$-splittings by
constructing a concrete realization $G^1$. A proof of this known result appears in
Appendix \ref{appendix_splittings}.
%
\begin{lemma}
  Let $\epsilon \in {\mathfrak g}^0 $ be a lift of some grading element
  $E \in \graded({\mathfrak g})$. Let $G^0$ be {\em any} Lie group integrating
  ${\mathfrak g}^0 $, and let $G^1 \subset G^0$ be the connected Lie subgroup with Lie
  algebra ${\mathfrak g}^1$. Then:
  \begin{conditions}
  \item Under the adjoint action, $G^1$ acts freely and transitively on the affine space
    $\epsilon + {\mathfrak g}^1\subset {\mathfrak g}^0$, and consequently on $E$-splittings of
    ${\mathfrak g} $. In particular, $G^1$ is simply connected (i.e.,
    $G^1 \cong \exp({\mathfrak g}^1)$) so that the infinitesimal adjoint action of
    ${\mathfrak g}^1$ on ${\mathfrak g} $ has a unique globalization
    $\Adjoint\colon G^1 \rightarrow \automorphism({\mathfrak g})$ extending the adjoint
    action just mentioned.\label{splittings1}
  % \item For any $g \in G^1$, $\Adjoint_g - \identity$ sends ${\mathfrak g}^j$ to
  %   ${\mathfrak g}^{j+1}$, for any $j \in {\mathbb Z}$, i.e., is homogeneous of degree
  %   one.\label{splittings30}
  % \item The only linear map $\varphi \colon {\mathfrak g} \rightarrow {\mathfrak g} $ that
  %   commutes with $\adjoint_e$ and such that $\varphi - \identity$ is homogeneous of degree
  %   one is the identity.\label{splittings40}
  \item For any $\epsilon_1, \epsilon_2 \in \epsilon + {\mathfrak g}^1$, we have
    $\Phi_{\epsilon_2} = \Adjoint_g\circ \Phi_{\epsilon_1}$, where $g \in G^1$ is the unique element for
    which $\epsilon_2 = \Adjoint_g \epsilon_1$. \label{splittings2}
  \end{conditions}
\end{lemma}

\subsection{Weyl gauges for filtered Lie algebroids}\label{weyl}
A {\df Weyl gauge} for a filtered Lie algebroid $A$ will be any section $\epsilon$ of
$A^0$ such that $E = \graded_0(\epsilon)$ is a fibre-wise grading section of the bundle of
Lie algebras $\graded(A^0)$, and
\begin{equation}
  [X, \epsilon] \in A^1 \enspace\text{for all $X \in A$.}\label{w2}
\end{equation}
If $A$ is firmly filtered, then the canonical action of $A$ on its anchor kernel
determines an action $\adjoint$ of $A$ on $\graded(A^0)$.  Equation \eqref{w2} then holds
if and only if $E$ is $\adjoint$-invariant. That is, in the firm case, Weyl gauges exist
if and only if an $\adjoint$-invariant fibre-wise grading section of $\graded(A^0)$
exists, and any lift to $A^0$ of such a section is a Weyl gauge. In fact, according to the
corollary stated below all Weyl gauges arise in this way.

Note that we do not require that $E$ be a fibre-wise grading section of
$\graded(A)$, only of $\graded(A^0)$ (but see also \ref{model_data_gradings}).

\begin{theorem}
  Let $A$ be a filtered Lie algebroid admitting a Weyl gauge $\epsilon$, and let $B \subset A$
  denote the isotropy of $\epsilon$ under the canonical representation of $A$ on its anchor
  kernel, i.e., the kernel of the map
  $X \mapsto [X, \epsilon] \colon A \rightarrow A^1$. Then:
  \begin{conditions}
  \item $A$ is firmly filtered, and in particular, $A^1 \subset A$ is an ideal (i.e.,
    $\Gamma(A^1) \subset \Gamma(A)$ is an ideal).\label{pq1}
  \item $A$ is the internal semi-direct product of $B$ and $A^1$.\label{pq2}
  \item The grading $A^0=\oplus_{i\ge0}{\mathfrak a}_i$ associated with $\epsilon$ is
    invariant under the canonical representation of $B$. In particular, the splitting
    $\Phi_\epsilon \colon \graded(A^1)\rightarrow A^1$ intertwines the representation of
    $A/A^1\cong B$ on $\graded(A^1)$ with the representation of $B$ on $A^1$, so that $A$
    is the external semi-direct product of $A/A^1$ and $\graded(A^1)$.\label{pq3}
  \item Under the identification $A \cong A/A^1 \oplus_{\adjoint}\graded(A^1)$ of
    \eqref{pq3}, the Weyl gauge $\epsilon$ takes the form $\epsilon=(E,0)$, for some section $E$ of
    $A^0/A^1 \subset A/A^1$ that commutes under Lie algebroid bracket with all
    sections of $A/A^1$; and $\adjoint_EY = jY$ for any $Y \in \graded(A^0)_j$.\label{pq4}
  \end{conditions}
\end{theorem}
\noindent%
Note that the identification $A \cong A/A^1 \oplus_{\adjoint}\graded(A^1)$ transfers to
$A/A^1 \oplus_{\adjoint}\graded(A^1)$ the following filtration:
$(A/A^1 \oplus_{\adjoint}\graded(A^1))^i= (A^i/A^0)
\oplus_{\adjoint}(\oplus_{j\ge\max\{1,i\}}\graded(A)_j)$.

\begin{example}[Projective geometry] In example \ref{projective} the Lie algebroid
  $A \subset J^1 (TM)$ acts on $TM$ in the usual way, $\adjoint_{J^1 V}W = [V,W]$, which
  gives us associated representations of $A$ on $\gl(TM)$ and $T^*\!M $. On each component
  of $\graded(A^0)=\gl(TM)\oplus T^*\!M$ the infinitesimal adjoint action of $A$ is given
  by these representations, which shows that
  $E = -\identity \in \gl(TM) \subset \graded(A^0)$ is $\adjoint$-invariant. Consequently,
  any lift $\epsilon $ of $-\identity$ through $A^0 \rightarrow A^0/A^1 = \gl(TM)$ is a
  Weyl gauge for $A$. According to the theorem, each such gauge defines an identification
  of $A$ with the semi-direct product $J^1 (TM) \oplus_{\adjoint}T^*\!M $.
\end{example}

\begin{proof}[Proof of theorem]
  The isotropy $B \subset A$ is a subalgebroid, by Jacobi's identity. We first prove
  \begin{equation}
     A = B \oplus A^1, \label{y7}
  \end{equation}
  as vector bundles. It suffices to show that the restriction $r$ of
  $X \mapsto [X, \epsilon]$ to a map $A^1 \rightarrow A^1$ is an isomorphism. However, by
  F1, this restriction is filtration-preserving, and the corresponding map
  $\graded(A^1) \rightarrow \graded(A^1)$ sends $\xi \in \graded(A^1)_j$ to $j \xi$,
  because $\graded_0(\epsilon)$ is a fibre-wise grading section of $\graded(A^0)$. As this
  is obviously an isomorphism, $r$ must be too.

  Next we prove the grading $A^0=\oplus_{i\ge0}{\mathfrak a}_i$ associated with $\epsilon$ is
  invariant under the canonical representation of $B$. To that end, suppose
  $Y \in \Gamma({\mathfrak a}_j)$ for some $j\ge 0$ and let $X \in \Gamma(B)$ be
  arbitrary. The Jacobi identity for the bracket on $A$ gives us
  \begin{equation*}
    [X, [\epsilon, Y]] = [[X, \epsilon], Y] + [\epsilon, [X, Y]].
  \end{equation*}
  On the other hand, applying $\adjoint_X$ to both sides of the
  identity $[\epsilon, Y] = jY$, we have
  \begin{equation*}
     [X, [\epsilon, Y]] = j\adjoint_XY.
  \end{equation*}
  Combining these two results, we obtain
  \begin{equation*}
    [[X, \epsilon], Y] + [\epsilon, \adjoint_XY] = j \adjoint_XY.
  \end{equation*}
  But $[X, \epsilon] = 0 $, because $X \in \Gamma(B)$. We conclude that
  $\adjoint_XY \in \Gamma({\mathfrak a}_j)$.

  Having proven, in particular, that $B$ preserves the filtration of $A^0$, to establish
  \eqref{pq1} it suffices, in view of \eqref{y7}, to show that the filtration of $A^0$ is
  invariant under the canonical action of itself, which follows immediately from F1.

  Claim \eqref{pq2} follows from \eqref{pq1} and \eqref{y7}. The first part of \eqref{pq3}
  has already been addressed, and the rest now follows easily. Part \eqref{pq4} is now also
  clear.
\end{proof}

\begin{corollary}\label{ew1}
  A filtered Lie algebroid $A$ admits a Weyl gauge if and only if it is firmly
  filtered and $\graded(A^0)$ admits an $\adjoint$-invariant fibre-wise grading section $E$.
\end{corollary}

\begin{proof}
  Given a firmly filtered Lie algebroid $A$ with $\adjoint$-invariant fibre-wise grading
  section $E$ of $\graded(A^0)$, any lift of $E$ to a section $\epsilon \in \Gamma(A^0)$
  is immediately seen to be a Weyl gauge. The converse statement follows from the theorem.
\end{proof}

If $A$ is a filtered Lie algebroid, then $A^1$, which lies in the anchor kernel of $A$, is
a bundle of nilpotent Lie algebras, and is accordingly integrated by a bundle of
simply-connected nilpotent Lie groups, denoted $\exp(A^1)$.

\begin{remark}
  By simple-connectivity, the adjoint action of $A^1$ on $A^0$ integrates to an action
  $\Adjoint$ of $\exp(A^1)$ on $A^0$. We have the identity
  $\Adjoint_{\exp(Z)}X=e^{-\adjoint_Z}X$, for any $Z \in \Gamma(A^1)$ and
  $X \in \Gamma(A^0)$, but the right-hand side makes sense for any $X \in \Gamma(A)$.
\end{remark}

\begin{proposition}
  Let $A$ be a filtered Lie algebroid admitting a Weyl gauge, and ${\mathcal G} $ any Lie
  groupoid integrating $A$. Then the source-connected Lie subgroupoid
  ${\mathcal G}^1 \subset {\mathcal G} $ integrating $A^1$ is a bundle of simply-connected
  nilpotent Lie groups isomorphic to $\exp(A^1)$.
\end{proposition}

\begin{proof}
  We prove the first part of the conclusion, as the second part follows from the first, by
  Lie I for Lie groupoids. By Axiom F2, $A^0$ and $A^1$ lie in the kernel of the anchor of
  $A$, and so both are bundles of Lie algebras (totally intransitive). The
  source-connectedness of ${\mathcal G}^1$ now implies that ${\mathcal G}^1 $ is totally
  intransitive (its source and target fibres coincide) so that these fibres are connected
  Lie groups. These Lie groups are subgroups of the fibres of the source-connected
  subgroupoid ${\mathcal G}^0 \subset {\mathcal G}$ integrating $A^0$ (also a bundle of
  Lie groups). With a Weyl gauge $\epsilon$ in hand, we may apply Lemma
  \eqrefs{splittings}{splittings1} fibre-wise to show that these groups are in fact
  simply-connected and nilpotent.
\end{proof}

\subsection{Filtered Lie groupoids and Weyl gauges}\label{weyl2}
Let ${\mathcal G} $ be a filtered Lie groupoid over $M$. The filtration need not be firm;
see \ref{filtered_groupoids} for definitions. We call $\epsilon  \in \Gamma(A)$ a {\df Weyl gauge}
for ${\mathcal G} $ if it is a Weyl gauge for $A$, and if for every arrow
$g \in {\mathcal G}$ with source $m \in M$ we have
\begin{equation}\label{tui}
   \Adjoint_g \epsilon(m) - \epsilon(gm) \in A^1(gm),
\end{equation}
where $gm$ denotes the target of $g$. If ${\mathcal G} $ is firmly filtered, then this
condition holds if and only if $E= \graded_0(\epsilon)$ is ${\mathcal G}$-invariant under
$\Adjoint$, in which case the requirement \eqrefs{weyl}{w2} is automatic.

\begin{proposition}
  Let ${\mathcal G} $ be a filtered Lie groupoid with Lie algebroid $A$ and
  ${\mathcal G}^1 \subset {\mathcal G} $ the source-connected Lie subgroupoid integrating
  $A^1$.
  \begin{conditions}
    \item Under $\Adjoint$, ${\mathcal G}^1$ acts trivially on $\graded(A^0)$.\label{xerox1}
    \item If ${\mathcal G} $ admits a Weyl gauge then ${\mathcal G}^1$ is a bundle of
      simply-connected nilpotent Lie groups isomorphic to $\exp(A^1)$.\label{xerox2}
  \end{conditions}
\end{proposition}
\begin{proof}
  Part \eqref{xerox1} holds because $A^1$ already acts trivially on $\graded(A^0)$ by F1,
  and ${\mathcal G}^1$ has connected source-fibres. Part \eqref{xerox2} is an immediate
  corollary of Proposition \ref{weyl}.
\end{proof}

To navigate a mild obstruction to obtaining semi-direct products in the groupoid
case, we will say the filtration of $\mathcal G$ is {\df weakly firm} if $A^1$ is
${\mathcal G} $-invariant under $\Adjoint$. Evidently a firm filtration of
${\mathcal G} $ is weakly firm. (This notion will not be important for our later applications to parabolic geometry.)
\begin{remark}
  Suppose ${\mathcal G} $ is filtered and admits a Weyl gauge $\epsilon$. Then if $\mathcal G$ has
  connected source fibres, then we claim it is weakly firm. Indeed, $\epsilon$ will be a
  Weyl gauge for the Lie algebroid $A$ of ${\mathcal G} $, so that $A^1 \subset A$ must be an ideal, by
  Theorem \eqrefs{weyl}{pq1}. Our claim follows now from the connectedness assumption.
\end{remark}

Suppose ${\mathcal G} $ is firmly filtered, so that ${\mathcal G}/{\mathcal G}^1 $ acts on
$\graded(A^0)$, by \eqref{xerox1}. This action, also denoted $\Adjoint$, preserves the Lie
algebra bundle bracket. Now, let $\exp(\graded(A^1))$ denote the totally intransitive Lie
groupoid with simply-connected fibres that integrates $\graded(A^1)$, a Lie algebra bundle
with nilpotent Lie algebra model. Then the action just mentioned integrates to an action
of ${\mathcal G}/{\mathcal G}^1$ on $\exp(\graded(A^1))$, also denoted $\Adjoint$,
preserving the totally intransitive Lie groupoid structure, i.e., it maps each (nilpotent)
Lie group fibre isomorphically onto another Lie group fibre. We can accordingly define
the semi-direct product ${\mathcal G}/{\mathcal G}^1 \times_{\Adjoint}\exp(\graded(A^1))$,
and have the following globalization of Theorem \ref{weyl}.

\begin{theorem}
  Let ${\mathcal G} $ be a weakly firm, filtered Lie groupoid with Lie algebroid
  $A$. Define ${\mathcal G}^1 \subset {\mathcal G} $ as in the proposition above, and
  suppose ${\mathcal G} $ admits a Weyl gauge $\epsilon$.  Then, if
  ${\mathcal H} \subset {\mathcal G} $ denotes the isotropy subgroupoid of $\epsilon$ under the
  canonical representation of ${\mathcal G} $, then:
  \begin{conditions}
  \item ${\mathcal G}^1 \subset {\mathcal G} $ is normal,\label{pr1}
  \item ${\mathcal G}={\mathcal G}^1{\mathcal H} $ is the internal semi-direct product of ${\mathcal H} $ and
    ${\mathcal G}^1$,\label{pr2}
  \item The grading $A^0=\oplus_{i\ge0}{\mathfrak a}_i$ associated with $\epsilon$ is
    invariant under the canonical representation of ${\mathcal H}$. \label{pr3}
  \item ${\mathcal G} $ is firmly filtered.\label{pr4}
  \item As a Lie groupoid, ${\mathcal G} $ is identifiable with the external semi-direct
    product ${\mathcal G}/{\mathcal G}^1
    \times_{\Adjoint}\exp(\graded(A^1))$. Specifically, let
    $\Phi_\epsilon \colon \graded(A^1) \rightarrow A^1$ denote the splitting associated with
    $\epsilon$, and let $\tilde \Phi_\epsilon \colon \exp(\graded(A^1)) \rightarrow {\mathcal G}^1$ be
    the morphism of totally intransitive Lie groupoids that integrates $\Phi_e$.  For
    $g \in {\mathcal G}/{\mathcal G}^1$, define $g^{\mathcal H} \in {\mathcal H} $ by the
    requirement $g^{\mathcal H} {\mathcal G}^1 = g$.  Then the map
    $$(g, k) \mapsto \tilde \Phi_\epsilon(k) g^{\mathcal H} \colon {\mathcal G}/{\mathcal G}^1
    \times_{\Adjoint}\exp(\graded(A^1)) \rightarrow {\mathcal G}$$ is a Lie groupoid
    isomorphism.\label{pr5}
  \end{conditions}
\end{theorem}
\begin{proof}
  Since we assume ${\mathcal G} $ is weakly firm, ${A^1 \subset A}$ is invariant under the
  canonical representation $\Adjoint$ of ${\mathcal G} $ on ${\mathcal G}^1$. But, by the
  proposition, the exponential map for ${\mathcal G}^1$ is a diffeomorphism, and we will
  have $g\exp(Z)g^{-1} = \exp(\Adjoint_gZ)$ for any arrow $g \in {\mathcal G} $ beginning
  at the base point of each $Z \in A^1$. This proves \eqref{pr1} because the filtration is
  weakly firm.

  To prove \eqref{pr2} we now show each arrow $g \in {\mathcal G}$, beginning at some
  $m \in M$, can be written uniquely as $g = kh$, with $k \in {\mathcal G}^1$ and
  $h \in {\mathcal G} $. Indeed, from \eqref{tui} we have
  $\Adjoint_g\epsilon(m) \in \epsilon(gm) + A^1|_{gm}$. But, according to Lemma
  \eqrefs{splittings}{splittings1}, the Lie group ${\mathcal G}^1_{gm}$ (the source=target
  fibre of ${\mathcal G}^1$ at $gm \in M$) acts freely and transitively on the affine
  space $\epsilon(gm) + A^1|_{gm}$. Therefore there exists a unique $k \in {\mathcal G}^1$ such
  that $\Adjoint_g\epsilon(m) = \Adjoint_k \epsilon(gm)$. But this means
  $\Adjoint_{k^{-1}g}\epsilon(m) = \epsilon(gm) = \epsilon(k^{-1}gm)$, i.e., $k^{-1}g \in {\mathcal H} $.

  To prove \eqref{pr3}, suppose $Y \in \Gamma({\mathfrak a}_j)$ for some $j\ge 0$ and let
  $h \in {\mathcal H} $ be an arbitrary arrow beginning at some $m \in M$. Since the
  bracket on $A^0$ is ${\mathcal G}$-invariant under $\Adjoint$, the grading identity
  $[\epsilon, Y](m) = jY(m)$ gives us $[\Adjoint_h\epsilon(m), \Adjoint_hY(m)] = j\Adjoint_hY(m)$. From
  the definition of ${\mathcal H} $, we conclude that
  $[\epsilon(hm), \Adjoint_hY(m)] = j\Adjoint_hY(m)$, establishing that
  $\Adjoint_hY(m) \in {\mathfrak a}_j$, as required.

  In view of the fact that ${\mathcal G} = {\mathcal G}^1 {\mathcal H} $, and having
  established \eqref{pr3}, it suffices, in proving \eqref{pr4}, to show that the
  filtration of $A^0$ is invariant under the action of ${\mathcal G}^1$. But $A^0$ is
  already invariant under the action of $A^1$ by F1. Since ${\mathcal G}^1$ is
  source-connected, the filtration of $A^0$ is therefore invariant under the action of
  ${\mathcal G}^1$.

  Part \eqref{pr5} is a rather straightforward consequence of the other parts, whose
  proof is omitted.
\end{proof}

\begin{corollary}\label{ew2}
  A weakly firm, filtered Lie groupoid ${\mathcal G} $ with Lie algebroid $A$ admits a
  Weyl gauge if and only if it is firmly filtered and $\graded(A^0)$ admits an
  $\Adjoint$-invariant fibre-wise grading section $E$.
\end{corollary}
\begin{proof}
  Given an $\Adjoint$-invariant fibre-wise grading section $E$ of $\graded(A^0)$, any lift
  to a section of $A^0$ is a Weyl gauge for $\mathcal G$, as is immediately verified. The
  converse statement follows from the theorem.
\end{proof}

\subsection{Weyl gauge transformations}\label{gauge_transformations}
Let $A$ be a firmly filtered Lie algebroid over $M$ and $\epsilon$ a Weyl gauge
lifting some grading section $E$ of $\graded(A^0)$. Then, applying Theorem \ref{weyl}, we
obtain an isomorphism
$\phi_\epsilon \colon (A/A^1)\oplus_{\adjoint}\graded(A^1) \xrightarrow{\sim} A$. A new
Weyl gauge $\epsilon'$, lifting $E$, determines a second isomorphism
$\phi_{\epsilon'} \colon (A/A^1)\oplus_{\adjoint}\graded(A^1) \xrightarrow{\sim} A$, so
that $\phi_{\epsilon'}\circ \phi_\epsilon^{-1} \colon A \rightarrow A$ is a
filtration-preserving Lie algebroid automorphism covering the identity on $M$, and mapping
the gauge $\epsilon$ to $\epsilon'$. We may construct automorphisms of a firmly filtered
Lie groupoid in a similar way, using Theorem \ref{weyl2}.

\begin{theorem}
  The automorphisms of firmly filtered Lie algebroids and Lie groupoids described above
  are precisely the Weyl gauge transformations (conjugations) defined in \ref{uniqueness}.
\end{theorem}

\begin{proof}[Proof of the {\bfseries infinitesimal case}]
  Let $\epsilon $, $\epsilon'$, $\phi_\epsilon $ and $\phi_{\epsilon'}$ have the meanings
  above. Then it is not hard to see, from the statement of Theorem \ref{weyl}, that
  $\phi_{\epsilon'}\circ \phi_\epsilon^{-1} $ is the unique Lie algebroid isomorphism
  $\varphi$ covering the identity such that:
  \begin{conditions}
  \item \label{gold1} $\varphi(B_\epsilon) = B_{\epsilon'}$, where $B_\epsilon$ denotes
    the isotropy of $\epsilon $ under the canonical representation of $A$ on its anchor
    kernel.
  \item \label{gold2} $\varphi(X) \equiv X \modulo A^1$, for all $X \in \Gamma(A)$.
  \item \label{gold3} $\varphi(Y) = \Phi_{\epsilon'}\circ \Phi_\epsilon^{-1}(Y)$ for all
    $Y\in \Gamma(A^1)$, where $\Phi_\epsilon \colon \graded(A^1) \rightarrow A^1$ denotes
    the splitting determined by $\epsilon $.
  \end{conditions}
  Now, a fibre-wise application of Lemma \eqrefs{splittings}{splittings1} show that there
  exists $Z \in \Gamma(A^1)$ such that
  $\epsilon' = \Adjoint_{\exp(Z)}\epsilon = e^{-\adjoint_Z}\epsilon $. See also Remark
  \ref{weyl}. To show $\phi_{\epsilon'}\circ \phi_\epsilon^{-1}$ is a Weyl gauge
  transformation, it suffices to show that the Weyl gauge transformation
  $\varphi:=e^{-\adjoint_Z}$ satisfies the above conditions. But \eqref{gold1} follows
  immediately, by construction, because $e^{-\adjoint_Z}$ is a Lie algebroid morphism;
  \eqref{gold2} follows from the expansion
  $e^{-\adjoint_Z}X:=X -[Z, X] + \frac{1}{2!}[Z, [Z, X]] - \cdots$ and the fact that
  $\Gamma(A^1) \subset \Gamma(A)$ is an ideal ($A$ is firmly filtered); while
  \eqref{gold3} follows from the fibre-wise application of Lemma
  \eqrefs{splittings}{splittings2}.

  It remains to show {\em every} Weyl gauge transformation $e^{-\adjoint_Z}$ is of the
  form $\phi_{\epsilon'}\circ \phi_\epsilon^{-1}$ for some $\epsilon $ and
  $\epsilon'$. But the above argument already shows this, if we choose $\epsilon $ to be
  any Weyl gauge and $\epsilon' := e^{-\adjoint_Z}(\epsilon)$.
\end{proof}

\begin{proof}[Proof of the {\bfseries global case}]
  Let ${\mathcal G} $ be a firmly filtered Lie groupoid with Lie algebroid $A$, and let
  $\epsilon$ and $\epsilon'$ have the meanings above. Applying Theorem \ref{weyl2}, we
  obtain Lie groupoid isomorphisms
  $\phi_\epsilon, \phi_{\epsilon'} \colon {\mathcal G}/{\mathcal G}^1
  \times_{\Adjoint}\exp(\graded(A^1)) \rightarrow {\mathcal G}$. From the statement of the
  theorem, it is not too hard too see that $\phi_{\epsilon'}\circ \phi_\epsilon^{-1} $ is
  the unique Lie groupoid isomorphism $\varphi$ covering the identity such that:
  \begin{conditions}
  \item \label{silver1} $\varphi({\mathcal H}_\epsilon) = {\mathcal H}_{\epsilon'}$, where
    ${\mathcal H}_\epsilon$ denotes the isotropy of $\epsilon $ under the canonical
    representation of ${\mathcal G}$ on the anchor kernel of $A$.
  \item \label{silver2} $\varphi(g){\mathcal G}^1 \equiv g {\mathcal G}^1$, for all
    $g \in {\mathcal G} $.
  \item \label{silver3} $d\varphi(Y) = \Phi_{\epsilon'}\circ \Phi_\epsilon^{-1}(Y)$ for all
    $Y\in \Gamma(A^1)$, where $\Phi_\epsilon \colon \graded(A^1) \rightarrow A^1$ denotes
    the splitting determined by $\epsilon $.
  \end{conditions}
  In convincing herself of this, the reader will keep in mind that
  ${\mathcal G}^1\cong\exponential(A^1)$ and $\exponential(\graded(A^1))$ are
  source simply-connected, so that a groupoid morphism having one of these as domain is
  determined completely by its infinitesimalization.

  Now choose $Z \in \Gamma(A^1)$ as in the infinitesimal argument, so that
  $\epsilon'=\Adjoint_{\exp(Z)}\epsilon=e^{-\adjoint_Z}\epsilon $. To show that
  $\phi_{\epsilon'}\circ \phi_\epsilon^{-1}$ is a Weyl gauge transformation, it suffices
  to show that the Weyl gauge transformation $\varphi :=K_{\exp(Z)}$ satisfies the above
  conditions, where $K_{\exp(Z)}\colon {\mathcal G} \rightarrow {\mathcal G}$ denotes
  conjugation by the (bi)section $\exp(Z)$. To this end, suppose $h \in {\mathcal G} $ is
  an arrow beginning at some $m \in M$ and that $h \in {\mathcal H}_\epsilon$. Then
  $\Adjoint_h \epsilon(m) = \epsilon(hm)$. Applying $\Adjoint_{\exp(Z)}$ to both sides, we
  conclude that $\Adjoint_{K_{\exp(Z)}(h)}\epsilon'(m) = \epsilon'(m)$, showing
  $K_{\exp(Z)}(h) \in {\mathcal H}_{\epsilon'}$. We can reverse the roles of $\epsilon $
  and $\epsilon' $ and repeat the argument, and conclude that
  $K_{\exp(Z)}({\mathcal H}_\epsilon) = {\mathcal H}_{\epsilon'}$, i.e., \eqref{silver1}
  holds. The normality of ${\mathcal G}^1$ (Theorem \eqrefs{weyl2}{pr1}) means
  $g {\mathcal G}^1 = {\mathcal G}^1g$, for any $g \in {\mathcal G}$. If
  $g \in {\mathcal G}$ is an arbitrary arrow, beginning at some $m \in M$, we compute,
  appealing to normality twice,
    \begin{multline*}
      K_{\exp(Z)}(g){\mathcal G}^1 =
    {\mathcal G}^1 \exp(Z(gm))g\exp(-Z(m))\\ =
    {\mathcal G}^1 g\exp(-Z(m)) =
    g\exp(-Z(m)){\mathcal G}^1 =
    g{\mathcal G}^1,
  \end{multline*}
  which proves \eqref{silver2}. Since $dK_{\exp(Z)}=e^{-\adjoint_Z}$, \eqref{silver3}
  already follows from the argument given in the infinitesimal case.\footnote{The source
    of the minus sign is our convention of using right-invariant vector fields to define
    Lie brackets, so that $dK_{\exp(Z)}X=\Adjoint_{J^1\exp(Z)}X=e^{-\adjoint_Z}X$,
    $X \in \Gamma(A)$.}

  To show every Weyl gauge transformation $K_{\exp(Z)}$ is of the form
  $\phi_{\epsilon'}\circ \phi_\epsilon^{-1}$ for some $\epsilon $ and $\epsilon'$, take
  $\epsilon $ to be any Weyl gauge, $\epsilon' := e^{-\adjoint_Z}(\epsilon)$, and repeat
  the preceding argument.
\end{proof}

% According to the theorem below, gauge transformations are closed under
% composition.

% It is not hard to see that a gauge transformation $\varphi$ must satisfy:
% \begin{align}
%    \varphi(X) &\equiv X \modulo A^1,\quad  X \in \Gamma(A)\label{gauge1}\\
%    \varphi(Y) &\equiv Y \modulo A^{j+1},\quad Y \in \Gamma(A^j),\, j > 0.\label{gauge2}
% \end{align}
% In particular, the second identity follows from a general fact about splittings of a
% filtered vector bundle $V$: If $\Phi_1, \Phi_2 \colon \graded(V) \rightarrow V$ are
% splittings, then $\Phi_2 \circ \Phi_1^{-1} - \identity$ is homogeneous of degree one.

% The group of all filtration-preserving Lie algebroid isomorphisms
% $\varphi \colon A \rightarrow A$ satisfying \eqref{gauge1} and \eqref{gauge2} will be
% denoted $\GGauge(A)$, a definition that makes sense for an arbitrary filtered Lie
% algebroid $A$. Note that \eqref{gauge1} implies $\varphi$ must cover the identity, because
% F1 then forces $\#\varphi(X) = \# X$, and we suppose the base $M$ is connected.

% \begin{theorem}
%   Let $A$ be a filtered Lie algebroid over $M$. Then for each pair of Weyl gauges
%   $\epsilon_1, \epsilon_2$ with $\graded_0(\epsilon_1)=\graded_0(\epsilon_2)$ there exists unique
%   $\varphi \in \GGauge(A)$ such that $\varphi(\epsilon_1) = \epsilon_2$. In particular, if $A$ admits
%   a Weyl gauge, then $\GGauge(A)$ is precisely the set of gauge transformations of $A$.
% \end{theorem}


% In particular, $\GGauge(A)$ acts freely and transitively on the set of all Weyl gauges for
% $A$ that lift some fixed fibre-wise grading section $E$ of $\graded(A^0)$, whenever this
% exists.  Applying Lemma \eqrefs{splittings}{splittings1} fibre-wise shows that the group
% of sections $\Gamma({\exp(A^1)})$ of the bundle of nilpotent Lie groups $\exp(A^1)$ also
% acts freely and transitively via $\Adjoint$ on the set of Weyl gauges, lifting some
% section $E$. While each choice of Weyl gauge $\epsilon$ accordingly determines a bijection
% $\GGauge(A)\cong \Gamma({\exp(A^1)})$, there is no canonical isomorphism between the two
% groups in general. The example below is a notable exception.

% \begin{proof}[Proof of theorem]
%   From our preparatory remarks above, we already know that some $\varphi \in \GGauge(A)$
%   with $\varphi(\epsilon_1)=\varphi(\epsilon_2)$ exists, namely some gauge transformation. To prove the
%   first statement of the theorem it remains to establish uniqueness.

%   Suppose $\varphi' \in \GGauge(A)$ also maps $\epsilon_1$ to $\epsilon_2$. Then
%   $\varphi^{-1} \circ \varphi'$ will be an element of $\GGauge(A)$ mapping $\epsilon_1$ to
%   $\epsilon_1$. So, to establish uniqueness, it suffices to suppose $\varphi(\epsilon_1) = \epsilon_1$ and
%   prove that $\varphi $ must be the identity.

%   By Theorem \ref{weyl}, we may suppose, without loss of generality, that $A$ is the
%   semi-direct product $B\oplus_r (\oplus_j {\mathfrak a}_j)$ of a filtered Lie algebroid
%   $B$, with $B\le 0$, with a filtered Lie algebra bundle
%   $A^1=\oplus_{j=1}^k{\mathfrak a}_j$, on which $B$ is acting by $r$, a representation
%   that preserves the grading. Moreover, we may suppose there exists a section $E$ of $B^0$
%   such that $\epsilon_1 = (E, 0)$, and such that $[E, X]=0$ for all $X \in \Gamma(B)$. When we
%   think of $E$ as a section of the Lie algebra bundle
%   $B^0 \oplus (\oplus_{j>0}{\mathfrak a}_j)$, we have $\adjoint_EY=r_EY$ for
%   $Y \in \Gamma(\oplus_{j>0}{\mathfrak a}_j)$, where $\adjoint$ is the adjoint
%   representation of this Lie algebra bundle.

%   Requirement \eqref{gauge1} means that $\varphi(X, Y) = (X, \theta(X) + \lambda(Y))$, for
%   some vector bundle morphisms $\theta \colon B \rightarrow A^1$ and
%   $\lambda \colon A^1 \rightarrow A^1$ covering the identity on $M$. Since
%   $\varphi(\epsilon_1)=\epsilon_1$, we conclude that $\theta(E) = 0$.

%   Since $\varphi $ is a Lie algebroid morphism, we must have
%   $\varphi([(E,0), (0,Y)]) = [\varphi(E,0), \varphi(0,Y)]$ for all $Y \in A^1$. Applying
%   the definition of the semi-direct product bracket, and using $\theta(E)=0$, we can write
%   this as $\lambda(\adjoint_EY) = \adjoint_E \lambda(Y)$. Since requirement \eqref{gauge2}
%   implies that is $\lambda - \identity$ is homogeneous of degree one, we may apply Lemma
%   \eqrefs{splittings}{splittings40} fibre-wise to conclude that $\lambda(Y) = Y$, so
%   that $\varphi$ is the identity.

%   Turning to the second claim of the theorem, suppose $\varphi \in \GGauge(A)$, let
%   $\epsilon_1$ be a Weyl gauge, and put $\epsilon_2 := \varphi(\epsilon_1)$.
%   Corollary \ref{ew1} shows that $A$ is firmly filtered, so that a section
%   $\epsilon \in \Gamma(A^0)$ is a Weyl gauge if and only if $\graded_0(\epsilon)$ is an
%   $\adjoint$-invariant grading section of $\graded(A^0)$. But \eqref{gauge1} ensures that
%   $\graded_0(\epsilon_1) = \graded_0(\epsilon_2)$, so $\epsilon_2$ is Weyl gauge, because
%   $\epsilon_1$ is. By the first part of the theorem, $\varphi$ must coincide with the
%   gauge transformation mapping $\epsilon_1$ to $\epsilon_2$.
% \end{proof}

\refreshpage
\section{Cartan connections on Lie groupoids and algebroids}\label{cartan_section}

Cartan connections on Lie groupoids, introduced in \cite[Appendix A]{Blaom_12}, generalize
to the intransitive case the classical Cartan connections introduced by Ehresmann
\cite{Ehresmann_51} and in widespread use, when the latter notion is stripped of model
data. The corresponding infinitesimal notion, Cartan connections on Lie algebroids, were
introduced some time earlier, in \cite{Blaom_06}. The relationship with the classical
notion is detailed in \cite{Blaom_16b}.

The meaning of curvature for these connections is different from the classical
one. Curvature is still an obstruction to symmetry, but the kind of symmetry is not
preordained by the specification of a flat model {\em a priori}.

With the exception of Proposition \ref{cartan}, which we presume is new, this section is a
summary of definitions and results presented in the cited works and elsewhere. It is
logically independent of Sections \ref{introduction} and  \ref{semi-direct}.

\subsection{Cartan connections on a Lie groupoid}\label{cartan}%
A {\df Cartan connection} on a Lie groupoid ${\mathcal G} $ over $M$ is an $n$-plane field
$D \subset T {\mathcal G}$ arising from some right inverse
${\mathcal G} \rightarrow J^1 {\mathcal G} $ for the canonical projection
$J^1 {\mathcal G} \rightarrow {\mathcal G} $, which is necessarily uniquely determined by
$D$. Here $J^1 {\mathcal G} $ denotes the Lie groupoid of one-jets of bisections of
${\mathcal G} $. Of course, we are understanding the right inverse to be a Lie groupoid
morphism. This is equivalent to requiring that $D \subset T {\mathcal G}$ be
multiplicatively closed, in the sense of \cite{Salazar_13,Crainic_etal_15}, but this
interpretation will play no role here.

The usual adjoint action of a Lie group on its Lie algebra is generalized by an action of
$J^1 {\mathcal G} $ on the Lie algebroid $A$ of ${\mathcal G} $, denoted $\Adjoint$
\cite{Blaom_16b}. Composing with the right inverse
${\mathcal G} \rightarrow J^1 {\mathcal G} $ of
$J^1 {\mathcal G} \rightarrow {\mathcal G} $ associated with $D$, we obtain a
representation $\bar D$ of ${\mathcal G}$ on $A$. This representation extends the
canonical one of ${\mathcal G} $ on elements of the anchor kernel of $A$ (which we have
also been denoting by $\Adjoint$ in Section \ref{semi-direct}).

The prototype of a Cartan connection is the horizontal $n$-plane field $D$ on
an action groupoid $G \times M$, for a smooth action of some Lie group $ G $ on
$M$, which need not be transitive. In this case
\begin{equation}
  \bar D_{(g, m)}(\xi, m) = (\Adjoint_g \xi, g\cdot m).\label{adjoint}
\end{equation}

Every Cartan connection $D$ on a {\em transitive} Lie groupoid can be recovered from the
representation $\bar D$:

\begin{proposition}
  Suppose ${\mathcal G} $ is a Lie groupoid with a transitive Lie algebroid $A$. Then for
  every representation $\rho $ of ${\mathcal G} $ on $A$, extending the canonical
  representation of ${\mathcal G} $ on the anchor kernel, there exists a unique Cartan
  connection $D$ on ${\mathcal G} $ such that $\bar D = \rho $.
\end{proposition}
\noindent%
The infinitesimal version of this result, Proposition \ref{hsd} below, already appears in
\cite{Blaom_06}, and has an easy proof. The proposition above is proven in Appendix
\ref{rut}.


\subsection{Infinitesimal Cartan connections}\lab{hsd}%
Infinitesimalizing a Cartan connection, viewed as a Lie groupoid
morphism ${\mathcal G} \rightarrow J^1 {\mathcal G}$, we obtain a splitting $s
\colon A \rightarrow J^1 A $ of the exact
sequence
\begin{equation*}
  0\longrightarrow T^*\!M\otimes A\longrightarrow J^1A\longrightarrow A\longrightarrow 0
\end{equation*}
in the category of Lie algebroids. Here $J^1 A $ denotes the Lie algebroid of one-jets of
sections of the Lie algebroid $A $ of ${\mathcal G}$. In the category of vector bundles, splittings
$s$ of the above sequence are in one-to-one correspondence with Koszul connections
$\nabla$ on $A$; this correspondence is given by\footnote{According to our sign
  conventions, the inclusion $T^*\!M \otimes A \rightarrow J^1 A $ induces the following
  map on sections: $df \otimes X \mapsto f J^1 X - J^1 (f X)$.}
\begin{equation}
  sX = J^1 X + \nabla X; \qquad  X \in \Gamma(A). \mathlab{cspan}
\end{equation}
When $s \colon A \rightarrow J^1 A $ is a morphism of Lie algebroids, as is the case here,
then $\nabla $ is called a {\df Cartan connection} on $A$ \cite{Blaom_06}, or an {\df
  infinitesimal Cartan Connection} when we want to distinguish it from the corresponding
global notion. Evidently, the notion makes sense for arbitrary Lie algebroids, not only
those integrated by Lie groupoids. According to \cite{Blaom_06}, $\nabla $ is a Cartan
connection on $A$ if and only if
\begin{equation*}
  \nabla_V[X, Y] = [\nabla_VX,
        Y]+[X,\nabla_VY]-\nabla_{\bar\nabla_XV}Y+\nabla_{\bar\nabla_YV}X,
\end{equation*}
for all vector fields $V$ on $M$ and sections $X, Y$ of $A$. Here $\bar\nabla$ denotes the
associated $A$-connection on $TM$ defined by
\begin{equation}
 \bar\nabla_XV= \#\nabla_VX +[\#X, V],
\end{equation}
an $A$-representation when $\bar\nabla $ is Cartan. Here $\# \colon A \rightarrow TM$
denotes anchor.

Given a Cartan connection $\nabla $ on some Lie algebroid $A$, we can compose the
corresponding splitting $s \colon A \rightarrow J^1 A$ with the adjoint action of $J^1 A$
on $ A$, $\adjoint_{J^1X}Y = [X, Y]$, to obtain a self-representation $\bar \nabla $ of
$A$. Explicitly, we have

\begin{equation}
 \bar\nabla_XY = \nabla_{\#Y}X +[X, Y].\label{zero}
\end{equation}
The anchor $\# \colon A \rightarrow TM$ becomes $\bar\nabla$-equivariant. A $TM$-connection $\nabla $ is actually Cartan if and only if
\begin{equation}
  (\nabla_V\torsion \bar\nabla)(X,Y) =
 \curvature \nabla (\#X, V)Y -  \curvature \nabla (\#Y, V) X,
\end{equation}
where
\begin{equation*}
  \torsion \bar\nabla (X, Y) = \bar\nabla_XY - \bar\nabla_YX - [X, Y] =
  \nabla_{\#Y}X - \nabla_{\#X}Y + [X, Y].
\end{equation*}

The representation $\bar\nabla$ of $A$ on itself coincides with the canonical
representation of $A$ on sections lying in the anchor kernel (denoted $\adjoint$ in
Section \ref{semi-direct}). In the transitive case, $\nabla $ can be recovered from
$\bar\nabla $:

\begin{proposition}[\mbox{\cite[Proposition 6.1]{Blaom_06}}]
  Suppose $A $ is a transitive Lie algebroid. Then for every representation $\rho $ of
  $A $ on itself, extending the canonical representation of $A$ on sections lying in the
  anchor kernel, there exists a unique Cartan connection $\nabla $ on $A$ such that
  $\bar \nabla = \rho $.
\end{proposition}

\subsection{Curvature as obstruction to symmetry}\label{curvature}
The {\df curvature} of $\nabla $ is defined as usual as per Koszul connections. This
notion of curvature is not to be confused with curvature as this is generally understood
in the Cartan geometry literature, what we have called {\df model curvature}, whose Lie
algebroid analogue was defined in \ref{normalization}. For further context, see
\cite{Blaom_16b}.  The prototype of an infinitesimal Cartan connection is the trivial flat
connection $\nabla $ on an action algebroid ${\mathfrak g} \times M$, for some
infinitesimal action of a Lie algebra $\mathfrak g$ on $M$. If we identify
${\mathfrak g} $ with the constant ($\nabla$-parallel) sections of
${\mathfrak g} \times M$, then its bracket is
$\torsion\bar\nabla(\,\cdot\,,\,\cdot\,)$. Indeed, let
$\tau \in \Gamma(\wedge^2 A^* \otimes A)$ denote the trivial extension of the bracket on
${\mathfrak g} $ to a fibre-wise bracket on $A = {\mathfrak g} \times M$, and recall that
the Lie algebroid bracket on ${\mathfrak g} \times M$ is given by
\begin{equation}
  [X,Y]=\nabla_{\#X}Y-\nabla_{\#Y}X +\tau(X,Y). \label{one}
\end{equation}
Then we can write
\begin{equation}
    [X,Y]=\bar\nabla_XY-\bar\nabla_YX - \tau(X,Y),\label{two}
\end{equation}
from which $\tau = \torsion \bar\nabla $ immediately follows.

\begin{theorem}[\cite{Blaom_06}]
  If $M$ is simply connected, then every Lie algebroid $A$ equipped with a flat Cartan
  connection $\nabla$ is naturally isomorphic to an action algebroid
  ${\mathfrak g} \times M$ (possibly intransitive) where ${\mathfrak g}\subset \Gamma(TM) $
  is the Lie algebra of $\nabla $-parallel sections, equipped with bracket
  $\torsion \bar\nabla$.
\end{theorem}
\noindent More informally, we have:
\begin{aside}
  A Lie algebroid equipped with a Cartan connection is an infinitesimal symmetry deformed
  by curvature; the torsion of the connection is the deformed symmetry Lie bracket.
\end{aside}

If $\curvature \nabla =0$ but $M $ is not simply connected, then $A$ is a Lie algebra
action with monodromy twist \cite{Blaom_16b}. Lie groupoids with Cartan connections,
whose infinitesimalizations are flat, define pseudogroups of symmetries of $M$, and under
an additional completeness assumption, twisted Lie group actions \cite{Blaom_16,
  Blaom_16b}. In the transitive case, one can recover a locally homogeneous structure,
assuming ``geometric closure'', if not global homogeneity up to cover \cite{Blaom_13}.

\begin{example}[Riemannian geometry]
  Associated with every Riemannian metric is a canonical Cartan connection $\nabla $ on
  the isotropy subalgebroid\footnote{This isotropy is the abstract homogeneous PDE you
    solve to find Killing fields (whether or not they exist).} $A \subset J^1 (TM)$ of the
  metric \cite{Blaom_06,Blaom_12}, which is an infinitesimalization of a global connection
  $D$ on the isotropy subgroupoid ${\mathcal G} \subset J^1(M \times M)$ of the metric
  \cite{Blaom_16b}. It's significance is that the anchor induces a map
  $\Gamma(A) \rightarrow \Gamma(TM)$ establishing a one-to-one correspondence between
  $\nabla $-parallel sections and infinitesimal isometries (Killing fields).

  Under a natural identification of $A$ with $ TM \oplus \so(TM)$, the Lie bracket is
  given by
\begin{equation*}
  \left[
  \begin{pmatrix}
    V_1\\ C_1
  \end{pmatrix},
  \begin{pmatrix}
    V_2\\ C_2
  \end{pmatrix}
\right] =
\begin{pmatrix}
  [V_1,V_2]\\
  [C_1, C_2] + \nabla^{TM}_{V_1} C_2 - \nabla^{TM}_{V_2}
  C_1 + \curvature \nabla^{TM}(V_1,V_2)
\end{pmatrix}\enspace,
\end{equation*}
where $\nabla^{TM}$ is the Levi-Cevita connection. The Cartan connection is given by
\begin{equation*}
  \nabla_U
  \begin{pmatrix}
    V \\ C
  \end{pmatrix}
  =
  \begin{pmatrix}
    \nabla^M_UV + C U \\
    \nabla^M_UC + \curvature \nabla^M (U,V)
  \end{pmatrix}\,,
\end{equation*}
which has torsion
\begin{equation}
  \torsion \bar\nabla \left(
    \begin{pmatrix}
        V_1 \\ C_1
      \end{pmatrix},
      \begin{pmatrix}
        V_2 \\ C_2
      \end{pmatrix}
  \right)=
  \begin{pmatrix}
    C_1 V_2 -C_2 V_1 \\
    [C_1,C_2] - \curvature \nabla^{TM} (V_1,V_2)
  \end{pmatrix}\,.  \label{torsion}
\end{equation}
The curvature of $\nabla $ is readily computed, vanishing precisely when $M$ has constant
sectional curvature $s$. From the formula for the torsion, we conclude that
${\mathfrak g} $ in the preceding theorem is the symmetry Lie algebra of the Riemannian
sphere, plane or hyperbolic space, according to whether $s$ is positive, zero, or
negative.
\end{example}

\subsection{Cartan connections compatible with a filtration}\label{compat}
Recall that an infinitesimal Cartan connection $\nabla$ on a filtered Lie algebroid $A$ is
{\df compatible} with the filtration if the filtration is invariant under the associated
representation $\bar\nabla $. Similarly, a Cartan connection $D$ on a filtered Lie
groupoid ${\mathcal G} $ with Lie algebroid $A$ is {\df compatible} with the filtration
provided the filtration of $A$ is invariant under the associated representation $\bar D$,
which in turn implies compatibility of the corresponding infinitesimal Cartan connection
$\bar\nabla$.

In addition to the examples given in \ref{filtered}, the following result justifies our
focus on {\em firmly} filtered Lie algebroids.
\begin{proposition}
  If a transitive filtered Lie groupoid (Lie algebroid) admits a compatible
  (infinitesimal) Cartan connection, then it is firmly filtered.
\end{proposition}
\begin{proof}
  Suppose $\nabla $ is a Cartan connection on a transitive filtered Lie algebroid
  $A$. Then $\bar\nabla $ extends the canonical representation $\adjoint$ of $A$ on its
  anchor kernel, which contains $A^0$. So $\adjoint_X Y := [X, Y] = \bar\nabla_XY$ for
  $X \in A$ and $Y \in A^0$. If $\nabla $ is compatible with the filtration, then $A^0$
  and the filtration of $A^0$ must therefore be $\adjoint$-invariant. The groupoid case
  follows immediately from the infinitesimal one.
\end{proof}

\subsection{Filtered Klein geometries}\label{homogeneous}
We now prove some claims made in \ref{eg2} regarding the homogeneous space $M=G/P$
described there. Let ${\mathcal G} = G \times M$ be the action groupoid, equipped with its
canonical Cartan connection $D$, so that ${\mathcal G}$ acts on
$A = {\mathfrak g} \times M$ according to \eqrefs{cartan}{adjoint}. Since the filtration
of ${\mathfrak g} $ is $P$-invariant, the filtration of $A$ is $\bar D$-invariant.

Since $A$ is transitive and $A^0$ is the anchor kernel, we have, as vector bundles,
\begin{equation*}
  \graded(A) \cong \graded(TM)\oplus \graded(A^0).
\end{equation*}
As in \ref{curvature}, we denote the fibre-wise Lie bracket on $A={\mathfrak g} \times M$
coming from ${\mathfrak g} $ by $\tau $, which coincides with the torsion of the
infinitesimalization $\nabla $ of $D$, namely the canonical flat Koszul connection on the
trivial bundle ${\mathfrak g} \times M$. We note in passing that $\tau$ is evidently
$\bar D$-invariant, and so $\bar\nabla$-invariant. When we want to emphasize we are using
the bracket $T=\graded_0(\tau)$ when viewing $\graded(A)$, $\graded(A^0)$ or $\graded(TM)$
as Lie algebra bundles, we shall denote them by $\graded^T(A)$, $\graded^T(A^0)$ and
$\graded^T(TM)$.

\begin{proposition}
  The vector bundle filtration of $A = {\mathfrak g} \times M$ defined in \ref{eg2} is a
  firm Lie algebroid filtration, and ${\mathcal G} = G \times M$ is a firmly filtered Lie
  groupoid. Furthermore, equipping $\graded(A)$ with the corresponding Lie algebra bundle
  structure (Proposition \ref{filtered}), we have
  \begin{equation*}
    \label{decomposition}
    \graded(A) = -\graded^T(TM)\oplus \graded^T(A^0)\quad
    \text{(Lie algebra bundle direct sum)}
  \end{equation*}
  where -$\graded^T(TM)$ is $\graded^T(TM)$ equipped with
  negative bracket, and $T=\graded_0(\tau)$.
\end{proposition}

\begin{proof}
  Axiom F2 holds by construction. Let $X\in \Gamma(A^j)$ and $Y\in \Gamma(A^k)$ be
  given. Then we claim:
  \begin{align}
  \bar\nabla_X Y &= [X, Y] \quad\text{if $k \ge 0$}\label{gamma}\\
  \bar\nabla_X Y &= \tau(X, Y) \quad\text{if $j \ge 0$}\label{delta}\\
  [X, Y] &= \tau(X, Y) \quad\text{if $j \ge 0$ and $k \ge 0$} \label{alpha}\\
  [X, Y] &\equiv -\tau(X, Y) \mod A^{j + k + 1} \quad\text{if $j < 0$ and $k < 0$}\label{beta}\\
  [X, Y] &\in \Gamma(A^{j + k + 1}) \quad\text{if $j < 0$ and $k \ge 0$}.\label{blue}
  \end{align}
  Equation \eqref{gamma} follows from \eqrefs{hsd}{zero} and F2. If $j\ge 0$, then
  Equation \eqrefs{curvature}{one} reads $[X, Y] = - \nabla_{\#Y}X +\tau(X, Y)$, because
  $\#A^j=0$ in that case. This and \eqrefs{hsd}{zero} delivers \eqref{delta}.  Claim
  \eqref{alpha} follows immediately from the preceding two.

  If $j < 0$, then $j + k + 1 \le k$, and so
  $A^k \subset A^{j + k+ 1}$. Similarly, if $k < 0$, then
  $A^j \subset A^{j + k + 1}$. Since the filtration is
  $\bar\nabla$-invariant, \eqref{beta} now follows from \eqrefs{curvature}{two}.

  As already mentioned, if $j <0 $, then $A^k \subset A^{j+k+1}$. On
  the other hand, if additionally $k \ge 0$, then
  $[X, Y] = \bar\nabla_XY$, by \eqref{gamma}. So \eqref{blue} is a
  consequence of the $\bar\nabla $-invariance of $A^k$.

  To establish Axiom F1 for filtered Lie algebroids, we need to show
  $[X, Y] \in \Gamma(A^{j+k})$. Equations \eqref{alpha} takes care of the case $j\ge 0$
  and $k \ge 0$. Equation \eqref{beta} takes care of the case $j < 0$ and $k < 0$ because
  $A^{j+k+1} \subset A^{j+k}$ is always true. The remaining case is $j < 0$ and $k \ge 0$
  (and the case $j \ge 0$ and $k < 0$, which will follow by symmetry). But as
  $A^{j + k + 1} \subset A^{j + k}$, this already follows from \eqref{blue}.

  The last statement in of the theorem follows easily from \eqref{alpha}, \eqref{beta},
  and \eqref{blue}.

  Since the filtration of $A$ is $\bar D$-invariant, $D$ is compatible with the
  filtration, and so firmness follows from Proposition \ref{compat}.
\end{proof}

\refreshpage
\section{Model data}\label{modeldata}
Model data, defined in \ref{preview}, generalizes the trivial Lie algebra bundle
structure of an action algebroid ${\mathfrak g} \times M$.

\subsection{Constructing Cartan connections compatible with model data}\label{constructing}
In Section \ref{filtered_cartan} we shall need the following important result, reducing,
in the {\em transitive} case, the problem of constructing Cartan connections compatible
with given model data, to the problem of constructing representations of a suitable
subalgebroid/subgroupoid.

\begin{proposition}
  {\em \bfseries Infinitesimal case.} Let $A$ be a transitive Lie algebroid that can be written as
  vector bundle sum $A = B \oplus A'$, where $B \subset A$ is a subalgebroid and
  $A' \subset A$ an ideal lying in the kernel of the anchor
  $\# \colon A \rightarrow TM$. Let $\tau $ be model data on $A$ and suppose
  there exists a representation $\rho^B$ of $B$ on $A$, with respect to which $\tau $ is
  invariant, and such that $\rho^B$ extends the canonical representation of $B \subset A $
  on the anchor kernel of A:
  \begin{equation}
    \rho^B_X Z = [X, Z]\enspace \text{whenever $\#Z=0$, $Z \in \Gamma(A)$,
      $X \in \Gamma(B)$}.\label{ext1}
  \end{equation}
  Then there exists a unique Cartan connection $\nabla $ on $A$, necessarily weakly
  compatible with $\tau $, such that
  \begin{equation}
    \bar\nabla_{X + Y}W = \rho^B_XW + \tau(Y, W);\qquad X
    \in \Gamma(B),\,Y \in \Gamma(A'),\,W \in \Gamma(A).\label{ext2}
  \end{equation}
  If $\tau $ is compatible with a filtration of $A$, and $\rho^B$ preserves the
  filtration, then $\nabla $ is also compatible with the filtration.
  If, additionally,
  \begin{equation}
    \rho^B_{Z}W = \tau(Z, W)\enspace
    \text{whenever $\#Z=0$, $Z \in \Gamma(B)$, $W \in \Gamma(A)$,}\label{ext3}
  \end{equation}
  then $\tau $ is strongly compatible with $\nabla $.

  {\em \bfseries Global case.} Suppose ${\mathcal G} $ is a Lie groupoid, with Lie algebroid $A$,
  that can be written ${\mathcal G} = {\mathcal G}' {\mathcal H} $ with
  ${\mathcal G}'\cap {\mathcal H} = M$ (groupoid of identity elements), where
  ${\mathcal G}' \subset {\mathcal G} $ is a totally intransitive, normal, Lie subgroupoid
  with simply-connected fibres. Let $\tau $ be model data on $A$ and suppose there is a
  representation $\rho^{\mathcal H}$ of ${\mathcal H} $ on $A$, with respect to which
  $\tau $ is invariant, and such that $\rho^{\mathcal H}$ extends the canonical
  representation of ${\mathcal H} \subset {\mathcal G} $ on the anchor kernel of A:
  \begin{equation}
    \label{pony4}
    \rho^{\mathcal H}_hZ = \Adjoint_h Z  \enspace
      \text{whenever $\#Z=0$, $h \in {\mathcal H}$}.
  \end{equation}
  Then, there exists a unique Cartan connection $D $ on ${\mathcal G}$, necessarily
  weakly compatible with $\tau $, such that
  \begin{equation}
    \bar D_{kh}W = \Adjoint^\tau_k \rho^{\mathcal H}_hW,\label{ext17}
  \end{equation}
  for each arrow $h \in H$ beginning at some $m \in M$, $k \in {\mathcal G}^1|_{hm}$ and
  $W \in A|_m$. Here $\Adjoint^\tau$ is unique representation of ${\mathcal G}'$ on $A$
  integrating the infinitesimal representation $\adjoint^\tau$ of the Lie algebroid $A'$
  of ${\mathcal G} '$ on $A$ defined by $\adjoint^\tau_YW=\tau(Y, W)$.  If $\tau $ is
  compatible with a filtration of $A$, and $\rho^B$ preserves the filtration, then $D$ is
  also compatible with the filtration.
\end{proposition}
\noindent%
Note that $\Adjoint^\tau$ is well-defined on account of the hypothesis of
simple-connectivity.
\begin{proof}{\em \bfseries Infinitesimal case.} Under the hypotheses of the theorem, define an
  $A$-connection $\rho $ on $A$ using the right-hand side of \eqref{ext2}:
  \begin{equation*}
   \rho_{X + Y}W = \rho^B_XW + \tau(Y, W);\qquad
    X \in \Gamma(B),\,Y \in \Gamma(A'),\,W \in \Gamma(A).
  \end{equation*}
  By Proposition \ref{hsd}, to show there exists a Cartan connection $\nabla $ satisfying
  \eqref{ext2}, it suffices to show that $\rho $ is actually a representation, and,
  secondly, that $\rho $ extends the canonical representation of $A$ on sections of its
  anchor kernel:
  \begin{equation}
    \label{gobbly}
    \rho_WZ = [W, Z]\enspace\text{whenever $\#Z=0$, $W \in \Gamma(A)$.}
  \end{equation}

  If $W \in \Gamma(B)$, then \eqref{gobbly} holds, by hypothesis \eqref{ext1}. If
  $W \in \Gamma(A')$ and $\#Z=0$, then $\rho_WZ=\tau(W,Z)=[W, Z]$, because both $W$ and
  $Z$ lie in the anchor kernel and $\tau $ is model data. Since $A = B \oplus A'$, this
  proves \eqref{gobbly}.

  Since the restriction of $X \mapsto \rho_X $ to $B$ is $\rho^B$, a representation, and
  the restriction of $Y \mapsto \rho_Y $ to $A'$ is $Y \mapsto \tau(Y, \,\cdot\,)$, also a
  representation, to show $\rho $ is itself a representation, it suffices to prove that

  \begin{equation*}
    \rho_X \rho_Y W - \rho_Y \rho_X W - \rho_{[X,Y]}W = 0, \qquad W \in \Gamma(A),
  \end{equation*}
  whenever $X \in \Gamma(B)$ and $Y \in \Gamma(A')$. But in that case,
  $[X, Y] \in \Gamma(A')$, because $A' \subset A$ is an ideal, and we compute
  \begin{align*}
    \rho_X \rho_Y W - \rho_Y \rho_X W - \rho_{[X,Y]}W
       &= \rho^B_X(\tau(Y, W)) - \tau(Y, \rho^B_XW) - \tau([X,Y], W)\\
                     &= \rho^B_X(\tau(Y, W)) - \tau(Y, \rho^B_XW) - \tau(\rho^B_XY, W),
                       \quad\text{by \eqref{ext1}}  \\
                     &= 0,
                       \quad\text{by the $\rho^B$-invariance of $\tau $.}
  \end{align*}
  Proof of the remaining claims in infinitesimal case is straightforward and omitted.

  {\em \bfseries Global case.} Define a map $(g, W) \mapsto \rho_gW \in A$, from the
  submanifold of all $(g, W) \in {\mathcal G} \times A$ such that $g$ is an arrow
  beginning at the base point of $W$, using the right-hand side of \eqref{ext17}:
  \begin{equation*}
    \rho_{kh}W=\Adjoint^\tau_k \rho^{\mathcal H}_hW;\qquad k \in {\mathcal G}',\,h \in {\mathcal H}.
  \end{equation*}
  To show that there exists a unique Cartan connection $D$ on $A$ satisfying
  \eqref{ext17}, it suffices to show that $\rho$ is a representation, and that $\rho $
  extends the canonical representation of ${\mathcal G} $ on the anchor kernel of $A$:
  \begin{equation}
    \rho_gZ = \Adjoint_gZ\enspace\text{whenever $\#Z=0$}\label{ext18}
  \end{equation}
  and $g \in {\mathcal G} $ is an arrow beginning at the base point of $Z$.

  By the hypothesis \eqref{pony4}, \eqref{ext18} already holds for $g \in {\mathcal
    H}$. Since ${\mathcal G} ={\mathcal G}' {\mathcal H} $, to prove \eqref{ext18} in
  general, it suffices to prove
  \begin{equation}
    \Adjoint^\tau_k Z= \Adjoint_kZ\enspace\text{whenever $\#Z=0$, $k \in {\mathcal G}'$} .
  \end{equation}
  In fact, since ${\mathcal G}'$ has connected fibres, is suffices to prove the
  infinitesimalization,
  \begin{equation*}
          \adjoint^\tau_YZ = [Y, Z]\enspace\text{whenever $\#Z=0$, $Y \in A'$.}
  \end{equation*}
  But this true because both $Y$ and $Z$ here lie in the anchor kernel,
  $\adjoint^\tau_YZ:=\tau(Y,Z)$, and $\tau $ is model data.

  Since $\rho^{\mathcal H} $ and $\rho^{{\mathcal G}^1}$ are already representations, to
  show $\rho $ itself is a representation, it suffices to show, for any arrow
  $h \in {\mathcal H} $ beginning at some $m \in M$, that
  \begin{equation*}
    \rho^{\mathcal H}_h \rho^{{\mathcal G}^1}_k \rho^{\mathcal H}_{h^{-1}}W = \rho^{{\mathcal G}^1}_{hkh^{-1}}W,
  \end{equation*}
  where $k \in {\mathcal G}^1|_m$ and $W \in A|_{hm}$ are arbitrary. In fact, since
  ${\mathcal G}^1$ has connected fibres, it is enough to show the two Lie group
  homomorphisms ${\mathcal G}^1|_m \rightarrow \automorphism(A|_m)$ below have the same
  derivative:
  \begin{align*}
    k &\mapsto  \rho^{\mathcal H}_h \rho^{{\mathcal G}^1}_k \rho^{\mathcal H}_{h^{-1}}\\
    k &\mapsto  \rho^{{\mathcal G}^1}_{hkh^{-1}}.
  \end{align*}
  The readily computed derivatives are:
  \begin{align*}
    X &\mapsto \rho^{\mathcal H}_h \adjoint^\tau_X \rho^{\mathcal H}_{h^{-1}}(\,\cdot\,)
        = \rho^{\mathcal H}_h \tau(X, \rho^{\mathcal H}_{h^{-1}}(\,\cdot\,))\\
    \text{and}\quad X &\mapsto \adjoint^\tau_{\Adjoint_hX}(\,\cdot\,)=\tau(\Adjoint_hX, \,\cdot\,) =
                        \tau(\rho^{\mathcal H}_h X, \,\cdot\,),\quad\text{by \eqref{pony4}}.
  \end{align*}
  Equality of these derivatives follows from the $\rho^{\mathcal H}$-invariance of $\tau $.

  Proof of the remaining claims of the proposition is elementary and omitted.
\end{proof}

% Some of our notions of compatibility are summarized in Table 1.
% \begin{table}[]
% \centering
%   \begin{tabular}{@{}|c|c|c|c|@{}}
%   \toprule
%   compatibility of $\downarrow$ with $\rightarrow$ & $\tau$   & $\nabla$                        &  $\epsilon$\\ \midrule
%   filtration & $\tau(A^j, A^k) \subset A^{j+k}$ &  $A^j$ is $\bar\nabla$-invariant $\forall j$ & -   \\
%   $\tau$     &                                 &  $\tau $ is $\bar\nabla $-invariant  & $\graded_0(e)$ grades $\graded_T(A)$ \\
%   $\nabla $  &                                 &                                      &  $\epsilon$ is $\bar\nabla $-invariant \\  \bottomrule
% \end{tabular}
% \vspace{0.75\baselineskip}
% \caption{Summary of compatibility conditions for structures on a filtered Lie algebroid
%   $A$. Here $\tau $ model data, $T=\graded_0(\tau)$, $\nabla $ is an infinitesimal Cartan
%   connection, and $\epsilon$ a Weyl gauge.}
% \end{table}

\subsection{Gradings associated with model data}\label{model_data_gradings}

Let us say that model data $\tau$ is {\df compatible} with a Weyl gauge
$\epsilon \in \Gamma(A^0)$ if $E = \graded_0(\epsilon)$ is a fibre-wise grading element of
$\graded^T(A)$, $T=\graded_0(\tau)$, and not just of $\graded(A^0)=\graded^T(A^0)$.

Let $A$ be a filtered Lie algebroid admitting a Weyl gauge $\epsilon$. Then, according to
Theorem \ref{weyl}, we have an associated grading $A^0=\oplus_{i\ge 0}{\mathfrak a}_i$
that is invariant under the action of the isotropy subalgebroid $B \subset A$ of
$\epsilon$. If $\epsilon$ is compatible with model data $\tau$, that is itself compatible
with the filtration of $A$, then this grading extends to a grading
$A = \oplus_i {\mathfrak a}_i $, where $X \in {\mathfrak a}_j$ if and only if
$\tau(\epsilon, X) = jX$. This defines a splitting isomorphism
$\Phi_\epsilon \colon \graded^T(A) \rightarrow A$.

\begin{proposition} {\em \bfseries Infinitesimal case.} In the scenario above, let $\nabla $ be any
  infinitesimal Cartan connection weakly compatible with $\tau $. Then:
  \begin{conditions}
  \item The grading $A = \oplus_i {\mathfrak a}_i$ is invariant under the representation
    $\bar\nabla $ of $B$ on $A$.    \label{u4}
  \item For any $X \in \Gamma({\mathfrak a}_k)$, $k\ge 0$, and
    $Y \in \Gamma({\mathfrak a}_j)$, $j \in {\mathbb Z} $, one has
    $\bar\nabla_XY \in \Gamma({\mathfrak a}_j \oplus {\mathfrak a}_{j+k})$.\label{u3}
%  \item $\nabla $ is compatible with the filtration of $A$. \label{u7}
  \end{conditions}
  {\em\bfseries Global case.} If ${\mathcal G} $ is a weakly firm, filtered Lie groupoid with Lie
  algebroid $A$, $\epsilon$ is a Weyl gauge for ${\mathcal G} $ compatible with the model data
  $\tau $, and $D$ is a Cartan connection on ${\mathcal G} $ compatible with $\tau $,
  then:
  \begin{conditions}
  \item The grading $A=\oplus_i {\mathfrak a}_i$ associated with $\epsilon$ is invariant under
    the representation $\bar D $ of the isotropy subgroupoid
    ${\mathcal H}\subset {\mathcal G} $ of $\epsilon$.\label{uu4}
%  \item $D$ is compatible with the filtration of $A$.\label{uu7}
  \end{conditions}
\end{proposition}

The reader is warned that $B$ does not generally align itself with the complement
$\oplus_{i\le 0}{\mathfrak a}_i$ of $A^1=\oplus_{i\ge 1}{\mathfrak a}_i$ in $A$ defined by
the grading.  We may only conclude that $B$ is the graph of some linear function
$\oplus_{j\le 0} {\mathfrak a}_i \rightarrow A^1$ that vanishes on ${\mathfrak a}_0$,
which is necessarily contained in $B$.

\begin{corollary}
  If a (weakly firm) filtered Lie algebroid (resp., Lie groupoid) admits a Weyl gauge
  compatible with some model data $\tau $, then any Cartan connection weakly compatible with
  $\tau $ is compatible with the filtration.
\end{corollary}

\begin{proof}[Proof of corollary]
  If $\nabla $ is the Cartan connection in the Lie algebroid case, then
  $\bar\nabla$-invariance of the filtration of $A$ follows from \eqref{u4} and \eqref{u3},
  and the semi-direct product structure of $A$ (Theorem \eqrefs{weyl}{pq2}).

  For the Lie groupoid case and a global Cartan connection $D$, we know the filtration is
  $\bar\nabla $-invariant, where $\nabla $ is the infinitesimalization of $D$, from the
  Lie algebroid case just proven. In particular, continuing in the notation of the
  proposition, the restriction of $\bar\nabla $ to a representation of $A^1$ on $A$ is
  filtration-preserving. Therefore, the restriction of $\bar D$ to a representation of
  ${\mathcal G}^1$ is filtration-preserving, because ${\mathcal G}^1$ is source-connected.
  Full ${\bar D}$-invariance of the filtration follows from this fact, \eqref{uu4}, and
  the semi-direct product structure of $\mathcal G$ (Theorem \eqrefs{weyl2}{pr2}).
\end{proof}
%
\begin{proof}[Proof of proposition]
  Our proofs of \eqref{u4} and \eqref{u3} are variations on an argument appearing in the
  proof of Theorem \ref{weyl}.  Indeed, suppose that $Y \in \Gamma({\mathfrak a}_j)$ for
  some $j$ and let $X \in \Gamma(B)$ be arbitrary. Then, applying $\bar\nabla_X$ to both
  sides of the identity $\tau(\epsilon, Y) = jY$, and appealing to the
  $\bar\nabla$-invariance of $\tau$ (weak compatability), we have
\begin{equation*}
    \tau(\bar\nabla_{X}\epsilon, Y) + \tau(\epsilon, \bar\nabla_XY) = j \bar\nabla_XY.
\end{equation*}
But $\bar\nabla_{X} \epsilon = [X, \epsilon]$, because $\epsilon$ is in the anchor kernel, while $[X, \epsilon] = 0 $,
because $X \in \Gamma(B)$. We conclude that $\bar\nabla_XY \in \Gamma({\mathfrak
  a}_j)$. This proves \eqref{u4}.

Turning to \eqref{u3}, write $\bar\nabla_XY=\sum_iW_i$ for
  some $W_i \in \Gamma({\mathfrak a}_i)$, which implies
\begin{equation*}
    \tau(\epsilon, \bar\nabla_XY) = \sum_iiW_i.
\end{equation*}
On the other hand, $\tau(\epsilon, Y) = jY$, which, after applying $\bar\nabla_X$ to both
sides, and appealing to the $\bar\nabla$-invariance of $\tau $, becomes
\begin{equation*}
  \tau(\bar\nabla_X \epsilon, Y) + \tau(\epsilon, \bar\nabla_XY) = j\sum_iW_i.
\end{equation*}
As $X$ and $\epsilon$ are sections of $A^0$, we have
$\bar\nabla_X E = [X, \epsilon] = \tau(X, \epsilon) = -kX$. From this and the two preceding equations we
deduce
\begin{equation*}
   \sum_i(i-j)W_i + k \tau(Y, X) =0.
\end{equation*}
Since $A = \oplus_i {\mathfrak a}_i$ is a grading with respect to $\tau$, the last term on
the left-hand side is a section of $\Gamma({\mathfrak a}_{j+k})$. Projecting onto each
component ${\mathfrak a}_i$ of the grading $A = \oplus_i {\mathfrak a}_i$, we obtain
$W_i = 0$ for all $i$, with the possible exceptions $i=j, j+k$, which shows
$\bar\nabla_XY \in \Gamma({\mathfrak a}_j \oplus {\mathfrak a}_{j+k})$.

The proof of \eqref{uu4} is similar to that of \eqref{u4} above, following from the
$\bar D$-invariance of $\tau $, the definition of the spaces ${\mathfrak a}_j$, and the
fact that ${\mathcal H} $ fixes $\epsilon$.
\end{proof}

% \begin{corollary}
%   Every gauge transformation $\varphi \colon A \rightarrow A$ induces the identity in
%   homology $H_n(A^1, A) \rightarrow H_n(A^1, A)$.
% \end{corollary}

\refreshpage
\section{Filtered Cartan geometries}\label{filtered_cartan}
Suppose ${\mathcal G} $ is a firmly filtered Lie groupoid, with Lie algebroid $A$,
supporting a Cartan connection $D$ compatible with the filtration, and model data $\tau $
compatible with the filtration. Then we call $({\mathcal G}, D, \tau)$ a {\df filtered
  Cartan geometry} if:
\begin{conditions}
   \item $\tau $ is compatible with $D$ (in the sense of \ref{preview}).
   \item ${\mathcal G}$ admits a Weyl gauge compatible with $\tau $.\label{fc2}
\end{conditions}
Because we assume ${\mathcal G} $ is firmly filtered, \eqref{fc2} just means
${\mathcal G}$ admits an $\Adjoint$-invariant, fibre-wise grading section of
$\graded^T(A)$, where $T:=\graded_0(\tau)$ (Corollary \ref{weyl2}). There is no
requirement here that $\tau $ be reductive or semisimple, and such notions will play no
role in the current section. However, Proposition \ref{all}, stated later, shows that every
parabolic geometry is a filtered Cartan geometry.

If we only have a firmly filtered Lie algebroid $A$, and an infinitesimal Cartan
connection $\nabla$, compatible with the filtration and compatible with $\tau $,
and if $A$ admits a $\tau$-compatible Weyl gauge, then $(A, \nabla, \tau)$ is an {\df
  infinitesimal filtered Cartan geometry}.

In this section, we provide a general, explicit, description of {\em transitive}, filtered
Cartan geometries, by exploiting theorems on semi-direct product structure established in
Section \ref{semi-direct}. In this description, we specify the additional data needed to
recover a transitive Cartan geometry from its (abstract) Levi reduction. While we are
mainly interested in the special parabolic case, the extra abstraction introduced here
emphasizes Weyl gauges as the essential actor in the resulting characterization.

\subsection{Abstract Levi structures: the infinitesimal case}\label{inflevi}
The reduction procedure described for parabolic geometries in \ref{reduction_} generalizes
to transitive filtered Cartan geometries. We begin with the infinitesimal case.

Let $(A, \nabla, \tau)$ be a transitive infinitesimal filtered Cartan geometry. Since $A$
is firmly filtered, the canonical representation $\adjoint$ of $A$ on $A^0$, in which
$A^1$ is acting trivially, descends to a representation $\adjoint$ of $B:=A/A^1$ on
$\graded(A^0)$. This canonical representation is extended by a representation of $B$ on
$\graded(A)$, induced by the representation $\bar\nabla $ of $A$ on itself, and we denote
this by $R^\nabla$. If we write ${\mathfrak a}_j:=\graded(A)_j$ for $j>0$, then using the
transitivity we can write
\begin{conditions}
  \item[{\bfseries C0.}]
  \quad $\graded(A) \cong \graded(TM)\oplus B^0 \oplus (\oplus_{j>0}{\mathfrak a}_j)$.
\end{conditions}
In addition to the grading-preserving representation $R^\nabla$ on the above, we have the
Lie algebra bundle bracket $T := \graded_0(\tau)$ which, on account of the compatibility
Axiom c2, shows that
\begin{equation}
  \label{form_}
  T(C, V) = R^\nabla_C V,\quad
  T(C, Z) = R^\nabla_C Z,\quad
  T(C, C') = [C,C'],
\end{equation}
whenever $C,C'\in\Gamma(B^0)$, $V\in \Gamma(\graded(TM))$,
$Z \in \Gamma(\oplus_{j>0} {\mathfrak a}_j)$. The last equation holds because $\tau$
extends the canonical bracket on $A^0$. Note $R^\nabla Z$ does not actually depend on
$\nabla $, because it is determined by the canonical representation of $A$ on $A^1$.

Motivated by the above, an {\df abstract infinitesimal Levi structure} will be a 4-tuple
$(B, \oplus_{j>0} {\mathfrak a}_j, R, T)$, where:
\begin{conditions}
  \item $B$ is a transitive, filtered Lie algebroid over $M$ with $B \le 0$ and with $B^0$
    as its anchor kernel.
  \item $\oplus_{j>0}{\mathfrak a}_j$ is a graded vector bundle over $M$, with
    ${\mathfrak a}_j=0$ for all sufficiently large $j$.
  \item $R$ is a a grading-preserving representation of $B$ on C0 that extends
    the canonical action of $B$ on $B^0$
  \item\label{chh0} $T$ is an $R$-invariant Lie algebra bundle structure on C0
    compatible with the obvious grading and satisfying
    \begin{equation*}
      T(C, V) = R_C V,\quad
      T(C, Z) = R_C Z,\quad
      T(C, C') = [C,C'],
    \end{equation*}
    whenever $C,C'\in\Gamma(B^0)$, $V\in \Gamma(\graded(TM))$,
    $Z \in \Gamma(\oplus_{j>0} {\mathfrak a}_j)$.
  \item\label{six} As a graded Lie algebra bundle, C0 admits an $R$-invariant grading section,
    necessarily of the form $(0, E, 0)$, for some $E \in \Gamma(B^0)$, where $E$ is required to
    commute with arbitrary sections of $B$.
\end{conditions}
\noindent Note that it is not required that $T$ restrict to the canonical Lie algebra
bundle structure on $\graded(TM)$. If this restriction is the {\em negative} of the
canonical one, then the Levi structure is {\df regular}.

According to the immediately preceding observations, associated with every transitive
infinitesimal filtered Cartan geometry is an infinitesimal Levi structure, called its {\df
  Levi reduction}, regular if the filtered Cartan geometry is regular.

\subsection{Abstract Levi structures: the global case}\label{abstract_levi}%
\mbox{}\newline
\noindent%
An {\df abstract Levi structure} is a 4-tuple
$({\mathcal H}, \oplus_{j>0}{\mathfrak a}_j, R, T)$ where:
\begin{conditions}
  \item ${\mathcal H} $ is a transitive, filtered Lie groupoid over $M$ with Lie algebroid
    $B$, whose anchor kernel is $B^0$, and with $B \le 0$.
  \item $\oplus_{j>0}{\mathfrak a}_j$ is a graded vector bundle over $M$, with
    ${\mathfrak a}_j=0$ for all sufficiently large $j$.
  \item $R$ is a grading-preserving representation of ${\mathcal H}$ on
    C0 that extends the canonical action of ${\mathcal H}$ on $B^0$.
   \item\label{chh00} $T$ an $R$-invariant Lie algebra bundle structure on
    C0 compatible with the grading, and such that
    \begin{equation*}
      T(C, V) = dR_C V,\quad
      T(C, Z) = dR_C Z,\quad
      T(C, C') = [C,C'],
    \end{equation*}
    for all $C,C'\in\Gamma(B^0)$, $V\in \Gamma(\graded(TM))$,
    $Z \in \Gamma(\oplus_{j>0} {\mathfrak a}_j)$.
  \item\label{five} As a graded Lie algebra bundle, C0 admits an $R$-invariant grading
    section, necessarily of the form $(0, E, 0)$, for some $E \in \Gamma(B^0)$, where $E$
    is required to be ${\mathcal H} $-invariant.
\end{conditions}
Here $dR$ is the infinitesimalization of the representation $R$. The structure is {\df
  regular} if its infinitesimalization $(B,\oplus_{j>0}{\mathfrak a}_j, dR, T)$ is
regular.  %

In analogy with our observations in \ref{inflevi}, we can associate with each transitive
filtered Cartan geometry $({\mathcal G}, D, \tau)$ an abstract Levi structure
$({\mathcal G}/{\mathcal G}^1, \graded(A^1), R^D, \graded_0(\tau))$ that we call its {\df
  Levi reduction}. It is regular if $({\mathcal G}, D, \tau)$ is. Here $R^D$ is the
representation of ${\mathcal G}/{\mathcal G}^1$ induced by the representation $\bar D$ of
${\mathcal G} $ on the Lie algebroid $A$ of ${\mathcal G} $.

\subsection{Morphisms}\label{morphisms}
A {\df morphism} of filtered Lie algebroids $q \colon A \rightarrow \tilde A$ is a Lie
algebroid morphism respecting the filtrations: $q(A^j) \subset \tilde A^j$. A {\df
  morphism} of filtered Lie groupoids
$Q \colon {\mathcal G} \rightarrow \tilde {\mathcal G} $ is a Lie groupoid morphism whose
infinitesimalization $q=dQ \colon A \rightarrow \tilde A$ is a morphism of firmly filtered
Lie algebroids. (Infinitesimal) Weyl gauge transformations are examples of automorphisms
of a filtered Lie groupoid (resp., Lie algebroid). We obtain the category of {\em firmly}
filtered Lie algebroids or Lie groupoids by simply restricting the class of morphisms to
those whose source and target are firmly filtered objects.

For simplicity, and as it will suffice for current purposes, we only define morphisms for
filtered Cartan geometries that are isomorphisms. A {\df morphism} of infinitesimal filtered
Cartan geometries
$$(A, \tau, \nabla) \rightarrow (\tilde A, \tilde \tau, \tilde \nabla)$$ is an isomorphism of
underlying filtered Lie algebroids such that $\tau$ and $\nabla $ push forward to
$\tilde \tau $ and $\tilde \nabla $; since $q$ is an isomorphism, pushing forward makes
sense.  A {\df morphism} of global filtered Cartan geometries $({\mathcal G}, \tau, D)$
and $(\tilde {\mathcal G}, \tilde \tau, \tilde D)$ is an isomorphism of underlying
filtered Lie groupoids that pushes $\tau $ and $D $ to $\tilde \tau$
and $\tilde D $.

A morphism of abstract infinitesimal Levi structures
$$(B, \oplus_{j>0} {\mathfrak a}_j, R, T) \rightarrow
(\tilde B, \oplus_{j>0} \tilde{\mathfrak a}_j, \tilde R, \tilde T)$$
consists of a pair $(q, \omega)$, where $q \colon B \rightarrow \tilde B$ is morphism of
filtered Lie algebroids, covering some smooth map $f \colon M \rightarrow \tilde M$, and
$\omega \colon \oplus_{j>0}{\mathfrak a}_j \rightarrow \oplus_{j>0}\tilde{\mathfrak a}_j$
a morphism of graded vector bundles, such that induced morphisms of graded vector bundles
\begin{gather*}
  (q, \omega)_* \colon \graded(TM)\oplus B^0 \oplus (\oplus_{j>0}{\mathfrak a}_j)
     \rightarrow \graded(TM)\oplus \tilde B^0 \oplus (\oplus_{j>0}\tilde{\mathfrak a}_j)\\
  (V, C, Z) \mapsto (\graded_0(Tf)(V), qC, \omega Z)
\end{gather*}
is: (i) a morphism of Lie algebra bundles, with respect to the brackets $T$ and
$\tilde T$; and (ii) an intertwining of the representations $R$ and $\tilde R$. Here
$Tf \colon TM \rightarrow TM$ is the tangent map of $f$, which will necessarily be
filtration-preserving because $\# \circ q = Tf \circ \#$. A morphism of abstract Levi
structures $({\mathcal H}, \oplus_{j>0}{\mathfrak a}_j, R, T)$ and
$(\tilde {\mathcal H}, \oplus_{j>0}\tilde{\mathfrak a}_j, \tilde R, \tilde T)$ is a pair
$(Q, \omega)$, where $Q \colon {\mathcal H} \rightarrow \tilde {\mathcal H} $ is morphism
of filtered Lie groupoids and
$\omega \colon \oplus_{j>0}{\mathfrak a}_j \rightarrow \oplus_{j>0}\tilde{\mathfrak a}_j$
a morphism of graded vector bundles, such that: (i) $(dQ, \omega)$ is a morphism of the
corresponding abstract infinitesimal Levi structures; and (ii) $(dQ, \omega)_*$
intertwines the (global) representations $R$ and $\tilde R$.

As it turns out, for the applications we have in mind, only morphisms of infinitesimal or
global Levi structures covering the identity on $M$ will be relevant, in which case $f$
above is just the identity.

\subsection{Consequences of the semi-direct product structure}\label{consequences}%
Beginning our analysis with the infinitesimal case, suppose $(A, \nabla, \tau)$ is a
transitive infinitesimal filtered Cartan geometry such that $A^0$ is the anchor kernel, and let
$\epsilon $ be a $\tau$-compatible gauge. According to Theorem \ref{weyl}, we may suppose,
without loss of generality, that $A$ is the semi-direct product of a transitive, filtered
Lie algebroid $B$, with $|B| \le 0$ and anchor $B^0$, with a filtered Lie algebra bundle
$\oplus_{j>0}{\mathfrak a}_j$, on which $B $ is acting, an action that preserves the
grading. Moreover, if we denote the action of $B$ on $\oplus_{j>0}{\mathfrak a}_j$ by $R$,
so that $A = B \oplus_R(\oplus_{j>0}{\mathfrak a}_j)$, then we know there exists a section
$E$ of $B^0$ such that:
\begin{gather*}
  [E, X]=0\quad \text{for all $X \in \Gamma(B)$}\\
  R_EY = jY\quad\text{for all $Y \in \Gamma({\mathfrak a}_j)$, $j>0$}.\\
  \epsilon = (E, 0) \in \Gamma(A).
\end{gather*}
The Weyl gauge determines a grading $A = \oplus_i {\mathfrak a}'_i$, where
${\mathfrak a}'_i$ is the kernel of
$X \mapsto \tau(E,X) - iX \colon A^i \rightarrow A^{i+1}$.

In general, ${\mathfrak a}'_k \subset B \oplus 0$ does not hold for $k <0$. However,
noting that the filtration of $A=B\oplus_R (\oplus_{j>0}{\mathfrak a}_j)$ is defined by
$A^i = B^i \oplus_R(\oplus_{j\ge\max\{1,i\}}{\mathfrak a}_j)$, it is not hard to see,
from the identities above, that ${\mathfrak a}'_0=B^0 \oplus 0$ and
${\mathfrak a}'_j=0\oplus{\mathfrak a}_j$ for $j> 0$.  From this we may deduce that the
splitting isomorphism $\Phi\colon \graded(A) \rightarrow A$ induced by the grading
$A = \oplus_i {\mathfrak a}'_i$ has the form
\begin{gather*}
    \Phi \colon \graded(TM) \oplus B^0 \oplus (\oplus_{j>0} {\mathfrak a}_j)
    \rightarrow B\oplus_R(\oplus_{j>0}{\mathfrak a}_j)\\
    (V, C, Z) \mapsto (C + \tilde \sigma (V), Z - \mathsf{P}(V)),
\end{gather*}
for some $\mathsf{P} \subset \Gamma(\graded(T^*\!M)\otimes(\oplus_{j>0}{\mathfrak a}_j))$,
and some vector bundle map $\tilde \sigma \colon \graded(TM) \rightarrow B$ satisfying
\begin{equation*}
  \tilde \sigma(\graded(TM)_k) \subset B^k\enspace\text{and}\enspace
    \graded_k(\# \tilde \sigma (V)) = V \quad\text{for all $V \in \graded(TM)_k$, $k < 0$}.
\end{equation*}
Here $\# \colon B \rightarrow TM$ denotes the anchor. This is just linear algebra and an
unpacking of the implicit identification
${\mathfrak a}_k\cong\graded(A)_k \cong \graded(TM)_k$ for $k < 0$.

The composite $\sigma=\#\circ\tilde\sigma $ satisfies
\begin{equation*}
  \sigma(\graded(TM)_k) \subset T^kM\enspace\text{and}\enspace
    \graded_k(\sigma (V)) = V \quad\text{for all $V \in \graded(TM)_k$, $k < 0$}.
\end{equation*}
We call such $\sigma \colon \graded(TM) \rightarrow TM $, which is necessarily an
isomorphism, a {\df splitting} of the filtered manifold $M$. The composite
$s = \tilde \sigma \circ \sigma^{-1} \colon TM \rightarrow B$ is a right-inverse for the
anchor $\# \colon B \rightarrow TM$, which we will call a {\df splitting of the anchor of $B$}. We
may now rewrite our formula for $\Phi $ as
\begin{conditions}\item[{\bfseries S1.}]
  \quad $\Phi(V, C, Z) = (C + s(\sigma(V)), Z - \mathsf{P}(V))$.
\end{conditions}
By construction, the model data $\tau $ is the push-forward of $T:=\graded_0(\tau)$ under
$\Phi $:
\begin{conditions}\item[{\bfseries S2.}]
  \quad $\tau(\Phi(\xi_1), \Phi(\xi_2)) = \Phi(T(\xi_1, \xi_2))$,
\end{conditions}
for $\xi_1,\,\xi_2 \in \graded(TM)\oplus B \oplus_R(\oplus_{j>0}{\mathfrak a}_j)$, and
$(0, E, 0)$ is a fibre-wise grading section of
$\graded(TM) \oplus B^0 \oplus (\oplus_j {\mathfrak a}_j)$, for the Lie bracket $T$.  To
complete our analysis, we derive a formula for the self-representation $\bar\nabla $ of
$A$, which characterizes the connection $\nabla$, because $A$ is transitive (Proposition
\ref{hsd}).  Since Proposition \ref{model_data_gradings} applies, the grading
$A=\oplus_i {\mathfrak a}'_i$ (there denoted $\oplus_i {\mathfrak a}_i$) is
$\bar\nabla_{(X,0)}$-invariant, for every section $X$ of $B$.  It follows that $\Phi $
intertwines some grading-preserving representation $R$ of $B$ on
$\graded(A)=\graded(TM)\oplus B^0 \oplus (\oplus_{j>0}{\mathfrak a}_j)$ with the
$\bar\nabla$-representation of $B \oplus 0$ on $A$:
\begin{equation*}
  \bar\nabla_{(X, 0)} \Big(\,\Phi(V,C,Z)\,\Big) = \Phi\Big(\,R_X(V, C, Z)\,\Big);\quad X \in B.
\end{equation*}
It's not hard to see that $R$ on the right is the same thing as $R^\nabla $, as defined in
\ref{inflevi} above, under the identification $B \oplus 0 \cong A/A^1$. As a consequence
we can write this as
\begin{equation}
    \bar\nabla_{(X, 0)} \Big(\,\Phi(V,C,Z)\,\Big)=\Phi(R_XV, [X,C], R_X Z),\label{groof}
\end{equation}
where the ``$R$\,'' in $R_XZ$ has the meaning assigned to it in the beginning of the
current discussion, and with
\begin{equation*}
  T(C, V) = R_C V,\quad
  T(C, Z) = R_C Z,\quad
  T(C, C') = [C,C'],
\end{equation*}
for all $C,C'\in\Gamma(B^0)$, $V\in \Gamma(\graded(TM))$,
$Z \in \Gamma(\oplus_{j>0} {\mathfrak a}_j)$.

On the other hand, for any $Y \in \Gamma(\oplus_{j>0}{\mathfrak a}_j)$, we have
$\Phi(0,0,Y)=(0,Y)$, so compatibility Axiom c2 leads to
\begin{align}
  \bar\nabla_{(0, Y)} \Big(\,\Phi(V, C, Z)\,\Big)
  &=\tau\Big(\,\Phi(0, 0, Y),\,\Phi(V, C, Z)\,\Big) =
    \Phi\Big(\,T((0, 0, Y), (V, C, Z))\,\Big)\label{cab0}\\
  &=\Phi\Big(\,(0,0,[Y,Z] - R_CY) + T(Y, V)\,\Big);
    \quad Y \in \Gamma(\oplus_{j>0}{\mathfrak a}_j).\notag
\end{align}
Combining this last with \eqref{groof}, we have, for any
$(X, Y) \in \Gamma(B \oplus_R(\oplus_{j>0} {\mathfrak a}_j))$,
\begin{conditions}\item[{\bfseries S3.}]
  \quad $\bar\nabla_{(X,Y)}\Phi(V, C, Z)
  =\Phi\Big(\,R_X(V, C, Z) + T((0, 0, Y), (V, C, Z))\,\Big)$,
\end{conditions}
whose right-hand side can also be written as
$$\Phi\Big(\,(R_XV, [X,C], [Y,Z] +R_XZ - R_CY) + T(Y, V)\,\Big).$$

The above analysis leads to the characterizations of transitive filtered Cartan geometries
given next.

\subsection{Prolongation: the infinitesimal case}\label{inflevi_}
Suppose that $(B, \oplus_{j>0}{\mathfrak a}_j, R, T)$ is an abstract infinitesimal Levi
structure. The structure $T$ makes $\oplus_{j>0}{\mathfrak a}_j$ into a graded Lie algebra
bundle and the {\df prolongation} of the abstract infinitesimal Levi structure is
the Lie algebroid semi-direct product $A = B \oplus_R(\oplus_{j>0}{\mathfrak a}_j)$. This
is a firmly filtered Lie algebroid with
$A^i = B^i \oplus_R(\oplus_{j\ge\max\{1,i\}}{\mathfrak a}_j)$.

\begin{theorem}[A characterization of transitive infinitesimal filtered Cartan geometries]
  Let $(B, \oplus_{j>0}{\mathfrak a}_j, R, T)$ be an abstract infinitesimal Levi structure,
  $\mathsf{P}$ be an arbitrary section of
  $\graded(T^*\!M)\otimes(\oplus_{j>0}{\mathfrak a}_j)$, $s \colon TM \rightarrow B$ any
  splitting of the anchor of $B$, and $\sigma \colon \graded(TM) \rightarrow TM $ some
  splitting of the filtered manifold $M$. Then:
  \begin{conditions}
  \item The map
    $\Phi \colon \graded(TM) \oplus B^0 \oplus (\oplus_j {\mathfrak a}_j) \rightarrow B
    \oplus_R(\oplus_{j>0}{\mathfrak a}_j)$ defined by {\normalfont S1} is
    invertible. Specifically, if $\pi \colon B \rightarrow B^0$ is defined by
    $\pi(X):=X - s(\#X)$, and if $(X, Y) = \Phi(V, C, Z)$, then $C = \pi X$,
    $V = \sigma^{-1}(\#X)$, and $Z = Y + \mathsf{P}(V)$. \label{chh1}
  \item\label{chh2} The prolongation $A = B \oplus_R(\oplus_{j>0}{\mathfrak a}_j) $ is a
    transitive, infinitesimal, filtered Cartan geometry, with model data $\tau $ defined
    by {\normalfont S2} and Cartan connection $\nabla $ uniquely determined by
    {\normalfont S3}. The corresponding Levi reduction is isomorphic to
    $(B, \oplus_{j>0}{\mathfrak a}_j, R, T)$.
  \item\label{cch2b} For any section $E$ as in \eqrefs{inflevi}{six},
    $\epsilon := \Phi^{-1}(0, E, 0)$ is a Weyl gauge for $A$ compatible with $\tau $ and
    for which $\Phi \colon \graded(A) \rightarrow A$ is the corresponding splitting.
  \item\label{cch3} Every transitive, infinitesimal, filtered Cartan geometry
    $(A, \nabla, \tau)$, with anchor kernel $A^0$, is, up to isomorphism, the prolongation
    of its Levi reduction, with Cartan connection $\nabla $ and model data $\tau $ of the
    form just described.
  \end{conditions}
\end{theorem}
\noindent%
The section $\mathrm P$ is called the {\df Rho tensor}.
\begin{proof}
  It is a triviality that $\Phi $ is injective. A dimension count implies $\Phi$ must be an
  isomorphism. A substitution verifies the rest of \eqref{chh1}.

  That $\tau $, defined by S2, is model data follows from the properties of $T$ posited in
  \eqrefs{inflevi}{chh0} and the definition of the semi-direct product Lie bracket for
  $B^0 \oplus_R(\oplus_{j>0} {\mathfrak a}_j)$.

  The isomorphism $\Phi$ intertwines the representation $R$ of $B$ on
  $\graded(TM) \oplus B^0 \oplus (\oplus_j {\mathfrak a}_j)$ with some representation
  $\rho^{B \oplus 0}$ of $B \oplus 0 \subset A$ on $A$:
  \begin{equation}
    \rho^{B \oplus 0}_{(X,0)}\Phi(V, C, Z) = \Phi\Big(\,R_X((V, C, Z))\,\Big).\label{ret1}
  \end{equation}
  To apply Proposition \ref{constructing} to $A$, with $\tau $ defined by
  S2, and $A'=A^1=0 \oplus (\oplus_{j>0} {\mathfrak a}_j)$, we need to
  establish \eqrefs{constructing}{ext1}. Here this means verifying that
  \begin{equation*}
    \rho^{B \oplus 0}_{(X,0)}\Phi(0, C, Z) = [(X,0), \Phi(0, C, Z)],
  \end{equation*}
  for $X \in \Gamma(B),\,C \in B^0,\,Z \in \Gamma(\oplus_{j>0}{\mathfrak a}_j)$, which is
  an easy computation following from \eqref{ret1}, and the fact that the bracket on the
  right-hand side is the semi-direct product bracket. Similarly, since $\tau $ is defined
  by S2, the properties of $T$ in \eqrefs{inflevi}{chh0} allow one to show that
  \eqrefs{constructing}{ext3} also holds in the present case. We conclude that there
  exists a unique Cartan connection $\nabla $ on $A$, compatible with $\tau $,
  such that
  \begin{equation*}
    \bar\nabla_{(X,Y)} \Phi(V, C, Z) = \rho^{B \oplus 0}_{(X,0)} \Phi (V, C, Z)
      + \tau((0,Y), \Phi(V, C, Z)).
  \end{equation*}
  The formula S3 follows from \eqref{ret1}, S2, and the identity $(0, Y) = \Phi(0, 0,
  Y)$. The last part of \eqref{chh2}, and \eqref{cch2b}, follow by construction. Part
  \eqref{cch3} of the theorem was already established in \ref{consequences}.
\end{proof}

\subsection{Prolongation: the global case}\label{abstract_levi_}
Suppose that $({\mathcal H}, \oplus_{j>0}{\mathfrak a}_j, R, T)$ is an abstract Levi
structure. The vector bundle $\oplus_{j>0} {\mathfrak a}_j$ gets an $R$-invariant graded
Lie algebra bundle structure by restricting $T$. This bundle has a necessarily nilpotent
Lie algebra model, and we let $\exp(\oplus_{j>0}{\mathfrak a}_j)$ denote the nilpotent Lie
group bundle with simply connected fibres that integrates $ \oplus_{j>0}{\mathfrak
  a}_j$. The restriction of $R$ to a representation of ${\mathcal H} $ on
$\oplus_{j>0}{\mathfrak a}_j$, by fibre-wise Lie algebra derivations, integrates to a
representation of ${\mathcal H}$ on $\exp(\oplus_{j>0}{\mathfrak a}_j)$ by fibre-wise Lie
group isomorphisms; denoting this by $R$ also, we have $R_h(\exp(Y))=\exp(R_hY)$, for any
arrow $h \in {\mathcal H}$ beginning at the base point of
$Y \in \oplus_{j>0}{\mathfrak a}_j $, because $\exp$ is a diffeomorphism in this case.

The {\df prolongation} of the Levi structure is the Lie groupoid semi-direct
product ${\mathcal G} = {\mathcal H} \times_R\exp(\oplus_{j>0}{\mathfrak a}_j)$. This is
a filtered Lie groupoid with Lie algebroid $B \oplus_{dR} (\oplus_{j>0}{\mathfrak a}_j)$,
the prolongation of Levi structure's infinitesimalization.

Additionally, the representation $\adjoint^T$ of the nilpotent Lie algebra bundle
$\oplus_{j>0}{\mathfrak a}_j$ on
$\graded(TM) \oplus B^0 \oplus (\oplus_{j>0}{\mathfrak a}_j)$ integrates to a
representation of the Lie group bundle $\exp(\oplus_{j>0}{\mathfrak a}_j)$ on
$\graded(TM) \oplus B^0 \oplus (\oplus_{j>0}{\mathfrak a}_j)$. We denote this
representation by $\Adjoint^T$.

\begin{theorem}[A characterization of transitive filtered Cartan geometries]\mbox{}\newline
  Let $({\mathcal H}, \oplus_{j>0}{\mathfrak a}_j, R, T)$ be an abstract Levi structure,
  $B$ the Lie algebroid of ${\mathcal H} $, $\mathsf{P}$ an arbitrary section of
  $\graded(T^*\!M)\otimes(\oplus_{j>0}{\mathfrak a}_j)$, $s \colon TM \rightarrow B$ any
  splitting of the anchor of $B$, and $\sigma \colon \graded(TM) \rightarrow TM $ some
  splitting of the filtered manifold $M$. Then:
  \begin{conditions}
  \item\label{chh01} The map
    $\Phi \colon \graded(TM) \oplus B^0 \oplus (\oplus_j {\mathfrak a}_j) \rightarrow B
    \oplus_{dR}(\oplus_{j>0}{\mathfrak a}_j)$ defined by {\normalfont S1} is
    invertible.
  \item\label{chh02} The prolongation
    ${\mathcal G}  = {\mathcal H} \times_R\exp(\oplus_{j>0}{\mathfrak a}_j) $ is a transitive,
    filtered Cartan geometry, with model data $\tau $ defined by
    {\normalfont S2} and Cartan connection $D$ uniquely determined by
  \item[{\normalfont\bfseries S3$^\prime$.}]  \vspace{0.3\baselineskip} \quad
    $\bar D_{(h,k)}\Phi(V, C, Z) = \Phi(\Adjoint^T_k(R_hV, \Adjoint_h C, R_h Z))$.
    \vspace{0.3\baselineskip}\newline The corresponding Levi reduction is isomorphic to
    $({\mathcal H}, \oplus_{j>0}{\mathfrak a}_j, R, T)$.
  \item\label{chh02b} For any section $E$ as in \eqrefs{abstract_levi}{five},
    $\epsilon = \Phi^{-1}(0, E, 0)$ is a Weyl gauge for ${\mathcal G} $ compatible with
    $\tau$ and for which $\Phi \colon \graded(A) \rightarrow A$ is the corresponding
    splitting.
  \item\label{cch03}
    \vspace{0.5\baselineskip}
    Every transitive, filtered, Cartan geometry
    $({\mathcal G}, D, \tau)$, with Lie algebroid $A$ and anchor kernel $A^0$, is, up to
    isomorphism, the prolongation of some abstract Levi structure, with Cartan
    connection $D $ and model data $\tau $ of the form just described.
  \end{conditions}
\end{theorem}
\begin{proof}
  The preceding infinitesimal result, Theorem \ref{inflevi_}, applies with $R$ there
  replaced with $dR$. In particular, \eqref{chh01} is just a restatement of
  \eqrefs{inflevi_}{chh1}.

  The isomorphism $\Phi$ intertwines the representation $R$ of ${\mathcal H} $ on
  $\graded(TM) \oplus B^0 \oplus (\oplus_j {\mathfrak a}_j)$ with some representation
  $\rho^{{\mathcal H} \times \identity}$ on
  ${\mathcal H} \times \identity \subset {\mathcal G} $ on
  $A = B\oplus_{dR}(\oplus_{j>0}{\mathfrak a}_j) $:
  \begin{equation}
    \rho^{{\mathcal H} \times \identity}_{(h,\identity)}\Phi(V, C, Z) =
      \Phi\Big(\,R_h((V, C, Z))\,\Big).\label{ret01}
  \end{equation}
  To apply the global case of Proposition \ref{constructing} to ${\mathcal G}$, with
  $\tau $ defined by S2, and
  ${\mathcal G}'=\identity \times \exp(\oplus_{j>0} {\mathfrak a}_j)$, we
  need to establish \eqrefs{constructing}{pony4}. Here this means verifying that
  \begin{equation*}
    \rho^{{\mathcal H} \times \identity}_{(h,\identity)}\Phi(0, C, Z) =
    \Adjoint_{(h,\identity)}\Phi(0, C, Z),
  \end{equation*}
  for each arrow $h \in {\mathcal G}$ beginning as some $m \in M$, $C \in B^0|_m$,
  $Z \in \oplus_{j>0}{\mathfrak a}_j|_m$. With the help of \eqref{ret01}, and the
  definition of $\Adjoint$ for semi-direct products, this is readily checked. We conclude
  that there exists a unique Cartan connection $D$ on ${\mathcal G} $, at least weakly
  compatible with $\tau$, such that
  \begin{equation}
    \label{mask1}
    \bar D_{(h,k)}\Phi(V, C, Z) =
       \Adjoint^\tau_{(\identity,k)}\rho^{{\mathcal H}\times \identity}_{(h,\identity)}\Phi(V, C, Z),
  \end{equation}
  where $\Adjoint^\tau$ is the representation of
  $\identity \times \exp(\oplus_{j>0}{\mathfrak a}_j) \subset {\mathcal G} $ on $A$
  integrating the representation $\adjoint^\tau$ of
  $A^1=0\oplus (\oplus_{j>0}{\mathfrak a}_j)$ on $A$ defined by
  $\adjoint^\tau_{(0,Y)}W = \tau((0,Y), W)$. By the definition of $\tau $, the isomorphism
  $\Phi $ intertwines the representation $\adjoint^\tau$ of $A^1$ with the representation
  $Y \mapsto T((0,0,Y),\,\cdot\,)$ of $\oplus_{j>0}{\mathfrak a}_j$. Consequently, as
  $\exp(\oplus_{j>0}{\mathfrak a}_j)$ has connected fibres, $\Phi $ intertwines the
  representations $\Adjoint^\tau$ and $\Adjoint^T$:
  \begin{equation}
    \label{mask2}
    \Adjoint^\tau_{(\identity, k)}\Phi(V, C, Z) = \Phi(\Adjoint^T_k((V, C, Z)).
  \end{equation}
  Combining \eqref{ret01}, \eqref{mask1} and \eqref{mask2}, we obtain S3${}^\prime$. The
  last part of \eqref{chh02}, and \eqref{chh02b}, follow by construction.

  It is easy to see that the infinitesimalization $\nabla $ of $D$ must be the Cartan
  connection delivered by Theorem \ref{inflevi_}. Since $\nabla $ is {\em strongly}
  compatible with $\tau $, $D$ is also.

  Turning to \eqref{cch03}, let $({\mathcal G}, D, \tau)$ be a transitive, filtered, Cartan
  geometry with Lie algebroid $A$ and anchor kernel $A^0$. By Theorem \eqrefs{weyl2}{pr5},
  we may suppose, without loss of generality, that
  ${\mathcal G} = {\mathcal H} \times_R\exp(\oplus_{j>0}{\mathfrak a}_j)$, for some
  filtered Lie groupoid ${\mathcal H}$ and graded Lie algebra bundle
  $\oplus_{j>0}{\mathfrak a}_j$, where ${\mathcal H} $ acts on
  $\oplus_{j>0}{\mathfrak a}_j$ by grading-preserving fibre-wise derivations, an action
  that integrates to an action of ${\mathcal H} $ on $\exp(\oplus_{j>0}{\mathfrak a}_j)$
  by fibre-wise Lie group isomorphisms, both actions to be denoted $R$. Moreover, the Lie
  algebroid $B$ of ${\mathcal H} $ will satisfy $B^j=0$ for $j>0$ and, by our hypotheses
  on $A$, $B$ is transitive with $B^0$ being the anchor kernel.

  Evidently, $A$ is identifiable with $B \oplus_{dR}(\oplus_{j>0}{\mathfrak a}_j)$,
  which the infinitesimalization $\nabla $ of $D$ makes into a transitive, infinitesimal,
  filtered Cartan geometry. Consequently, the analysis of \ref{consequences} applies, with
  $R$ in that analysis replaced with $dR$. Define ${\mathfrak a}'_j $, $j>0$, and $\Phi$
  as in that analysis. Then $\tau $ can be recovered from $T=\graded_0(\tau)$ according to
  S2, and, according to Proposition
  \eqrefs{model_data_gradings}{uu4}, the grading $A=\oplus_i {\mathfrak a}'_i$ (there
  denoted $\oplus_i {\mathfrak a}_i$) is $\bar D_{(h,\identity)}$-invariant, for every
  $h \in {\mathcal H} $. It follows that $\Phi $ intertwines some grading-preserving
  representation $R$ of ${\mathcal H}$ on
  $\graded(A)=\graded(TM)\oplus B^0 \oplus (\oplus_{j>0}{\mathfrak a}_j)$ with the
  $\bar D$-representation of ${\mathcal H} \times \identity$ on $A$:
  \begin{equation}
    \bar D_{(h, \identity)} \Phi(V,C,Z) = \Phi\Big(\,R_h(V, C, Z)\,\Big);\quad h \in {\mathcal H}.
  \end{equation}
  Since $\Phi(0, C, Z) = (C, Z)$ and $\bar D $ is just the canonical
  representation on sections of $A^0$, $R$ must extend the canonical representation of
  ${\mathcal H}$ on $\graded(A^0) = B^0 \oplus(\oplus_{j>0} {\mathfrak a}_j) $, which
  gives
  \begin{equation}
    \bar D_{(h, \identity)} \Phi(V,C,Z)\Phi(R_hV, \Adjoint_hC, R_h Z);\quad h \in {\mathcal H},\label{cab1}
  \end{equation}
  where the ``$R$'' in $R_hZ$ has the meaning given at the beginning of this discussion.

  On the other hand, \eqrefs{consequences}{cab0} implies
  \begin{equation*}
    \bar\nabla_{(0,Y)} \Phi(\xi) = \Phi(\adjoint^T_Y \xi),\qquad
    Y \in \Gamma(\oplus_{j>0}{\mathfrak a}_j),\,\xi \in \Gamma(\graded(A)).
  \end{equation*}
  Because $\exp(\oplus_{j>0}{\mathfrak a}_j)$ has simply-connected fibres, this
  intertwining by $\Phi $ of infinitesimal actions is an intertwining of their
  corresponding globalizations:
  \begin{equation}
    \label{cab2}
    \bar D_{(\identity, k)} \Phi(V, C, Z) = \Phi(\Adjoint^T_k(V,C, Z)).
  \end{equation}
  The formula S3$^\prime$ follows from \eqref{cab1} and \eqref{cab2} and the identity
  $(h, k) = (\identity, k)(h, \identity)$ for the semi-direct product.
\end{proof}

% \subsection{Prolongation as functor}\label{functor}
% Here we argue that prolongation is a suitable functor. This section is fairly formal and
% the reader may find it easier to reproduce the obvious definitions herself than to parse
% the details, which are included here for completeness.

% A morphism of filtered Lie algebroids $q \colon A \rightarrow \tilde A$ is a Lie algebroid
% morphism respecting the filtrations: $q(A^j) \subset \tilde A^j$. A morphism of filtered
% Lie groupoids $Q \colon {\mathcal G} \rightarrow \tilde {\mathcal G} $ is a Lie groupoid
% morphism whose infinitesimalization $q=dQ \colon A \rightarrow \tilde A$ is a morphism of
% firmly filtered Lie algebroids. We obtain the category of {\em firmly} filtered Lie
% algebroids or Lie groupoids by simply restricting the class of morphisms to those whose
% source and target are firmly filtered objects.

% A morphism of abstract infinitesimal Levi structures
% $(B, \oplus_{j>0} {\mathfrak a}_j, R, T)$ and
% $(\tilde B, \oplus_{j>0} \tilde{\mathfrak a}_j, \tilde R, \tilde T)$ consists of a pair
% $(q, \omega)$, where $q \colon B \rightarrow \tilde B$ is morphism of filtered Lie
% algebroids and
% $\omega \colon \oplus_{j>0}{\mathfrak a}_j \rightarrow \oplus_{j>0}\tilde{\mathfrak a}_j$
% a morphism of graded vector bundles, such that induced
% morphims of graded vector bundles
% \begin{gather*}
%   (q, \omega)_* \colon \graded(TM)\oplus B^0 \oplus (\oplus_{j>0}{\mathfrak a}_j)
%      \rightarrow \graded(TM)\oplus \tilde B^0 \oplus (\oplus_{j>0}\tilde{\mathfrak a}_j)\\
%   (V, C, Z) \mapsto (\graded_0(q^\vee)(V), qC, \omega Z)
% \end{gather*}
% is: (i) a morphism of Lie algebra bundles, with respect to the brackets $T$ and
% $\tilde T$; and (ii) an intertwining of the representations $R$ and $\tilde R$. Here
% $q^\vee \colon TM \rightarrow TM$ is the filtration-preserving morphism covered by $q$, in
% the sense that $\# \circ q = q^\vee \circ \#$. A morphism of abstract Levi structures
% $({\mathcal H}, \oplus_{j>0}{\mathfrak a}_j, R, T)$ and
% $(\tilde {\mathcal H}, \oplus_{j>0}\tilde{\mathfrak a}_j, \tilde R, \tilde T)$ is a pair
% $(Q, \omega)$, where $Q \colon {\mathcal H} \rightarrow \tilde {\mathcal H} $ is morphism
% of filtered Lie groupoids and
% $\omega \colon \oplus_{j>0}{\mathfrak a}_j \rightarrow \oplus_{j>0}\tilde{\mathfrak a}_j$
% a morphism of graded vector bundles, such that: (i) $(dQ, \omega)$ is a morphism of the
% corresponding abstract infinitesimal Levi structures; and (ii) $(dQ, \omega)_*$
% intertwines the (global) representations $R$ and $\tilde R$.

% The {\df abstract prolongation} of a morphism $(q, \omega)$ of abstract infinitesimal Levi
% structures as above is the morphism of firmly filtered Lie algebroids
% \begin{gather*}
%   B \oplus_R (\oplus_{j>0}{\mathfrak a}_j)
%     \rightarrow \tilde B \oplus_{\tilde R} (\oplus_{j>0}\tilde{\mathfrak a}_j) \\
%   (X, Y) \mapsto (qX, \omega Y).
% \end{gather*}
% For the morphism $(Q, \omega)$ of abstract Levi structures described above, we can
% integrate the morphism of Lie algebra bundles
% $\omega \colon (\oplus_{j>0}{\mathfrak a}_j, T) \rightarrow (\oplus_{j>0}\tilde{\mathfrak
%   a}_j, \tilde T) $ to a morphism of Lie group bundles
% $\Omega \colon \exp(\oplus_{j>0}{\mathfrak a}_j) \rightarrow
% \exp(\oplus_{j>0}\tilde{\mathfrak a}_j)$, and the {\df prolongation} of
% $(Q, \omega)$ is then the morphism of firmly filtered Lie groupoids,
% \begin{align*}
%   {\mathcal H} \times _R \exp(\oplus_{j>0}{\mathfrak a}_j)
%     &\rightarrow \tilde {\mathcal H}  \times_{\tilde R} \exp(\oplus_{j>0}\tilde{\mathfrak a}_j) \\
%   (h, k) &\mapsto  (Q(h), \Omega (k)).
% \end{align*}

% With these definitions, one readily establishes the following facts:
% \begin{proposition}
%   Abstract prolongation is a functor from the category of abstract infinitesimal or global
%   Levi geometries to the category of firmly filtered Lie algebroids, resp., Lie
%   groupoids.
% \end{proposition}

% \begin{corollary}
%   If two abstract infinitesimal or global Levi structures are isomorphic, then so are their
%   corresponding prolongations.
% \end{corollary}


\refreshpage
\section{Deforming model data and Cartan connections}\label{deform}
We need a way to relate different choices of model data in a filtered Cartan geometry
using transformations of the underlying Lie algebroid or integrating Lie
groupoid. Proposition \ref{deformations} below addresses this need.

\subsection{$\psi$-deformations}\label{deformations}
Let $A$ be a Lie algebroid. For each $\psi \in \Gamma(T^*\!M \otimes A) $, define
$\psi_{TM}:TM \rightarrow TM$ by
\begin{equation}\label{opal1}
  \psi_{TM} V = V + \#\,\psi\,V,
\end{equation}
and define $\Adjoint_\psi \colon A \rightarrow A$ by
\begin{equation}
  \label{opal2a}
  \Adjoint_\psi X = X + \psi(\#X).
\end{equation}
Here $\# \colon A \rightarrow TM$ denotes the anchor. The natural context giving rise to
these definitions is provided in \ref{kernel}. For the moment, it suffices to observe
that: (i) If $\psi_{TM}$ is invertible,
then so is $\Adjoint_\psi$, with
\begin{equation}
  \label{opal2}
  \Adjoint_\psi^{-1} = \Adjoint_{-\psi\circ(\psi_{TM})^{-1}};
\end{equation}
and (ii) If $A$ is filtered and transitive and $\psi$ is homogeneous of degree one, i.e.,
$\psi(A^k) \subset A^{k+1}$ for any $k$, then $\psi_{TM}$ is invertible, because in that
case $\psi_{TM}$ is filtration-preserving with
$\graded_0(\psi_{TM})=\identity$.

\begin{lemma}
  Let $A$ be a filtered Lie algebroid and $q \colon A \rightarrow A$ a vector bundle
  isomorphism covering the identity such that $q - \identity$ is homogeneous of degree
  $l\ge 1$. Then the push-forward $\tau' = q_*\tau $ of any model data $\tau $ on $A$
  compatible with the filtration is also compatible with the filtration, and satisfies
  $\graded_0(\tau')=\graded_0(\tau)$. Assuming $A^0$ is the anchor kernel of $A$, $\tau'$
  is also model data.
\end{lemma}
\begin{proof}
  Since $q$ will be filtration-preserving, so is $q^{-1}$, which shows $\tau' $ is
  compatible with the filtration. If $qX = X + Y$, then $q^{-1}X = X - q^{-1}(Y)$, and we
  can therefore see that $q^{-1} - \identity$ is also homogeneous of degree $l$. The
  push-forward is defined by $\tau'(X, Y) = q \tau (q^{-1}X, q^{-1}Y)$, and, with the
  preceding observations in hand, checking $\graded_0(\tau') = \graded_0(\tau)$ is
  straightforward. The last statement holds because $\tau $ is model data and $q, q^{-1}$
  are filtration-preserving.
\end{proof}

If $\tau $ is compatible with the filtration of a filtered Lie algebroid $A$, with anchor
kernel $A^0$, then, assuming $\psi $ is homogeneous of degree $l \ge 1$, the lemma shows
that $\tau' = (\Adjoint_\psi)_* \tau $ is model data with
$\graded_0(\tau') = \graded_0(\tau)$. Conversely, we have:
\begin{proposition}
  Let $A$ be a transitive filtered Lie algebroid with anchor kernel $A^0$, and $\tau$,
  $\tau'$ model data compatible with the filtration. Assume $T := \graded_0(\tau)$ admits
  a fibre-wise grading section $E$, and that $\graded_0(\tau') = T$. Then:
  \begin{conditions}
  \item\label{saturn1} There exists a unique $\psi \in \Gamma(T^*\!M \otimes A)$,
    necessarily homogeneous of degree one, such that $\tau' = (\Adjoint_\psi)_*\tau$.
  \item\label{saturn2} If $\tau $ is compatible with some infinitesimal Cartan connection
    $\nabla $, then $\tau'$ is compatible with the infinitesimal Cartan connection
    $\nabla'$ defined implicitly by
    $$\bar\nabla'_XY = \Adjoint_\psi (\bar\nabla_X(\Adjoint_\psi^{-1}Y)).$$
  \item \label{saturn3} If ${\mathcal G} $ is a Lie groupoid integrating $A$ and $\tau $
    is compatible with some Cartan connection $D$, then $\tau'$ is compatible with the
    Cartan connection $D'$ defined implicitly by
    $$\bar D'_gX = \Adjoint_{\psi(gm)}\bar D_g \Adjoint_{\psi(m)}^{-1}X,$$ for each arrow
    $g \in {\mathcal G} $ beginning at some $m \in M$, and each $X \in A|_{m}$, and whose
    infinitesimalization is $\nabla'$ above,
  \item\label{saturn5} If $({\mathcal G}, D, \tau)$ is a transitive filtered Cartan
    geometry, then $({\mathcal G}, D', \tau')$ is another transitive filtered Cartan
    geometry with the same Levi reduction. An analogous statement holds in the
    infinitesimal case.
  \end{conditions}

\end{proposition}
%

When $\tau'=(\Adjoint)_*\tau$, and $D'$ and $\nabla'$ are defined (implicitly) by
\eqref{saturn3} and \eqref{saturn2}, then the primed quantities will be called the {\df
  $\psi$-deformations} of $\tau $, $D$ and $\nabla $. The proof of the proposition is
given in \ref{existence_deformations}--\ref{same_levi} below. In \ref{gauge_transforms} we
connect $\psi$-deformations to Weyl gauge transformations.

\subsection{The existence of deformations}\label{existence_deformations}
The existence part of Proposition \eqrefs{deformations}{saturn1} has an elementary proof
proceeding as follows. Let $\tau$ and $\tau'$ be model data as in the proposition and fix
a lift $\epsilon \in \Gamma(A^0)$ through $A^0 \rightarrow A^0/A^1$ of $E$. Then, as we
have described in \ref{splittings}, we get two corresponding splittings
$\Phi, \Phi' \colon \graded(A) \rightarrow A $ of the Lie algebra bundles $(A, \tau)$ and
$(A, \tau')$. By definition, we have $\Phi_*T=\tau $ and $\Phi'_*T= \tau'$, and, because
$\tau $ and $\tau' $ agree on $A^0$ (by the definition of model data)
$\Phi' \circ \Phi^{-1}$ is the identity on $A^0$. It follows from the transitivity of $A$
that $\tau' = \Psi_* \tau$, where $\Psi := \Phi' \circ \Phi^{-1}$ satisfies
$\Psi(X) = X + \psi (\#X)=\Adjoint_\psi X$ for some vector bundle morphism
$\psi \colon TM \rightarrow A$.

Also following from the definition of splittings, we have, for any $X \in \Gamma(A^k)$ and
$k \in {\mathbb Z}$,
\begin{gather}
  X \equiv \Phi(\graded_k(X)) \modulo A^{k+1},\label{opal3}\\
  \Phi'(\graded_k(X)) \equiv X \modulo A^{k+1}.\label{opal4}
\end{gather}
From \eqref{opal3} we conclude that
$(\Phi' \circ \Phi^{-1})(X) \equiv \Phi'(\graded_k(X)) \modulo A^{k+1}$, because
$\Phi' \circ \Phi^{-1}$ is filtration-preserving. Combining this with \eqref{opal4}, we
conclude that $\Phi' \circ \Phi^{-1}(X) \equiv X \modulo A^{k+1}$, i.e., $\psi$ is
homogeneous of degree one.

\subsection{The kernel of $J^1 {\mathcal G} \rightarrow {\mathcal G} $}\label{kernel}

Let $A$ be any integrable Lie algebroid. The sections $\psi$ of $T^*\!M \otimes A$ for
which $\psi_{TM}$ are invertible are sections of an open neighborhood of the zero section
of $T^*\!M \otimes A$ that we denote $\model$. The proposition below shows that this set
is a model for the kernel of the projection $J^1 {\mathcal G} \rightarrow {\mathcal G} $
for {\em any} Lie groupoid ${\mathcal G} $ integrating $A$. In particular, it is a totally
intransitive Lie groupoid (a bundle of Lie groups). We now describe the corresponding
groupoid structure directly.

The zero section of $T^*\!M \otimes A$ constitutes the set of identity elements of
$\model$. Multiplication is given by
\begin{equation}
  \label{clost}
  \psi \varphi = \psi + \varphi + \psi \circ \# \circ \varphi = \varphi + \psi \circ \varphi_{TM}.
\end{equation}
Inversion is given by
\begin{equation*}
  \psi \mapsto  -\psi \circ (\psi_{TM})^{-1}.
\end{equation*}
A convenient consequence we mention in passing is the formula
\begin{equation}
  \label{clost2}
  \psi \varphi^{-1} = (\psi - \varphi)\circ \varphi_{TM}^{-1}.
\end{equation}
With respect to these groupoid structures, the map
$$\psi \mapsto \psi_{TM} \colon \model \rightarrow
\automorphism({TM})$$ is a morphism of totally intransitive Lie groupoids and the
commutative kernel consists of those $\psi \colon TM \rightarrow A$ with image lying in
the kernel of the anchor.

The reader will readily see that the maps defined by \eqrefs{kernel}{opal1} and
\eqrefs{kernel}{opal2a} define representations of $\model$ on $A$ and $TM$ respectively.
With respect to these representations the anchor is equivariant:
$\#\Adjoint_\psi X = \psi_{TM}\#X$.

Although the proposition below provides useful context, the proof of Proposition
\ref{deformations} will not actually require it. However, the result is needed in Appendix
\ref{rut}.

Let ${\mathcal G} $ be any Lie groupoid with Lie algebroid $A$. Represent elements of
$J^1 {\mathcal G} $ by maps tangent to some local bisection of ${\mathcal G} $, i.e., by
certain vector space morphisms $T_{m}M \rightarrow T_g {\mathcal G} $, where
$g \in {\mathcal G} $ is some arrow beginning at some $m \in M$. Recall that the adjoint
representation for a Lie groupoid ${\mathcal G} $ is actually a representation of
$J^1 {\mathcal G} $ on $A$ \cite{Blaom_16b}, and that $J^1 {\mathcal G} $ also acts
naturally on $TM$. Both representations are denoted $\Adjoint$, and with respect to these
the anchor is equivariant.

\begin{proposition}[\cite{Blaom_16b}]
  The map $\psi \mapsto \varcheck \psi \colon \model \rightarrow J^1 G$, defined by
  $\varcheck \psi V = V + \psi\,V$, is a Lie groupoid morphism and embedding, whose image
  is the kernel of the natural projection $J^1 G \rightarrow G$.\footnote{\cite{Blaom_16b}
    adopts a different sign convention for the embedding and definition of $\model$.} This
  map is equivariant with respect to the natural representations of both groupoids on $A$
  and $TM$: $\Adjoint_{\varcheck\psi} V = \psi_{TM}V$,
  $\Adjoint_{\varcheck\psi} X = \Adjoint_\psi X$, for $V \in {T_{m}M}$, $X \in A|_m$, and
  $m \in M$.
\end{proposition}

\subsection{The deformed Cartan connections}
In passing, let us explain how the deformed connections $\nabla'$ and $D'$ appearing in
Proposition \ref{deformations} arise very naturally. Recall that a Cartan connection $D$
is the $n$-plane field determined by some Lie groupoid right-inverse
$S \colon {\mathcal G} \rightarrow J^1 {\mathcal G}$ for the natural projection
$ J^1 {\mathcal G} \rightarrow {\mathcal G}$. Given some $\psi \in \Gamma(\model)$, we
may, according to the preceding proposition, view it as bisection of $J^1 {\mathcal G} $
and obtain, via conjugation, a corresponding automorphism $K_\psi$ of $J^1 {\mathcal G}$,
sending an arrow $\mu \in J^1_g {\mathcal G} $, beginning at some $m \in M$ with
projection $g \in {\mathcal G}$, to $\varcheck{\psi(gm)}\mu (\varcheck{\psi(m)})^{-1}$. It
is easy to see that $S':=K_\psi \circ S \colon {\mathcal G} \rightarrow J^1 {\mathcal G} $
is another right-inverse, defining a new Cartan connection $D'$. From the definition of
the corresponding representations $\bar D$ and $\bar D'$, one immediately derives the
formula in \eqrefs{deformations}{saturn3}.

Now $\bar\nabla $ is the infinitesimalization of the representation $\bar D $, and it
therefore follows from the formula in \eqrefs{deformations}{saturn3}, and a simple
computation, that the infinitesimalization $\bar\nabla'$ of $\bar D'$ is given by the
formula in \eqrefs{deformations}{saturn2}.

We now return to the proof of Proposition \ref{deformations}. Regardless of whether $A$ is
integrated by some Lie groupoid, the formula for $\bar\nabla'$ given in
\eqrefs{deformations}{saturn2} must define an infinitesimal Cartan connection, by the
characterization of such connections given in Proposition \ref{hsd}, which applies because
we assume $A$ is transitive. The main point here is that \eqrefs{deformations}{saturn2}
indeed defines a representation. The details are not difficult and are left to the
reader. It is a simple computation to show that $\tau' = (\Adjoint_\psi)_*\tau $ must be
$\bar\nabla'$-invariant ($\nabla'$-compatible) whenever $\tau $ is $\bar\nabla$-invariant
($\nabla$-compatible).

Similarly, the formula for $\bar D'$ given in \eqrefs{deformations}{saturn3} must define a
global Cartan connection, by the characterization of such connections given in Proposition
\ref{cartan}, and checking that $\tau' = (\Adjoint_\psi)_*\tau $ must be
$\bar D'$-invariant ($D'$-compatible) whenever $\tau $ is $\bar D$-invariant
($D$-compatible) is a simple computation.

This completes the proof of parts \eqref{saturn2} and \eqref{saturn3} of Proposition
\ref{deformations}.

\subsection{The uniqueness of $\psi$-deformations}\label{deformation_uniqueness}
Having seen that $\psi \mapsto \Adjoint_\psi $ defines a representation of $\model$ on
$A$, to prove the uniqueness of $\psi $ in Proposition \eqrefs{deformations}{saturn1}, it
evidently suffices to show that $(\Adjoint_\psi)^*\tau = \tau$ implies $\psi = 0$,
whenever $\psi $ is homogeneous of degree one, because $\Adjoint_0=\identity$.

Let $\tau $ and $E$ be as in Proposition \ref{deformations} and
$\psi \colon TM \rightarrow A$ be homogeneous of degree one. If we temporarily write
$\hat \psi(X) = \psi(\#X)$, then $(\Adjoint_\psi)^*\tau = \tau$ means
\begin{equation*}
  \tau(\hat\psi X, Y) + \tau(X,\hat\psi Y) + \tau(\hat\psi X, \hat\psi Y) = \hat\psi \tau(X, Y),
\end{equation*}
for all $X, Y \in \Gamma(A)$. In particular, if $\epsilon $ is any lift of $E$ through
$A^0 \rightarrow A^0/A^1$, then
\begin{equation}\label{opal5}
  \tau(\hat\psi X, \epsilon) = \hat\psi(\tau(X, \epsilon)); \qquad X \in \Gamma(A).
\end{equation}
For an inductive argument, suppose $\psi $ (and therefore $\hat\psi $) is homogeneous of
degree $l\ge 1$. Then \eqref{opal5} gives
$T(\graded_l(\hat\psi)\xi, E) = \graded_l(\hat\psi)(T(\xi, E))$, for any
$\xi \in \graded(A)$. In particular, if $j < 0$ and $\xi \in \graded(A)_j$, then
$(j+l) \graded_l(\hat\psi)\xi = j \graded_l(\hat\psi)\xi $, which can only be true if
$\graded_l(\hat\psi)\xi =0$. Since this last is trivially true in the other cases
$j\ge 0$, we conclude that $\hat\psi$, and hence $\psi $, is homogeneous of degree
$l+1$. Induction on $l$ shows $\psi = 0$. This completes the proof of Proposition
\eqrefs{deformations}{saturn1}.

\subsection{Levi reductions are unchanged by $\psi $-deformations}\label{same_levi}
Conclusion \eqrefs{deformations}{saturn5} follows fairly easily from the definitions and
Lemma \ref{deformations}, applied to $q=\Adjoint_\psi $, and is left to the reader.

\subsection{Weyl gauge transformations and $\psi$-deformations}\label{gauge_transforms}

If we use a Weyl gauge transformation to transform model data, then we can say something
about the $\psi$-deformation realizing the same change:

\begin{proposition}
  Let $A$ be a transitive filtered Lie algebroid with anchor kernel $A^0$, $\tau$ model
  data compatible with the filtration, and assume $T := \graded_0(\tau)$ admits a
  fibre-wise grading section $E$. Then for any $Z \in \Gamma(A^l)$, $l \ge 1$, there
  exists unique $\psi \in \Gamma(T^*\!M \otimes A)$, homogeneous of degree $l$, such
  that $(e^{-\adjoint_Z})_*\tau = (\Adjoint_\psi)_* \tau$. In that case, for any
  integer $k < 0$,
  \begin{equation}
    \label{opal7}
    \psi(\#X) \equiv \tau(Z, X) \modulo A^{k+l+1};\qquad X \in \Gamma(A^k).
  \end{equation}
\end{proposition}
%
\begin{remark}
After introducing the operator $\partial$ in \ref{curv_deform}, we will be able to express
\eqref{opal7} as $\graded_l(\psi) = \partial \graded_l(Z)$.
\end{remark}
%
\begin{proof}
  By Proposition \ref{deformations}, there exists unique
  $\psi \in \Gamma(T^*\!M \otimes A)$ such that
  $(e^{-\adjoint_Z})_*\tau = (\Adjoint_\psi)_* \tau$, but {\em a priori} we know only that
  $\psi $ is homogeneous of degree {\em one}. Fixing some lift $\epsilon $ through
  $A^0 \rightarrow A^0/A^1$ of $E$, we obtain corresponding splittings
  $A = \oplus_j {\mathfrak a}_j$ and $A = \oplus_j {\mathfrak a}_j'$ with respect to the
  Lie algebra bundle structures $\tau $ and $\tau':=(\Adjoint_\psi)_*\tau$,
  respectively. It is not too hard to see it suffices to prove \eqref{opal7} under the
  seemingly more restrictive hypothesis $X \in {\mathfrak a}_k$, in which case
  \begin{equation}
    \label{opal0}
    \Adjoint_\psi X \in {\mathfrak a}_k'.
  \end{equation}
  Since $\Adjoint_\psi(X) = X + \psi(\#X)$ and $\psi$ is homogeneous of degree one, we may
  define $X_k:=X$ and have $\psi(\#X) = \sum_{m\ge k + 1} X_m$ and
  $\Adjoint_\psi(X)=\sum_{m\ge k} X_m$, for some
  $X_{k+1} \in {\mathfrak a}_{k+1}, X_{k+2}\in {\mathfrak a}_{k+2},$ etc., finite in
  number. These preliminaries set up a simple but tedious computation, tracking the
  relevant degrees of homogeneity. For completeness, details now follow.

  The requirement \eqref{opal0} gives
  \begin{equation}
    \label{opal8}
    \tau'\big(\epsilon, \sum_{m\ge k}X_m\big) = k\sum_{m\ge k}X_m.
  \end{equation}
  We have
  \begin{gather*}
     e^{\adjoint_Z}\epsilon=\epsilon +[Z, \epsilon] + \frac{1}{2}[Z,[Z,\epsilon]] + \cdots\\
       =\epsilon +\tau(Z, \epsilon) + \frac{1}{2}\tau(Z,\tau(Z,\epsilon)) + \cdots\enspace.
  \end{gather*}
  On the other hand, we may write $Z = Z_l + Z^{l+1}$, for some
  $Z_l \in \Gamma({\mathfrak a}_l)$ and $Z^{l+1} \in \Gamma(A^l)$, and since
  $\tau(Z_l, \epsilon) = - lZ_l$, it's not hard to see that see that
  $e^{\adjoint_Z}\epsilon = \epsilon - l Z + \delta $, for some
  $\delta \in \Gamma(A^{l+1})$.

  Firmness of the filtration of $A$, and the expansion of $e^{\adjoint_Z}$, ensure that
  \begin{equation}
    \label{ruby0}
     e^{\adjoint_Z}Y \equiv Y \modulo A^l,
  \end{equation}
  where here $Y \in \Gamma(A)$ is completely arbitrary. Regarding the left-hand side of
  \eqref{opal8}, we now compute
  \begin{gather}
    \tau'\big(\epsilon, \sum_{m\ge k}X_m\big) =
    e^{-\adjoint_Z}\tau\Big(e^{\adjoint_Z}\epsilon,
    e^{\adjoint_Z}\big(\sum_{m\ge k}X_m\big)\Big)\notag\\
    = e^{-\adjoint_Z}\tau\big(\epsilon - lZ + \delta, \sum_{m\ge k}X_m\big) +
      e^{-\adjoint_Z}\tau(\epsilon - lZ + \delta, W),\label{ruby5}
  \end{gather}
  where $W := e^{-\adjoint_Z}(\sum_{m\ge k}X_m) - \sum_{m\ge k}X_m$, which lies in $A^l$,
  by \eqref{ruby0}. In particular, the second term on the right-hand side of \eqref{ruby5}
  must lie in $A^l$ also. So, developing \eqref{ruby5} further, we have
  \begin{gather*}
    \tau'\big(\epsilon, \sum_{m\ge k}X_m\big) \equiv
    e^{-\adjoint_Z}\tau\big(\epsilon - lZ + \delta, \sum_{m\ge k}X_m\big) \modulo A^l \\
    \equiv  e^{-\adjoint_Z}\Big(\,\sum_{m\ge k}m X_m -
      l\sum_{m\ge k}\tau(Z, X_m) + \sum_{m\ge k}\tau(\delta, X_m)\,\Big) \modulo A^l\\
      \equiv \sum_{m\ge k}m X_m - l\sum_{m\ge k}\tau(Z, X_m) +
      \sum_{m\ge k}\tau(\delta, X_m)\,\modulo A^l,
  \end{gather*}
  where in the last step we have again applied identity \eqref{ruby0}. Combining this with
  \eqref{opal8}, we conclude
  \begin{equation}
    \label{ruby6}
    \sum_{m>k}(m-k) X_m \equiv l\sum_{m\ge k}\tau(Z, X_m) + \sum_{m\ge k}\tau(\delta, X_m)\modulo A^l.
  \end{equation}
  Since the terms on the right-hand side lie in $A^{k+l}$, this shows that $X_m=0$
  whenever $k +1 \le m \le k + l -1$. In particular, this shows that
  $\psi(\#{\mathfrak a}_k) \subset A^{k+l}$. Since $k <0$ here is arbitrary, we have
  proven that $\psi $ is homogeneous of degree $l$. But now we may rewrite \eqref{ruby6}
  as
  \begin{equation*}
    \sum_{m \ge l} m X_{m+k} \equiv l\sum_{m\ge k}\tau(Z,X_m) + \sum_{m\ge k}\tau(\delta, X_m)\modulo A^l.
  \end{equation*}
  Since $l \ge l + k + 1$, because $k < 0$, we have $A^l \subset A^{l +k +1}$, and it
  follows that
  \begin{align*}
    \sum_{m \ge l} m X_{m+k} &\equiv l\sum_{m\ge k}\tau(Z,X_m) + \sum_{m\ge k}\tau(\delta, X_m)\modulo A^{l+k+1}\\
    \implies lX_{l+k} &\equiv l \tau(Z, X_k) \modulo A^{l+k+1}\\
    \implies \psi(\#X) &\equiv \tau(Z, X) \modulo A^{l+k+1}.
  \end{align*}
\end{proof}

\refreshpage
\section{Model curvature}\label{modelcurvature}
Model curvature, defined for parabolic geometries in \ref{normalization}, makes sense for
an arbitrary infinitesimal filtered Cartan geometry $(A, \nabla, \tau)$, so long as we
restrict to the transitive case. However, it now depends on both $\tau $ and the
compatible connection $\nabla$, which is not generally determined uniquely by $\tau $. The
main goal of this section is to understand how model curvature transforms under Lie
algebroid automorphisms (Proposition \ref{transform}) and $\psi$-deformations
(Proposition \ref{curv_deform}). We additionally define the ``oid'' analogue of tractor
bundles \cite{Bailey_etal_94}, \cite[\S1.5.7]{Cap_Slovak_09} to explain the relationship
between infinitesimal Cartan connections on Lie algebroids and the adjoint tractor
connections appearing in the principal bundle approach to parabolic geometries.

\subsection{Model curvature and consequences of its vanishing}\label{model_curvature}
Given a transitive global or infinitesimal filtered Cartan geometry with underlying Lie
algebroid $\# \colon A \rightarrow TM$, let $\tau $ denote the model data and $\nabla $
the compatible infinitesimal Cartan connection. With Theorem \ref{curvature} in mind, the
difference between between $\torsion \bar\nabla$ (a ``deformed bracket'') and $\tau $ (the
model bracket) is the {\df model curvature} of the geometry. Specifically, this is
the section $\kappa$ of $\wedge^2 T^*\!M \otimes A$ defined by
\begin{equation*}
  \kappa(\#X, \#Y) = \torsion \bar\nabla (X, Y) - \tau(X, Y); \qquad X, Y \in \Gamma(A),
\end{equation*}
which makes sense, on account of the strong compatibility property
\eqrefs{compat2}{strong} and equation \eqrefs{hsd}{zero} defining $\bar\nabla $.

\begin{proposition}
  The model curvature $\kappa $ determines the curvature of $\nabla $ according to
  \begin{equation*}
    \curvature \nabla (U, V)X = (\bar\nabla_X \kappa)(U, V).
  \end{equation*}
  In particular, if $\kappa =0$, then $\curvature \nabla =0$ and
  $\torsion \bar\nabla =\tau $. If the geometry is regular, then the model curvature is
  homogeneous of degree one, i.e., $\kappa(U, V) \in \Gamma(A^{j+k+1})$ for
  $U \in \Gamma(T^jM)$ and $V \in \Gamma(T^kM)$; it is otherwise homogeneous of degree
  zero.
\end{proposition}
\noindent The consequences of $\curvature \nabla =0$ have already been discussed in
\ref{curvature}. At the very least, according to Theorem \ref{curvature}, $A$ will locally
be a transitive action algebroid, with the acting Lie algebra isomorphic to the Lie
algebra model for $\tau $.

\begin{proof}
  For any Cartan connection $\nabla $ on a transitive Lie algebroid, one has the easily
  derived identity,
  \begin{equation}
    \label{solidarity}
    \curvature\nabla(\#X, \#Y)Z =  \bar\nabla_Z\torsion \bar\nabla (X, Y).
  \end{equation}
  See, for example, \cite[\S5.4]{Blaom_06}. From the definition of $\kappa $,
  \begin{equation}
    \label{poland}
    (\bar\nabla_Z\kappa)(\#X, \#Y) = (\bar\nabla_Z\torsion \bar\nabla)(X, Y) -
    (\bar\nabla_Z \tau)(X, Y).
  \end{equation}
  The stated identity follows from \eqref{solidarity}, \eqref{poland} and the
  $\bar\nabla $-invariance of $\tau $ (compatibility of $\tau$ and $\nabla$).

  By definition,
  \begin{equation}
    \label{pot}
    \kappa(\#X, \#Y) = \bar\nabla_XY - \bar\nabla_YX - ([X, Y] + \tau(X, Y))
  \end{equation}
  Suppose $X \in \Gamma(A^j)$ and $Y \in \Gamma(A^k)$ for some $j, k < 0$. As we argued in
  the proof of Proposition \ref{homogeneous}, the non-positivity of $j$ and $k$ means that
  $A^j \subset A^{j+k+1}$ and $A^k \subset A^{j+k+1}$. By $\bar\nabla $-invariance of the
  filtration of $A$, the first two terms on the right-hand side of \eqref{pot} lie in
  $\Gamma(A^{j+k+1})$. The last bracketed term lies in $\Gamma(A^{j+k})$, by Axiom F1 for
  Lie algebroid filtrations, and compatibility of $\tau $ with the filtration of $A$. In
  the regular case, this bracketed term lies in $A^{j+k+1}$, by the definition of
  regularity.

\end{proof}

\subsection{Model curvature under automorphisms}\label{transform}
Let $A$ be a transitive filtered Lie algebroid, $\tau $ model data compatible with the
filtration, and $\nabla$ a $\tau$-compatible Cartan connection.  Let
$f \colon M \rightarrow M'$ be a diffeomorphism and $q \colon A \rightarrow A'$ some
filtration-preserving Lie algebroid isomorphism, covering $f$, into some second filtered
Lie algebroid $A'$. Supposing $A^0$ is the anchor kernel of $A$, the push-forward
$q_*\tau$, defined by
$$(q_*\tau)(X, Y) = q \tau(q^{-1}X, q^{-1}Y),$$ will be model data on $A'$. The isomorphism
$Tf \colon TM \rightarrow TM'$ will be filtration-preserving. In particular, $\tau $ is
regular if and only if $q_*\tau$ is regular. According to our next results, under $q$,
model curvature transforms in a natural way.

\begin{proposition}
  The equation
  \begin{equation}
    \label{tarragon1}
    \bar\nabla'_XY = q_*\bar\nabla_{q^*X} (q^*Y); \qquad X, Y \in \Gamma(A'),
  \end{equation}
  implicitly defines a Cartan connection $\nabla' $ compatible with the push-forward
  $\tau'=q_*\tau $. Here $(q_*X)(m)=qX(f^{-1}(m))$ and $(q^*X)(m) = q^{-1}X(f(m))$, for
  $X \in \Gamma(A)$. If ${\mathcal G}$ a Lie groupoid integrating $A$, ${\mathcal G}'$ is
  a firmly filtered Lie groupoid integrating $A'$, $\nabla $ the infinitesimalization of a
  Cartan connection $D$ on ${\mathcal G} $, and
  $Q \colon {\mathcal G} \rightarrow {\mathcal G}' $ a Lie groupoid isomorphism with
  infinitesimalization $q$, then
  \begin{equation}
    \label{tarragon2}
    \bar D_g' = q \circ \bar D_{Q^{-1}(g)} \circ q^{-1}
  \end{equation}
  implicitly defines a Cartan connection $D'$ on ${\mathcal G}' $ compatible with
  $\tau' $, and infinitesimalizing to $\nabla'$. In any case, if $\kappa$ is the model
  curvature of $(\tau, \nabla)$ and $\kappa'$ the model curvature of $(\tau', \nabla')$,
  viewed as sections of $\wedge^2 T^*\!M \otimes {\mathcal A}$ and
  $\wedge^2 T^*\!M' \otimes {\mathcal A}'$, then we obtain the {\df transformation rule},
  \begin{equation}
    \label{tarragon5}
    \kappa'(V_1, V_2) = q \kappa (Tf^{-1} \cdot V_1, Tf^{-1}\cdot V_2); \qquad V_1, V_2 \in TM.
  \end{equation}
  If $({\mathcal G}, \tau, D)$ (resp., $(A, \tau, \nabla)$) is an (infinitesimal) filtered
  Cartan geometry, then $({\mathcal G}, \tau', D')$ (resp., $(A, \tau', \nabla')$) is an
  (infinitesimal) filtered Cartan geometry. In the special case that $Q$ (resp., $q$) is
  an (infinitesimal) Weyl gauge transformation (where $A=A'$ and $f = \identity$) the
  associated (infinitesimal) Levi structures for the primed and unprimed geometries are
  identical.
\end{proposition}
\begin{proof}
  To show $\nabla'$ is well-defined, we need to apply
  Proposition \ref{hsd}, which means showing: (i) $\bar\nabla'$, as defined by
  \eqref{tarragon1}, is a representation, and supposing $\#Y=0$, that (ii)
  $\bar\nabla'_XY = [X, Y]$. Verifying (i) is is an easy computation appealing to the fact
  that $\bar\nabla $ is a representation and that $q$ is a Lie algebroid
  morphism. Regarding (ii), we have
  \begin{equation*}
    \bar\nabla'_XY = q_*\bar\nabla_{q^*X}(q^*Y) = q_*[q^*X, q^*Y] = [X, Y],
  \end{equation*}
  where the second equality follows from the fact that
  $\bar\nabla_{\xi}{\eta} = [\xi, \eta]$ whenever $\# \eta =0$, and that
  $\# (q^*Y) = f^*(\# Y)$ for any $Y \in \Gamma(A)$. Since $\tau $ is $\bar\nabla$-invariant
  by hypothesis, another easy computation shows that $\tau'$ is $\bar\nabla'$-invariant,
  i.e., is compatible with $\bar\nabla'$.

  Regarding the global case, we prove a little more, indicating the origins of formulas
  \eqref{tarragon1} and \eqref{tarragon2}. Note first that because $Q$ is a groupoid
  morphism, we have the identity
  \begin{equation}
    \label{tarragon3}
    q \circ \Adjoint_\mu = \Adjoint_{(J^1Q)\mu} \circ q; \qquad \mu \in J^1 {\mathcal G},
  \end{equation}
  where $\Adjoint$ is the adjoint representation of $J^1 {\mathcal G} $ on $A $
  (see \cite{Blaom_16b}). For a proof of \eqref{tarragon3}, suppose $\mu = J^1_mb$, for
  some bisection $b$ of $\mathcal G$. Then for an arbitrary element of $A$, represented by
  source-fibre path $t \mapsto g(t)$ beginning at $m$, we have
  \begin{equation*}
    \Adjoint_{J^1_m b}\left(\frac{d}{dt}g(t)\Big|_{t=0}\right)
    = \frac{d}{dt}b(g(t)m)g(t)b(m)^{-1}\Big|_{t=0},
  \end{equation*}
  so that
  \begin{multline*}
    (q \circ \Adjoint_{J^1_m b})\left(\frac{d}{dt}g(t)\Big|_{t=0}\right)
    = \frac{d}{dt}Q(b(g(t)m))Q(g(t))Q(b(m))^{-1}\Big|_{t=0}\\
    = \Adjoint_{(J^1Q)(J^1_m b)}  \frac{d}{dt}Q(g(t))\Big|_{t=0}
    = \Adjoint_{(J^1Q)(J^1_m b)}  q\left(\frac{d}{dt}g(t)\Big|_{t=0}\right).
  \end{multline*}
  and \eqref{tarragon3} is proven. If
  $S \colon {\mathcal G} \rightarrow J^1 {\mathcal G} $ is the splitting associated with
  $D$, then associated with the splitting
  \begin{equation}
    \label{tarragon4}
      S ' = J^1 Q \circ S \circ Q^{-1}
  \end{equation}
  is a Cartan connection $D'$ on ${\mathcal G}'$, and applying the identity
  \eqref{tarragon3} and the definition of representations $\bar D $ and $\bar D'$
  associated with these connections, we obtain the formula \eqref{tarragon2}. Showing that
  $\bar\nabla'$ is the infinitesimalization of $\bar D'$ is a simple computation. The
  $\bar D'$-invariance of $\tau'$ readily follows from the $\bar D$-invariance of $\tau $,
  i.e., $\tau' $ is indeed compatible with $D'$.

  Regarding \eqref{tarragon5}, we compute, for any $X, Y \in \Gamma(A)$,
  \begin{align*}
    \kappa'(\#X, \#Y) &= \bar\nabla'_XY - \bar\nabla'_YX - [X, Y] - \tau'(X, Y)\\
                      &= q_*\bar\nabla_{q^*X}(q^*Y) - q_*\bar\nabla_{q^*Y}(q^*X)
                        - q_*[q^*X, q^*Y] - q_*\left(\,\tau(q^*X, q^*Y)\,\right) \\
    &= q_*\left(\,\kappa(\# q^*X, \# q^*Y)\,\right) = q_*\left(\,\kappa(f^*(\# X), f^*\# Y)\,\right),
  \end{align*}
  and \eqref{tarragon5} follows.

  The proof of statements regarding the special case of Weyl gauge transformations are not
  difficult, after one applies Lemma \ref{deformations} to see that
  $\graded_0(\tau)=\graded_0(\tau')$ in that case. Details are left to the reader.
\end{proof}

\subsection{The Kostant codifferential}\label{homology}
Let $A$ be a filtered Lie algebroid with filtration-compatible model data $\tau $. For the
moment, the Lie algebra model for $\tau $ is arbitrary; it need not be reductive, and we
need not suppose $A$ is transitive. However we will assume $A$ admits a $\tau$-compatible
Weyl gauge.

Recall from \ref{normalization} that we have a natural chain complex

\begin{equation}
  \label{chain1} 0 \leftpartial{\tau} A \leftpartial{\tau} A^1 \otimes A
\leftpartial{\tau} \wedge^2 A^1 \otimes A \leftpartial{\tau} \cdots,
\end{equation}
where the Kostant codifferential $\partial^\tau$ is defined by
\eqrefs{normalization}{form1}. In the proposition below, we will establish that the
corresponding bundles of homology groups have realizations depending only on
$T = \graded_0(\tau)$, and are canonically {\em graded}, and not just canonically
filtered.

Notice that the bracket $T = \graded_0(\tau)$ makes $\graded(A)$ into a representation of
the Lie algebra bundle $\graded(A^1)$ and we obtain a graded version of \eqref{chain1},
\begin{equation}
  \label{chain2} 0 \leftpartial{*}  \graded(A)
  \leftpartial{*} \graded(A^1) \otimes \graded(A)
  \leftpartial{*} \wedge^2 \graded(A^1) \otimes \graded(A) \leftpartial{*} \cdots,
\end{equation}
where $\partial^*$ is defined by the same formula \eqrefs{normalization}{form1}, with $\tau $ there
replaced with $T$.

The filtration of $A$ induces a filtration of each term in the complex \eqref{chain1}; for
example decomposable elements of $(\wedge^2 A^1 \otimes A)^l$ are of the form
$Y\wedge Z \otimes X$, for some $Y\in A^i$, $Z \in A^j$ and $X \in A^k$ with $i, j \ge 1$
and $i + j +k = l$. Similarly, each term of the complex \eqref{chain2} is graded. The
differential $\partial^\tau$ is filtration-preserving, while $\partial^*$ is
grading-preserving. There is no canonical chain map from complex \eqref{chain1} to
\eqref{chain2}. However, for each fixed $l \in {\mathbb Z} $, we have subcomplexes
\begin{gather}
  \label{chain3} 0 \leftpartial{\tau}  A^l \leftpartial{\tau} (A^1\otimes A)^l \leftpartial{\tau} (\wedge^2 A^1 \otimes A)^l \leftpartial{\tau} \cdots \\
  \label{chain4} 0 \leftpartial{*}  \graded(A)_l
  \leftpartial{*} (\graded(A^1) \otimes \graded(A))_l
  \leftpartial{*} (\wedge^2 \graded(A^1) \otimes \graded(A))_l \leftpartial{*} \cdots,
\end{gather}
and $\graded$ is a chain map from \eqref{chain3} to \eqref{chain4}.

We let $H_n(A^1, A)$, $H_n(\graded(A^1), \graded(A))$, $H_n(A^1, A)^l$, and
$H_n(\graded(A^1),\graded(A))_l$ denote the degree $n$ homologies of the complexes
\eqref{chain1}, \eqref{chain2}, \eqref{chain3}, and \eqref{chain4}, understood as vector
bundles over $M$. Because $\partial^\tau $ is filtration-preserving and $\partial^*$ is
grading-preserving, for each $l \in {\mathbb Z}$, the natural morphisms
\begin{align*}
  H_n(A^1,A)^l &\rightarrow H_n(A^1,A)\\
  H_n(\graded(A^1),\graded(A))_l &\rightarrow H_n(\graded(A^1),\graded(A))
\end{align*}
are injective, and we see easily that this allows us to view $H_n(A^1, A)$ as a filtered
vector bundle, and $H_n(\graded(A^1),\graded(A))$ as a graded vector bundle.

Each term in the complex \eqref{chain1} is a representation of $A^1$, and $\partial^\tau $
is equivariant with respect to these representations, so that $H_n(A^1, A)$ is a also an
$A^1$-representation.  These integrate to representations of the bundle of
simply-connected nilpotent Lie groups $\exp(A^1)$ integrating $A^1$.  In the case $A$ is
integrated by some Lie groupoid ${\mathcal G} $ admitting a Weyl gauge, we may identify
$\exp(A^1)$ with a normal subgroupoid ${\mathcal G}^1 \subset {\mathcal G} $, by
Proposition \ref{weyl2}.

\begin{proposition}
  Let $A$ be a filtered Lie algebroid and $\tau $ model data compatible with the
  filtration. Then:
  \begin{conditions}
  \item The actions of $A^1 $ and $\exp(A^1)$ on $H_n(A^1, A)$ are trivial. In particular,
    if $\nabla $ is a Cartan connection on $A$ compatible with $\tau $, then the
    representation $\bar\nabla $ of $A$ on itself makes $H_n(A^1,A)$ into an
    $A/A^1$-representation. In the global case, if $D$ is a $\tau$-compatible Cartan
    connection on ${\mathcal G} $, then the representation $\bar D $ of ${\mathcal G} $ on
    $A$ makes $H_n(A^1,A)$ into ${\mathcal G}/{\mathcal G}^1$-representation. \label{hay1}
  \item For each Weyl gauge $\epsilon$ compatible with $\tau $, the canonical isomorphism
    associated with the splitting $\Phi_\epsilon \colon \graded(A) \rightarrow A$,
    $$\tilde \Phi_\epsilon \colon \wedge^n \graded(A^1) \otimes \graded(A) \rightarrow \wedge^n A^1 \otimes A$$
    is a chain map between the complexes \eqref{chain2} and \eqref{chain1}.
    \label{hay2}
  \item The corresponding isomorphism in homology
    $$ (\tilde \Phi_\epsilon)_* \colon H_n(\graded(A^1), \graded(A)) \rightarrow H_n(A^1, A)$$
    is independent of the choice of $\epsilon$. In particular, if $A$ admits a Weyl gauge, then
    the filtered vector bundle $H_n(A^1, A)$ has a canonical splitting. \label{hay3}
  \end{conditions}
\end{proposition}

\begin{lemma}
  Let $\Adjoint^\tau $ denote the representation of of $\exp(A^1)$ on $A$ and let
  $\epsilon_1, \epsilon_2$ be two Weyl gauges compatible with $\tau $. Then there exists a smooth
  section $k$ of $\exp(A^1)$ such that
  $\Phi_{\epsilon_2}(\xi) = \Adjoint^\tau_{k(m)}\Phi_{\epsilon_1}(\xi)$, for any
  $\xi \in \graded(A)|_{m}$.
\end{lemma}
\begin{proof}
  Applying Lemma \eqrefs{splittings}{splittings1} fibre-wise, there is a unique section
  $k $ of the bundle of simply-connected nilpotent Lie groups $\exp(A^1)$ such that
  $\epsilon_2(m) = \Adjoint^\tau_{k(m)} \epsilon_1(m)$. Since we suppose $\epsilon_1$ and
  $\epsilon_2$ are smooth, $k$ must be also. The desired result now follows from the
  fibre-wise application of \eqrefs{splittings}{splittings2}.
\end{proof}

\begin{proof}[Proof of proposition]
  In proving \eqref{hay1}, it suffices to prove the claim for $A^1$, since $\exp(A^1)$ has
  connected source-fibres. We need to show that $A^1$ maps the kernel of
  $\partial^\tau \colon \wedge^n A^1 \otimes A \rightarrow \wedge^{n-1}A^1 \otimes A$ into
  the image of
  $\partial^\tau \colon \wedge^{n+1}A^1 \otimes A \rightarrow \wedge^n A^1 \otimes
  A$. Following \cite[p.~263]{Cap_Slovak_09}, we see this follows from the identity
  \begin{equation*}
    -\adjoint_Y^\tau \omega =
    \partial^\tau(Y \wedge \omega) +
    Y \wedge \partial^\tau \omega;
    \qquad \omega \in \Gamma(\wedge^n A^1 \otimes A),\,Y \in \Gamma(A^1).
  \end{equation*}
  To prove the identity, it suffices to prove it for decomposable $\omega $. For example,
  if $\omega = Z \otimes X$ ($n = 1$), then we compute
  \begin{align*}
    \partial^\tau(Y \wedge \omega) &= - Z \otimes \tau(Y, X) + Y \otimes \tau(Z, X) - \tau(Y,Z) \otimes X\\
    Y \wedge \partial^\tau \omega &= Y \wedge (-\tau(Z, X)),\\
    \text{so that}\quad \partial^\tau (Y \wedge \omega) + Y \wedge \partial^\tau \omega &=
    -Z \otimes \tau(Y,X) - \tau(Y,Z) \otimes X = - \adjoint^\tau_Y \omega.
  \end{align*}
  See op.~cited for the general argument.

  The definition of $\tilde \Phi_\epsilon$ is clear. For example, we have
  $\tilde \Phi_\epsilon(Z_1 \wedge Z_2 \otimes X) = \Phi_\epsilon(Z_1)\wedge
  \Phi_\epsilon(Z_2) \wedge \Phi_\epsilon(X)$. To prove \eqref{hay2}, it suffices to show
  that
  $\partial^\tau\tilde \Phi_\epsilon \omega = \tilde \Phi_\epsilon \partial^* \omega $ for
  all $\omega \in \wedge^{n+1} \graded(A^1) \otimes \graded(A)$ that is decomposable,
  which is readily accomplished: Take $\omega$ to be of the form
  $\graded(Y_0) \wedge \ldots \wedge \graded(Y_n) \otimes \graded(X)$, where, without loss
  of generality, we suppose $Y_0,\ldots,Y_n$ and $X$ each lie in some component
  ${\mathfrak a}_j$, in the decomposition $A=\oplus_i {\mathfrak a}_i$ associated with
  $\epsilon $ ($j\ge 1$ in the case of $Y_0,\ldots,Y_n$). Part \eqref{hay3} now follows
  from preceding parts and the lemma above.
\end{proof}

\subsection{Model curvature under $\psi$-deformations}\label{curv_deform}
Under the same blanket assumptions as \ref{homology}, consider the {\em cochain} complex
\begin{equation}
  \label{chain5a} 0 \rightpartial{}  \graded(A)
  \rightpartial{} \graded(A)_{-}^* \otimes \graded(A)
  \rightpartial{} \wedge^2 \graded(A)_{-}^* \otimes \graded(A) \rightpartial{} \cdots,
\end{equation}
where $\graded(A)_{-}:=\oplus_{j<0} \graded(A)_j$ is a Lie algebra subbundle, which
accordingly acts on $\graded(A)$.  Over each point $m \in M$, \eqref{chain5a} is the
classical cochain complex associated with the representation $\adjoint^T$ of
$\graded(A)_{-}|_m$ on $\graded(A)|_m$. Here $\partial$ is defined by
\begin{align*}
  \partial \omega (V_0, \ldots, V_n) &=
  \sum_{i=0}^{n}(-1)^iT(V_i, \omega(V_0, \ldots, \hat V_i, \ldots V_n))\\
  &+ \sum_{i<j}(-1)^{i+j}\omega(T(V_i,V_j), V_0,\ldots, \hat V_i, \ldots \hat V_j, \ldots V_n),
\end{align*}
where hats indicate omission. In the reductive case we will see in \ref{hodge} that
\eqref{chain5a} can be viewed as the ``adjoint'' of \eqrefs{homology}{chain2}.

The formula shows that $\partial$ is grading-preserving if we equip
$\wedge^n \graded(A)_{-}^*\otimes \graded(A)$ with the grading in which a section
$\omega $ has degree $l$ if it is homogeneous of degree $l$, by which we mean that
$\omega(V_1, \ldots V_n)\in \Gamma(\graded(A)_{l+i_1+i_2+\ldots+i_n})$ whenever
$V_j \in \Gamma(\graded(A)_{i_j})$, for each $j \in \{1, \ldots n\}$.

Our interest in the cochain complex \eqref{chain5a} is following:
\begin{proposition}
  Let $(A, \nabla, \tau)$ be an infinitesimal filtered Cartan geometry. Furthermore,
  suppose that $A$ is transitive and that $A^0$ is the anchor kernel of $A$, so that
  $\graded(A)_{-} \cong \graded(TM)$ and $\partial_n$ is a map
  $$\partial_n\wedge^n \graded(T^*\!M) \otimes \graded(A)\rightarrow
  \wedge^{n+1} \graded(T^*\!M) \otimes \graded(A).$$ For some
  $\psi \in \Gamma(T^*\!M \otimes A)$ that is homogeneous of degree $l \ge 1$, let
  $\nabla'$ and $\tau'$ be the $\psi$-deformations of $\nabla $ and $\tau $, as defined in
  \ref{deformations}, and let $\kappa $, $\kappa'$ denote the model curvatures of the
  infinitesimal parabolic geometries $(A, \nabla, \tau)$ and $(A, \nabla', \tau')$. Then
  $\kappa' - \kappa $ is homogeneous of degree $l$ with
  $\graded_l(\kappa' - \kappa) = -\partial \graded_l(\psi)$.
\end{proposition}
\begin{proof}
  It is not hard to see that the claim follows from the following two facts proven below:
  \begin{conditions}
  \item\label{plat1} The restriction of $\torsion \bar\nabla' - \torsion \bar\nabla$ to a
    section of $\wedge^2\graded(A)_{-}^*\otimes A$ is homogeneous of degree $l + 1$.
  \item\label{plat2}
    The restriction $r = \tau' - \tau $ to a section of $\wedge^2\graded(A)_{-}^*\otimes
    A$ is homogeneous of degree $l$, with $\graded_l (r) = -\partial\graded_l(\psi)$.
  \end{conditions}

  Let $X \in \Gamma(A^j)$ and $Y \in \Gamma(A^k)$ arbitrary sections, with $j, k <
  0$. Here are some {\df Preliminary Observations:} Since $\psi$ is homogeneous of degree
  $l \ge 1$, $\psi_{TM} \colon TM \rightarrow TM $ is filtration-preserving, with
  $\graded_0(\psi_{TM})=\identity= \graded_0(\psi_{TM}^{-1})$; $\bar\nabla_X$ and
  $\bar\nabla_Y$ are also filtration-preserving, because $\nabla $ is required to be
  compatible with filtration, by the definition of infinitesimal filtered Cartan
  geometries; because $j, k < 0$, we always have $A^m \subset A^{m + j + 1}$ and
  $A^m \subset A^{m + k + 1}$ for any integer $m$; because $l\ge 1$, we always have
  $A^{m +l} \subset A^m$, for any $m$; and
  $\graded_0(\#) \colon \graded(A)_{-} \rightarrow \graded(TM)\cong \graded(A)_{-}$ is the
  identity.

  On expanding the definition of $\bar\nabla'$ (Equation \eqrefs{deformations}{saturn2})
  and the definition of $\Adjoint_\psi$ (Equation \eqrefs{deformations}{opal2a}) and its
  inverse (Equation \eqrefs{deformations}{opal2}) one obtains
  \begin{equation*}
    \bar\nabla'_XY - \bar\nabla_XY  =\bar\nabla_X(\psi(\psi_{TM}^{-1}(\#Y))) +
    \psi(\#\bar\nabla_XY) +
    \psi(\#\bar\nabla_X(\psi(\psi_{TM}^{-1}(\#Y)))).
  \end{equation*}
  By our Preliminary Observations, the terms on the right-hand side lie in
  $A^{k+l}$, $A^{k+l}$ and $A^{k + 2l}$, respectively, and accordingly,
  \begin{equation*}
    \bar\nabla'_XY - \bar\nabla_XY \in \Gamma(A^{j+k+l}) \ni
      \bar\nabla'_YX - \bar\nabla_YX,
  \end{equation*}
  where the second part follows by symmetry. Claim \eqref{plat1} follows immediately.

  Similarly expanding $\tau'=(\Adjoint_\psi)_*\tau$, one derives
  \begin{multline}
    \tau'(X, Y) - \tau(X, Y) = -\tau(\psi(\psi_{TM}^{-1}(\#X)), Y) -
    \tau(X, \psi(\psi_{TM}^{-1}(\#Y)))\\
    + \tau(\psi(\psi_{TM}^{-1}(\#X)), \psi(\psi_{TM}^{-1}(\#Y)))\\
    + \psi(\# \tau(X, Y))\\
    - \psi(\#\tau(\psi(\psi_{TM}^{-1}(\#X))), Y) - \psi(\#\tau(X, \psi(\psi_{TM}^{-1}(\#Y))))\\
    + \psi(\#(\psi(\psi_{TM}^{-1}(\#X)), \psi(\psi_{TM}^{-1}(\#Y)))).
  \end{multline}
  By our Preliminary Observations, the terms on the second and fourth lines lie in
  $A^{j+k+2l}$, while that on the last line lies in $A^{j+k+3l}$, which means both lie in
  $A^{j+k+l +1}$. The remaining terms lie in $A^{j+k+l}$, which shows that $r$ is indeed
  homogeneous of degree $l$, and
  \begin{multline*}
    \tau'(X, Y) - \tau(X, Y) \equiv \\
      -\tau(\psi(\psi_{TM}^{-1}(\#X)), Y) -
      \tau(X, \psi(\psi_{TM}^{-1}(\#Y))) +  \psi(\#\tau(X, Y))
    \modulo A^{j+k+l+1},
  \end{multline*}
  from which \eqref{plat2} now readily follows.
\end{proof}

\subsection{The Bianchi identity}\label{section_bianchi}
The next result will be used later to prove Theorem \eqrefs{harmonic}{poker3}.
\begin{proposition}
  Let $(A, \nabla, \tau)$ be a transitive, infinitesimal, filtered Cartan geometry, as in
  Proposition \ref{curv_deform}, and suppose $\kappa $ is homogeneous of degree $l \ge
  1$. Then $\partial \graded_l(\kappa) = 0$.
\end{proposition}
\noindent%
This result is the degree-reduced version of the following {\df Bianchi identity} for the model curvature,
\begin{multline}
  \label{bianchi}
  (\bar\nabla_{X_3}\kappa)(\#X_1, \#X_2) + \kappa (\kappa (\#X_1, \#X_2), \#X_3) \\
   + \kappa(\# \tau(X_1, X_2), \#X_3) + \tau(\kappa(\#X_1, \#X_2), X_3) + \text{terms cyclic in 1-2-3} = 0,
\end{multline}
which we prove below.
\begin{proof}[Proof of proposition]
   Suppose $X_1, X_2, X_3 \in \Gamma(A)$ (which are arbitrary
   above) have {\em negative} filtration degrees, summing to $m$. Then, as $\bar\nabla $
   is filtration-preserving, and as $\kappa $ is homogeneous of degree $l\ge 1$, it
   follows that $(\bar\nabla_{X_3}\kappa)(\#X_1, \#X_2)$, and its cyclic permutations, have at
   most degree $m + l + 1$. The second term in \eqref{bianchi} will have degree at most
   $m + 2l$, which likewise, cannot exceed $ m + l + 1$. So,
  \begin{equation*}
    \kappa(\# \tau(X_1, X_2), \#X_3) + \tau(\kappa(\#X_1, \#X_2), X_3) +
    \text{terms cyclic in 1-2-3} \equiv 0 \modulo A^{m + l + 1}.
  \end{equation*}
  Evidently, both the terms on the left-hand have degree $m + l$, and from this the
  proposition now follows easily, noting that under our identification
  $\graded(A)_{-}\cong \graded(TM)$, $\graded_0(\#)$ is the just the projection
  $\graded(TM) \oplus \graded(A^0) \rightarrow \graded(TM)$.
\end{proof}

For a proof  of \eqref{bianchi}, first note that any infinitesimal Cartan connection
$\nabla $ on a Lie algebroid, one has the Bianchi identity
\begin{equation}
    \label{pq1}
    (\bar\nabla_{X_3}\torsion \bar\nabla )(X_1, X_2) + \torsion \bar\nabla
      (\torsion    \bar\nabla (X_1, X_2), X_3) + \text{terms cyclic in 1-2-3} = 0.
\end{equation}
See \cite[Example 6.5]{Blaom_12}. Since $\bar\nabla \tau  = 0$
(compatibility), it follows from the definition of $\kappa $ that
\begin{equation*}
  (\bar\nabla_{X_3}\kappa )(\#X_1, \#X_2) = (\bar\nabla_{X_3}\torsion \bar\nabla )(X_1, X_2)
\end{equation*}
holds, as do the cyclicly permuted variants thereof. Using these in \eqref{pq1}, we obtain
\begin{equation*}
  (\bar\nabla_{X_3}\kappa)(\#X_1, \#X_2) + \torsion \bar\nabla
  (\torsion    \bar\nabla (X_1, X_2), X_3) + \text{terms cyclic in 1-2-3} = 0.
\end{equation*}
Rearranging the definition of $\kappa $, we have
$\torsion \bar\nabla(X,Y) = \kappa(\#X, \#Y) + \tau(X, Y)$, which we can use to rewrite
this last equation as \eqref{bianchi} above.


\subsection{Hodge theory}\label{hodge}
To the blanket assumptions of \ref{homology} we now add the following assumptions: $\tau $
is reductive, $A^0$ is a fibre-wise parabolic subalgebra of $(A, \tau)$, and the
filtration of $A$ is the associated canonical one. Then $T=\graded (\tau)$ is reductive
and $|A| \le k$ for some $k \in {\mathbb Z} $ (Lemma
\ref{parabolics_from_filtrations}). In this case, as we now explain, $\partial^*$ and
$\partial $ enjoy a relationship analogous to that between the differential and
codifferential operators of classical Hodge theory \cite{Warner_83}. Here we are trivially
extending to semisimple Lie algebra {\em bundles} observations about semisimple Lie {\em
  algebras} originating in Kostant \cite{Kostant_61}, and detailed in
\cite[\S3.3]{Cap_Slovak_09}.

Fixing some multiple of the Killing form for $T$, we may identify
$\graded(A^1)=\graded(A)_1 \oplus \graded(A)_2 \oplus \cdots \graded(A)_k$ with
$\graded(A)_{-}^*=(\graded(A)_{-k}\oplus \cdots \oplus \graded(A)_{-2}\oplus
\graded(A)_{-1})^*$. Under this identification, we can combine
\eqrefs{curv_deform}{chain5a} and \eqrefs{homology}{chain2} into one diagram
\begin{equation}
  \label{chain5} 0 \xrightleftharpoons[\partial^*]{\partial}  \graded(A)
  \xrightleftharpoons[\partial^*]{\partial} \graded(A^1) \otimes \graded(A)
  \xrightleftharpoons[\partial^*]{\partial} \wedge^2 \graded(A^1) \otimes \graded(A)
  \xrightleftharpoons[\partial^*]{\partial} \cdots.
\end{equation}
As we shall see, the following non-trivial decomposition, together with the calculation
summarised in Proposition \ref{curv_deform}, is what makes normalization of curvature in
parabolic geometry possible:
\begin{equation}
  \label{nontrivial} \image\partial_{n-1}\oplus\kernel \partial_n^* =
  \boxed{\wedge^n \graded(A^1) \otimes \graded(A) =
  \kernel \partial_n \oplus \image \partial_{n+1}^*}\,.% \qquad n \in {\mathbb Z}.
\end{equation}
As in Hodge theory, this follows from the existence (over each point $m \in M$) of an
inner product with respect to which $\partial_n$ is the adjoint of $\partial_{n+1}^*$, for
any $n$; in the construction, omitted here, the non-degenerate Killing form of $T$ plays
an essential role. See \cite[\S3.3]{Cap_Slovak_09} for details. And, as in Hodge theory,
we can deduce from \eqref{nontrivial}:

\begin{theorem}
  If $\square := \partial^* \partial + \partial \partial^*$, then
  \begin{gather}
    \kernel\square_n = \kernel_n \partial_n\cap \kernel_n \partial_n^*\label{hodge1}\\
    \text{and}\qquad\wedge^n\graded(A^1)\otimes \graded(A) =
    \image \partial_{n-1} \oplus \kernel\square_n \oplus \image \partial_{n+1}^*.
    \label{hodge2}
  \end{gather}
  In particular, the projection
  $\kernel \partial_n \rightarrow H^n(\graded(A)_-, \graded(A))$ restricts to an
  isomorphism $\kernel \square_n \cong H^n(\graded(A)_-, \graded(A))$, while the
  projection $\kernel \partial_n^* \rightarrow H_n(\graded(A^1), \graded(A))$ restricts to
  an isomorphism $\kernel \square_n \cong H_n(\graded(A^1), \graded(A))$.
\end{theorem}
\noindent%
Here $H^n(\graded(A)_-, \graded(A))$ is the degree-$n$ $\partial$-cohomology of
\eqref{chain5}, which by the theorem, is isomorphic to the $\partial^*$-homology
$H_n(\graded(A^1), \graded(A))$, which is canonically isomorphic to the
$\partial^\tau$-homology $H_n(A^1, A)$, by Proposition \ref{homology}. That is, the
(co)homologies of the chain complexes \eqrefs{homology}{chain1}, \eqrefs{homology}{chain2}
and \eqrefs{curv_deform}{chain5a} are all canonically isomorphic.

The next result is an immediate consequence of \eqrefs{homology}{hay3} and transitivity,
which gives an identification $\graded(A)_-\cong \graded(TM)$. It connects us to the point
of view in the principal bundle approach, but is also important because, following from
the work of \cite{Kostant_61}, the cohomology groups $H^n({\mathfrak g}_-, {\mathfrak g})$
are known in the cases we will need them \cite[\S3.3]{Cap_Slovak_09}.
\begin{proposition}
  Let $({\mathcal G}, \tau)$ be a parabolic geometry with Lie algebroid $A$, and let
  ${\mathfrak g} $ be a filtered Lie algebra constituting a model for the semisimple Lie
  algebra bundle structure $\tau$; without loss of generality, we may suppose
  ${\mathfrak g} $ is actually graded (Proposition \eqrefs{canonical_filtrations_}{hure}),
  and let ${\mathfrak g}_-=\oplus_{j<0} {\mathfrak g}_j$. Then the mutually isomorphic
  (co)homology vector bundles
  $$H_n(A^1,A),\quad H_n(\graded(A^1),\graded(A)),\quad H^n(\graded(TM),\graded(A))$$
  are associated bundles for a representation of the vertex group of
  ${\mathcal G}/{\mathcal G}^1$ over some point $m_0 \in M$ on the Lie algebra cohomology
  $H^n({\mathfrak g}_-, {\mathfrak g}) $.
\end{proposition}
\begin{remark}
  By Remark \ref{regularity_}, the vertex group is reductive, its Lie algebra being
  identifiable with the reductive Levi quotient
  ${\mathfrak p}/{\mathfrak g}^1 \cong {\mathfrak g}_0$, where ${\mathfrak p}
  =\oplus_{j<0}{\mathfrak g}_j$ and ${\mathfrak g}^0=\oplus_{j\ge0}{\mathfrak g}_j$.
\end{remark}

\subsection{Tractor bundles}\label{tractors}
This section, not referenced in the sequel, is included to explain the relationship
between the infinitesimal Cartan connections of the current approach, and the adjoint
tractor connections of the principal bundle approach. Tractor bundles are relevant to the
problem of constructing invariant differential operators, which is beyond the scope of the
present exposition.

Let $({\mathcal G}, D, \tau)$ be a transitive, filtered, Cartan geometry and $\nabla $ the
corresponding infinitesimal Cartan connection on the Lie algebroid $A$ of ${\mathcal G} $.
Recall that strong compatibility means that the representation $\bar\nabla$ of $A$ on
itself as a Lie algebroid, and the representation of $A$ on itself as a Lie algebra
bundle, $X \mapsto \adjoint^\tau(X) := \tau(X,\,\cdot\,)$, restrict to the same
representation of the anchor kernel $A^0$. So, we have
\begin{gather*}
  \adjoint^\tau_Y X = \bar\nabla_YX;\qquad Y \in \Gamma(A^0),\, X \in \Gamma(A)\\
  \bar D_g\adjoint^\tau_Y X = \adjoint^\tau_{\bar D_gY}\bar D_gX; \qquad Y,\,X \in A|_m,\,m \in M,\, g \in {\mathcal G},
\end{gather*}
where the second identity is just the $\bar D $-invariance of $\tau $, and we
understand $g$ to be some arrow beginning at $m$.

More generally, a {\df tractor bundle} is any representation $E$ of ${\mathcal G}$,
together with some infinitesimal representation $\adjoint^\tau$ of the Lie algebra bundle
$(A, \tau)$ on $E$, satisfying
\begin{gather}
  \adjoint^\tau_Y\sigma  = Y \sigma;\qquad Y \in \Gamma(A^0),\, \sigma \in \Gamma(E)\label{hj1}\\
  g\cdot\adjoint^\tau_Y \sigma = \adjoint^\tau_{\bar D_gY}(g\cdot \sigma);
  \qquad Y \in A|_m,\,m \in M,\, \sigma \in E,\, g \in {\mathcal G}.\label{hj2}
\end{gather}
Here we use juxtaposition to denote the action of $A$ on $E$ as a Lie algebroid (the
infinitesimalization of the representation of ${\mathcal G}$ on $E$). Note that \ref{hj2}
has the infinitesimalization
\begin{equation}
  \label{apfel}
  X\adjoint_Y^\tau \sigma = \adjoint_Y^\tau (X\sigma) + \adjoint^\tau_{\bar\nabla_XY}\sigma;
    \qquad X, Y \in \Gamma(A),\, \sigma \in \Gamma(E).
\end{equation}

The significance of tractor bundles is that they come equipped with Koszul
connections, called {\df tractor connections}, well-defined by
\begin{equation*}
  \nabla^E_{\#X} \sigma = X \sigma - \adjoint^\tau_X \sigma.
\end{equation*}
Here $\#$ denotes anchor. With the help of \eqref{apfel}, one computes
\begin{equation*}
  \curvature \nabla^E(U, V) \sigma = -\adjoint^\tau_{\kappa(U, V)}\sigma.
\end{equation*}

Returning to the special case $E=A$, where $\nabla^A$ is known
as the {\df adjoint tractor connection}, we readily derive the formula
\begin{equation}
  \nabla^A_VY = \nabla_VY + \kappa(V, \#Y),\label{tractor1}
\end{equation}
which proves the following:
%
\begin{aside}
  The infinitesimal Cartan connection is the adjoint tractor connection if and only if the
  model curvature vanishes.
\end{aside}

For an explicit construction of tractor bundles, connecting them with the definition
appearing in \cite{Cap_Slovak_09}, we adopt the principal bundle point of view. Fix some
arbitrary $m_0 \in M$, let $\Pi \subset {\mathcal G} $ denote all arrows beginning at
$m_0$, $P \subset \Pi$ the Lie group of arrows beginning and ending at $m_0$,
${\mathfrak g} $ the semisimple Lie algebra $(A|_{m_0}, \tau)$, and ${\mathfrak g}^0$ the
Lie algebra of $P$. Transitivity means $\Pi $ will be a principal $P$-bundle. Now let $V$
be a finite dimensional representation of $P$ and suppose the corresponding infinitesimal
representation ${\mathfrak g}^0 \rightarrow \gl(V)$ is the restriction of a representation
$\rho \colon {\mathfrak g} \rightarrow \gl(V)$. Then, we have:

\begin{proposition}
  The associated bundle $E(\rho) = \Pi \times_P V$ is a tractor bundle, and all tractor
  bundles are of the form $E(\rho)$ for some
  $\rho \colon {\mathfrak g} \rightarrow \gl(V)$ as above.
\end{proposition}

\begin{proof}
For elements $g_1, g_2 \in \Pi $ and $\xi \in {\mathfrak g} $, let us write
\begin{gather*}
  \langle g_1, g_2 \rangle  = g_1g_2^{-1} \in {\mathcal G}\\
  \langle g_2, \xi \rangle  = \bar D_{g_2} \xi \in A.
\end{gather*}
Transitivity means arbitrary elements of ${\mathcal G} $ and $A$ are of this form, and we have
\begin{equation}
  \bar D_{\langle g_1, g_2 \rangle } \langle g_2, \xi \rangle  = \langle g_1, \xi \rangle .\label{hj3}
\end{equation}
If, for each $[g_2, v] \equiv (g_2, v) \modulo P \in E(\rho)$, we define
\begin{equation*}
  \adjoint^\tau_{\langle g_2, \xi \rangle} [g_2, v]= [g_2, \rho_\xi v],
\end{equation*}
then, with the help of \eqref{hj3}, it is easy to see that \eqref{hj1} and \eqref{hj2}
hold.  The proof of the second assertion is left to the reader.
\end{proof}

\refreshpage
\section{Parabolic geometries. Part II}\label{parabolic_proofs}

This section proves results only stated in Section \ref{parabolic_summary}.

\subsection{All parabolic geometries admit compatible Weyl gauges}\label{all}
Suppose $\tau $ is the model data associated with a parabolic geometry (global or
infinitesimal). Then, according to Lemma \ref{parabolics_from_filtrations},
$T = \graded_0(\tau)$ is a semisimple Lie algebra bundle structure on $\graded(A)$, where
$A$ is the underlying filtered Lie algebroid. By Lemma \ref{grading_elements}, we
accordingly have a {\em unique} section $E$ of $\graded(A)_0$ that is a fibre-wise grading
section of $(\graded(A), T)$, what we shall call the {\df canonical grading section}. We
prove the following after stating some consequences:
\begin{proposition}
  For any global or infinitesimal parabolic geometry, any lift $\epsilon$ of the canonical
  grading section $E$ is a Weyl gauge compatible with the model data $\tau $, and all Weyl
  gauges compatible with $\tau$ are lifts of this form.
\end{proposition}

The existence of Weyl gauges, combined with Corollary \ref{model_data_gradings}, delivers:
%
\begin{corollaryA}
  In a global or infinitesimal parabolic geometry, any Cartan connection compatible with
  the model data is automatically compatible with the Lie algebroid filtration.
\end{corollaryA}

Having already established, in Theorem \ref{uniquely_determined}, that the (infinitesimal)
Cartan connections associated with (infinitesimal) parabolic geometries are
automatically strongly compatible with the model data, we obtain:
%
\begin{corollaryB}
  Every (infinitesimal) parabolic geometry is an (infinitesimal) filtered Cartan geometry.
\end{corollaryB}
\noindent%
Theorem \ref{abstract_levi_}, which describes all filtered Cartan geometries as
semi-direct products, now gives:
%
\begin{corollaryC}
  Every Lie groupoid ${\mathcal G} $ admitting the structure of a parabolic geometry
  $({\mathcal G}, \tau)$, and in particular, every action groupoid
  ${\mathcal G} = G \times G/P$ of a generalized flag manifold, is isomorphic to the
  semi-direct product ${\mathcal G}/{\mathcal G}^1 \times_{R^D}\exp \graded(T^*\!M)$. Here
  $D$ is a $\tau $-compatible Cartan connection (defined by \eqrefs{cartan}{adjoint}, in
  the flag manifold case) and ${\mathcal G}^1$ and the representation $R^D$ have their
  meanings described in \ref{reduction_} and \ref{existence}.
\end{corollaryC}

\begin{proof}[Proof of proposition]
  This time we begin with the global case which is simpler.  Let $({\mathcal G}, \tau)$ be
  a parabolic geometry, $M$ the base manifold, and $D$ a Cartan connection compatible with
  $\tau $ and the filtration of the Lie algebroid $A$ of $\mathcal G$.  Since $\tau $ is
  $\bar D$-invariant ($D$ and $\tau $ are compatible) $T$ is invariant with respect to the
  associated representation of ${\mathcal G} $ on $\graded(A)$, that we have also been
  denoting $\bar D $ (see \ref{reduction_}). In particular, for any arrow
  $g \in {\mathcal G} $ beginning at some $m \in M$, $\bar D_g$ must map grading elements
  of $\graded(A)|_m$ to grading elements of $\graded(A)|_{gm}$, which, by the
  aforementioned uniqueness, means $\bar D_gE(m) = E(gm)$, i.e., $E$ is
  $\bar D$-invariant, which is the same as $\Adjoint$-invariance, since ${\bar D}$
  restricts to the canonical representation on $A^0$. It follows that any lift $\epsilon$
  of $E$ through $A^0 \rightarrow A^0/A^1$ will be a Weyl gauge for ${\mathcal G} $. It is
  not hard to see that every Weyl gauge is of this form.

  Turning to the infinitesimal case, let $(A, \tau)$ be an infinitesimal parabolic
  geometry and $\nabla$ a Cartan connection compatible with $\tau $ and the filtration of
  $A$. Since $\tau $ is $\bar\nabla $-invariant (compatibility) $T$ is invariant with
  respect to the associated representation of $A$ on $\graded(A)$, which we have also been
  denoting by $\bar\nabla $. Let $X \in \Gamma(A)$, $j \in {\mathbb Z} $ and
  $Y \in \Gamma(\graded(A)_j)$ be arbitrary. Then $T(E, Y) = jY$ and, applying
  $\bar\nabla_X $ to both sides, we obtain, courtesy of the $\bar\nabla$-invariance of
  $T$,
  \begin{equation}
    \label{won}
    T(\bar\nabla_X E, Y) + T(E, \bar\nabla_X Y) = j \bar\nabla_X Y.
  \end{equation}
  On the other hand, the grading of $\graded(A)$ is $\bar\nabla$-invariant (the filtration
  of $A$ is $\bar\nabla$-invariant) so that $\bar\nabla_X Y \in \Gamma(\graded(A)_j)$,
  implying $T(E, \bar\nabla_X Y) = j \bar\nabla_X Y$. From \eqref{won} we now conclude
  that $T( \bar\nabla_X E, Y) =0$. From the arbitrariness of our choice of $j$ and $Y$
  above, we conclude that $ \bar\nabla_X E$ is fibre-wise in the center of a semisimple
  Lie algebra, and consequently vanishes. As $\bar\nabla $ restricts to the canonical
  representation on $\graded(A^0)$, this shows that $E$ is
  $\adjoint$-invariant. Accordingly, any lift $\epsilon$ of $E$ through
  $A^0 \rightarrow A^0/A^1$ will be a Weyl gauge for $A$. It is not hard to see that every
  Weyl connection is of this form.
\end{proof}

\subsection{Axiom P3 holds everywhere if it holds at a point}\label{parabolic}

\begin{proposition}
  If $M$ is connected then, in the global groupoid case, and in the case of an integrable
  Lie algebroid, it suffices to check that Axiom P3 of \ref{parabolic_defined} holds over
  a single point $m \in M$.
\end{proposition}

\begin{proof}
  We begin with the global case. Assume P3 for parabolic geometries holds at $m_1 \in M$
  and let $m_2 \in M$ be arbitrary. By transitivity, there exists an arrow
  $g \in {\mathcal G} $ from $m_1$ to $m_2$. If $D$ is a Cartan connection on
  ${\mathcal G} $ compatible with $\tau $, then compatibility means $\bar D_g$ is a Lie
  algebra isomorphism between $(A|_{m_1}, \tau|_{m_1})$ and $(A|_{m_2}, \tau|_{m_2})$. It
  is also filtration-preserving, because $D$ is automatically compatible with the
  filtration (Corollary B above). It follows that P3 holds at $m_2$.

  In the integrable, infinitesimal case, we may suppose $A$ is integrated by some Lie
  groupoid ${\mathcal G} $ with simply connected source fibres, so that the representation
  $\bar\nabla $ integrates to a representation $\bar D$, which must leave $\tau $ and the
  filtration of $A$ invariant, because $\bar\nabla $ does. We can now apply the preceding
  arguments verbatim.
\end{proof}

\subsection{On the Lie subgroupoid ${\mathcal G}^1$ integrating $A^1$}\label{subgroups}

\begin{proposition}
  Let $({\mathcal G}, \tau)$ be a parabolic geometry, and let
  ${\mathcal G}^1 \subset {\mathcal G} $ denote the source-connected subgroupoid
  integrating $A^1$.  Then ${\mathcal G}^1 $ is a bundle of simply-connected nilpotent Lie
  groups; it is also a normal subgroupoid of ${\mathcal G}$, so that
  ${\mathcal G}/{\mathcal G}^1$ is a Lie groupoid, also transitive.
\end{proposition}
\begin{proof}
  The first result claim follows from Proposition \eqrefs{weyl2}{xerox2}, the second from
  Theorem \eqrefs{weyl2}{pr1}.
\end{proof}

\subsection{The existence of parabolic geometries with given Levi reduction}\label{existence_}

Corollary B above shows that that following result is a special case of Theorem
\eqrefs{abstract_levi_}{chh02}:

\begin{theorem}[Existence]
  Every Levi structure $({\mathcal H}, T, R)$ is, up to isomorphism, the reduction of some
  parabolic geometry $({\mathcal G}, \tau)$. If the Levi structure is regular, then the
  parabolic geometry can be chosen to be regular.
\end{theorem}

\subsection{Curvature under automorphisms}\label{transform_}
Theorem \ref{uniquely_determined} shows that the model curvature is unambiguously defined
by the model data alone, in the special case of a global or infinitesimal parabolic
geometry.  As remarked in \ref{normalization}, we can use the Killing form to view model
curvature as a section of $\wedge^2 A^1 \otimes A$, which appears in a natural chain
complex with differential $\partial^\tau$ defined by
\eqrefs{uniquely_determined}{form1}. This alternative representation of the curvature
transforms naturally under automorphisms:

\begin{theorem} Let $({\mathcal G}, \tau)$ be any
  parabolic geometry and $Q \colon {\mathcal G} \rightarrow {\mathcal G}'$ a morphism of
  filtered Lie groupoids, in the sense of \ref{morphisms}. Then $({\mathcal G}', \tau')$
  is a parabolic geometry, where $\tau'=q_*\tau $ and $q := dQ \colon A \rightarrow A'$ is
  the infinitesimalization of $Q$. In particular, $(A',\tau')$ is an infinitesimal
  parabolic geometry.

  More generally, for any infinitesimal parabolic geometry $(A, \tau)$, and
  filtration-preserving Lie algebroid morphism $q \colon A \rightarrow A'$, we have: (i)
  $(A', \tau')$ is an infinitesimal parabolic geometry; (ii) $\tau' $ is regular if and
  only if $\tau $ is regular; and (iii) The corresponding model curvatures, $\kappa$ and
  $\kappa'$, when expressed as sections of $\wedge^2 A^1 \otimes A$ and
  $\wedge^2 (A')^1 \otimes A'$, are $q$-related, i.e., $\kappa' = q_* \kappa $, where
  $q_*(Z_1\wedge Z_2 \otimes X) := q_*Z_1\wedge q_*Z_2 \otimes q_*X$. In particular, if
  $\tau $ is normal, then so is $\tau'$.
\end{theorem}

\begin{proof}
  The very last assertion follows from the others, for it is easy to see, from the
  definition \eqrefs{normalization}{form1} of $\partial^\tau$, that
  $\partial^{\tau'} \circ q_* = q_* \circ \partial^\tau$. These other claims follow
  readily from the Proposition \ref{transform} and Theorem \ref{uniquely_determined}, with
  the exception of the transformation rule $\kappa' = q_* \kappa $. To prove it, remember
  that the identification $T^*\!M \cong A^1$, needed to view curvature as a section of
  $\wedge^2 A^1 \otimes A$, depends on the model data $\tau $, while in the case of
  $T^*\!M' \cong (A')^1$, it depends on $\tau'$. With this in mind, we see then that the
  rule follows from \eqrefs{transform}{tarragon5} and the lemma below.
\end{proof}

\begin{lemma}
  Let $\iota\colon A^1 \rightarrow T^*\!M $ denote the isomorphism induced by the
  $\tau$-Killing form, $B$ (or some fixed multiple thereof), and
  ${\iota'} \colon (A')^1 \rightarrow T^*\!M' $ the isomorphism induced by the
  $\tau'$-Killing form, $B'$ (or the same fixed multiple thereof). Then the
  following diagram commutes:
  \begin{equation*}\label{morph}
    \begin{CD}
      A^1 @>{q}>> (A')^1 \\
       @V{\iota}VV @VV{{\iota'}}V \\
       T^*\!M @>{(Tf^{-1})^*}>> T^*\!M
     \end{CD}\enspace.
   \end{equation*}
   Here $f \colon M \rightarrow M'$ is the map covered by $q \colon A \rightarrow A'$ and
   $(Tf^{-1})^*$ denotes the adjoint of $Tf^{-1}$.
\end{lemma}
\begin{proof}[Proof of lemma]
  It is easy to see the choice of multiplicative constant is immaterial, so suppose it is
  one. Now $B'(X, Y) = B(q^{-1}X, q^{-1}Y)$, because
  $\adjoint^{\tau'} = q \circ \adjoint^\tau \circ q^{-1}$. On the other hand, $\iota$ is
  defined implicitly by $\langle \iota X, \#Y\rangle = B(X, Y)$, for arbitrary sections
  $X$ and $Y$ of $A^1$ and $A$, respectively, and we have an analogous characterization
  for ${\iota'}$. We now compute, for arbitrary $X \in A^1|_m$, $Y \in A|_m$, $m \in M$,
  \begin{multline*}
    \langle {\iota'}qX, \# Y\rangle = B'(qX, Y) = B(X, q^{-1}Y)
    = \langle \iota X,\# q^{-1}Y\rangle \\
    = \langle \iota X,(Tf^{-1})(\#Y)\rangle
    = \langle (Tf^{-1})^*\iota)X,\#Y\rangle.
  \end{multline*}
\end{proof}

\subsection{Normalizing model curvature}\label{normalization_}

We turn now to the proof of the following central result:

\begin{theorem}[Normalization]
  Let $({\mathcal G}, \tau)$ be a regular parabolic
  geometry. Then there exists {\bfseries normal}, model data $\tau'$ such that
  $({\mathcal G} , \tau')$ is a regular parabolic geometry with the same Levi reduction.
\end{theorem}

Let $A$ be the Lie algebroid of ${\mathcal G} $.
\begin{lemmaA}
  Suppose $\sigma \in \Gamma(\wedge^nA^1 \otimes A)$ and $\partial^\tau \sigma $ is
  homogeneous of degree $l$. Then there exists
  $\tilde \sigma \in \Gamma(\wedge^n A^1 \otimes A)$, homogeneous of degree $l$, such that
  $\partial^\tau \tilde \sigma = \partial^\tau \sigma $.
\end{lemmaA}
\begin{proof}
  Any lift $\epsilon $ of the canonical grading section $E$ of $\graded(A)$ defines a
  splitting $A = \oplus_{j \in {\mathbb Z}}A_j$ for the filtration of $A$, which in turn
  gives us a grading of $C^n := \wedge^n A^1 \otimes A$, which is naturally filtered;
  specifically, $C^n_m$ is all finite sums of expressions of the form
  $Z_1\wedge \ldots \wedge Z_n \otimes  X$, where $Z_{i_j} \in A_j$ ($i_j \ge 1$), $X \in A_k$
  ($k \in {\mathbb Z}$), and $i_1+ \cdots + i_n + k = m$. In particular, writing
  $\sigma = \sum_m \sigma_m$ (finite sum) for some $\sigma_m \in C^n_m$, we have
  $\sum_m\partial^\tau \sigma_m \in (C^{n-1})^l$, by hypothesis. But from this is follows
  that $\partial^\tau \sigma_j=0$ for all $j< l$, because $\partial^\tau $ maps $C^n_m$ to
  $C^{n-1}_m$, for all $m$. We may therefore take
  $\tilde \sigma = \sum_{j\ge l} \sigma_j$.
\end{proof}
\begin{notation}
  If $\tau'$ is also model data on $A$, and if $\tau'=(\Adjoint_\psi)_*\tau $, for some
  $\psi \in \Gamma(T^*\!M \otimes A)$, homogeneous of degree $l$, then we will write
  $\tau\equivalent{l} \tau' $.
\end{notation}

\begin{lemmaB}
  If $\sigma \in \Gamma(\wedge^nA^1 \otimes A)$ and $\tau'\equivalent{l}\tau $, then
  $\partial^{\tau'} \sigma -\partial^\tau \sigma $ is homogeneous of degree $l + 1$
\end{lemmaB}
\begin{proof}
  Expanding the definition of $\Adjoint_\psi $ (Equation \eqrefs{deformations}{opal2a}) it is
  not difficult to see that $\tau'\equivalent{l}\tau $ implies that $\tau' - \tau $ is
  homogeneous of degree $l$. The lemma follows easily from this fact and the definition of
  $\partial^\tau$ (Equation \eqrefs{normalization}{form1}).
\end{proof}
\begin{proof}[Proof of theorem]
  Recall that {\df normal} means $\partial^\tau \kappa =0$. To prove existence of normal
  model data it suffices to prove the following:
  \begin{aside}
    If $\partial^\tau\kappa $ is homogeneous of degree $l \ge 1$, then there exists model
    data $\tau'$ with $\tau'\equivalent{l} \tau $ such that $\partial^{\tau'}\kappa $ is
    homogeneous of degree $l + 1$, where $\kappa'$ is the model curvature of $\tau'$.
  \end{aside}
  For then the theorem follows from an induction on $l$, an induction anchored by the fact
  that $\kappa $ (and hence $\partial^\tau \kappa)$) is homogeneous of degree one
  (Proposition \ref{model_curvature}).

  So, suppose $\partial^\tau \kappa$ is homogeneous of degree $l\ge 1$. Recall that
  $\graded$ is a chain map between the chain complexes \eqrefs{homology}{chain3} and
  \eqrefs{homology}{chain4}, so that we have the identity
  \begin{equation}
    \label{wood0}
    \partial^*\circ \graded_l = \graded_l \circ \partial^\tau.
  \end{equation}
  Identifying $T^*\!M$ with $A^1$ using the Killing form of $\tau$, there exists, by Lemma
  A, $\tilde\kappa \in \Gamma(\wedge^2 T^*\!M \otimes A)$, homogeneous of degree $l$, such
  that $\partial^\tau \tilde \kappa = \partial^\tau \kappa $.  From the boxed equation in
  \eqrefs{hodge}{nontrivial}, there exists $\psi \in \Gamma(T^*\!M \otimes A)$,
  homogeneous of degree $l$, such that
  $\graded_l(\tilde \kappa) - \partial \graded_l(\psi)$ lies in $\kernel \partial^*$, so
  that $\partial^* \graded_l(\tilde \kappa) = \partial^* \partial \graded_l (\psi
  )$. Applying \eqref{wood0} to the left-hand side, we can write this as
  \begin{equation}
    \label{wood1}
    \graded_l(\partial^\tau \kappa ) = \partial^* \partial \graded_l(\psi),
  \end{equation}
  which eliminates the auxiliary variable $\tilde \kappa$. On the other hand, if we take
  $\tau' =(\Adjoint_\psi)_*\tau $, then Proposition \ref{curv_deform} tells us that
  $\kappa' - \kappa $ is homogeneous of degree $l$ with
  \begin{equation}
    \label{wood2}
    \graded_l(\kappa'-\kappa) = -\partial \graded_l(\psi).
  \end{equation}
  Now as both $\kappa' - \kappa $ and $\partial^\tau \kappa $ are homogeneous of degree
  $l$, so is $\partial^\tau \kappa'$. But, applying $\partial^*$ to both sides of
  \eqref{wood2} and applying \eqref{wood0} again on the left, we obtain
  $\graded_l(\partial^\tau \kappa' - \partial^\tau \kappa) = -\partial^* \partial
  \graded_l(\psi)$, which can accordingly be written
  \begin{equation*}
    \graded_l(\partial^\tau \kappa')
    = \graded_l(\partial^\tau \kappa) - \partial^* \partial
  \graded_l(\psi)
  \end{equation*}
  Substituting \eqref{wood1}, we obtain $\graded_l(\partial^\tau \kappa')=0 $ which, on
  account of Lemma B, shows $\graded_l(\partial^{\tau'}\kappa') =0$, as required.

  By construction, the normal model data $\tau'$ is a $\psi$-deformation of $\tau
  $. Keeping Theorem \ref{uniquely_determined} in mind, it follows, as a special case of
  Proposition \eqrefs{deformations}{saturn5}, that $(A', \tau')$ is an infinitesimal parabolic
  geometry with the same Levi reduction as $(A, \tau)$, and in the global case that
  $({\mathcal G}, \tau')$ is a parabolic geometry with the same Levi reduction as
  $({\mathcal G}, \tau)$.

\end{proof}

\subsection{Harmonic curvature as an obstruction to symmetry}\label{top_curvature}
Recall that for model curvature to vanish, it suffices that the harmonic curvature
vanishes (Corollary \ref{harmonic}). The proof of the this result rested on Theorem
\eqrefs{harmonic}{poker3}, restated here for convenience:

\begin{proposition}
  Let $\kappa $ be the model curvature of a regular and normal parabolic geometry
  $({\mathcal G} , \tau)$. Then if $\kappa $ is homogeneous of $l \ge 1$ and
  $(\kappa_{\mathrm H})_l = 0$, then $\kappa $ is homogeneous of degree $l + 1$.
\end{proposition}
\begin{proof}
  Choose any Weyl gauge $\epsilon$ to get a splitting
  $\tilde \Phi_\epsilon \colon \wedge^2 \graded(A^1) \otimes \graded(A) \rightarrow
  \wedge^2 A^1 \otimes A$, as in Proposition \ref{homology}. Then, as $\kappa $ is
  homogeneous of degree $l$, we may write
  $(\tilde \Phi_\epsilon)^*\kappa =\sum_{i\ge l} \kappa_i$, for some sections $\kappa_i$
  of $(\wedge^2 \graded(A^1) \otimes \graded(A))_i$ satisfying $\partial^* \kappa_i =0$,
  because $\partial^\tau \kappa = 0$. Since $(\kappa_{\mathrm H})_l = 0$, we can see that
  the homology class $[\kappa_l]$ must vanish. This follows from the proposition just
  cited and the definition of the natural grading of $H_2(A^1, A)$ given there. However,
  $\partial \graded_l(\kappa) = 0$, by Proposition \ref{section_bianchi}, i.e.,
  $\partial \kappa_l = 0$, so that in fact
  $\kappa_l \in \kernel \partial_2 \cap \kernel\partial^*_2 = \kernel \square_2$. But,
  according to Theorem \ref{hodge}, the map
  $\omega \rightarrow [\omega] \colon \kernel\partial_2^* \rightarrow H_2(\graded(A^1),
  \graded(A))$ is, when restricted to $\kernel \square_2$, injective. Since $[\kappa_l]=0$,
  so then $\kappa_l=0$, and we conclude $\kappa $ is homogeneous of degree $l + 1$.
\end{proof}

\subsection{Uniqueness up to Weyl gauge transformations}\label{un}

\begin{theorem}[Uniqueness] Let $({\mathcal G}, \tau)$ be a regular parabolic
  geometry and let ${\mathfrak g} $ be Lie algebra model for $\tau $, identified with a
  graded reductive Lie algebra, as detailed at the end of \ref{harmonic}. Assume
  $H^1({\mathfrak g}_-, {\mathfrak g})^1=0$.  Then if $({\mathcal G}, \tau')$ is second
  parabolic geometry with $\graded_0(\tau')=\graded_0(\tau)$, then if both $\tau $ and
  $\tau'$ are normal, then $\tau' = q_*\tau$ for some infinitesimal Weyl gauge
  transformation $q$.
\end{theorem}

\begin{proof}
  Write $\tau_1 := \tau$. We will construct a sequence of infinitesimal Weyl gauge
  transformations $q_1, q_2, q_3, \ldots$, such that for any $l > 1$,
  $\tau' \equivalent{l} \tau_l$ (see Notation \ref{normalization_}) where
  $\tau_l := (q_{l-1})_*\tau_{l-1}$. Then, for sufficiently large $k$, we will have
  $\tau' = \tau_k$, because any $\psi \in \Gamma(T^*\!M \otimes A)$ of sufficiently high a
  degree of homogeneity vanishes, making $\Adjoint_\psi $ the identity. In that case, we
  will have $\tau' = q_* \tau$, where $q = q_{k-1} \circ q_{k-2} \circ \cdots \circ q_1$,
  and the theorem will be proven, because normality is preserved by Weyl gauge
  transformations (Theorem \ref{transform_}), as is regularity, because we will have
  $\graded_0(\tau')=\graded_0(\tau)$, by Lemma \ref{deformations}.

  So, for an induction, suppose $\tau_l$ is model data such that
  \begin{gather}
    \tau' \equivalent{l} \tau_l,\label{eins}\\
    \text{$\tau_l$ is regular with normal curvature $\kappa_l$,}\label{zwei}
  \end{gather}
  If $l=1$, \eqref{eins} holds, by Proposition \eqrefs{deformations}{saturn1};
  \eqref{zwei} holds by hypothesis. This anchors our induction. Our remaining task is to
  construct an infinitesimal Weyl gauge transformation $q_l$ such that
  $\tau_{l+1} := (q_l)_*\tau_l$ satisfies the above with $l$ replaced with $l + 1$.

  Now \eqref{eins} is shorthand for the existence of some
  $\psi \in \Gamma(T^*\!M \otimes A)$, homogeneous of degree $l$, such that
  $\tau'=(\Adjoint_\psi)_*\tau_l$. By Proposition \ref{curv_deform}, $\kappa' - \kappa_l$
  will be homogeneous of degree $l$, with
  \begin{equation}
    \label{vier}
    \graded_l(\kappa' - \kappa_l) = -\partial\graded_l(\psi).
  \end{equation}
  Since $\tau_l $ is normal,
  $\partial^{\tau_l} \kappa' = \partial^{\tau_l}(\kappa' - \kappa_l) -
  \partial^{\tau_l}\kappa_l= \partial^{\tau_l}(\kappa' - \kappa_l)$ must be homogeneous of
  degree $l$. Since $\partial^{\tau'}\kappa' = 0$, it follows from Lemma B, that
  $\graded_l(\partial^{\tau_l}\kappa')=0$. Applying $\partial^*$ to both sides of
  \eqref{vier}, using the normality of $\kappa_l$, and the identity
  $\partial^*\circ \graded_l=\graded_l \circ \partial^{\tau_l}$, we obtain
  $\graded_l(\partial^{\tau_l}\kappa') = -\partial^*\partial \graded_l(\psi)$, and whence
  $\partial^*\partial \graded_l(\psi) = 0$. So $\partial \graded_l(\psi) = 0$, by the
  direct sum decomposition on the left of \eqrefs{hodge}{nontrivial}. But the hypothesis
  on vanishing cohomology and Proposition \ref{hodge} show that
  $H^1(\graded(TM), \graded(A))_l=0$, so that there exists $Z \in \Gamma(A^l)$ such that
  \begin{equation}
    \label{funf}
    \graded_l(\psi) = \partial \graded_l(Z).
  \end{equation}

  Define $q_l := e^{-\adjoint_Z}$, and $\tau_{l+1}=(q_l)_*\tau_l$. Applying Proposition
  \ref{gauge_transforms}, there exists $\tilde \psi \in \Gamma(T^*\!M \otimes A)$,
  homogeneous of degree $l$, such that $\tau_{l+1} = (\Adjoint_{\tilde \psi})_*\tau_l$ and
  $\tilde \psi(\#X) \equiv \tau_l(Z, X) \modulo A^{k+l+1}$, whenever $X \in A^k$. This
  last can be expressed compactly as $\graded_l(\tilde \psi) = \partial \graded_l(Z)$. By
  \eqref{funf} we therefore have $\graded_l(\psi - \tilde \psi) = 0$, i.e.,
  $\psi - \tilde \psi $ is homogeneous of degree $l + 1$. Viewing $\psi, \tilde \psi $ as
  sections of the totally intransitive groupoid $\automorphism(TM, A)$, we conclude, using
  the product formula \eqrefs{kernel}{clost2}, that $\psi \tilde \psi^{-1}$ is also
  homogeneous of degree $l + 1$, which is relevant because
  \begin{equation*}
    \tau' = (\Adjoint_\psi)_*\tau_l =
      (\Adjoint_\psi)_*(\Adjoint_{\tilde \psi^{-1}})_*\tau_{l+1}
    = (\Adjoint_{\psi \tilde \psi^{-1}})_*\tau_{l+1},
  \end{equation*}
  which shows $\tau' \equivalent{l+1} \tau_{l+1}$. The new model curvature $\tau_{l+1}$ is
  normal and regular because $\tau_l$ is normal and regular, and these properties are
  preserved by infinitesimal Weyl gauge transformations.
\end{proof}


\subsection{Prolongation as functor}\label{functor}
Morphisms of filtered Lie algebroids and Lie groupoids have been described in
\ref{morphisms} (where morphisms of abstract Levi structures were also defined). As it
suffices for current purposes, we only define morphisms of (non-abstract) Levi structures
that cover the identity on $M$. So, a {\df morphism} of infinitesimal Levi structures
$(B, R, T)$ and $(\tilde B, \tilde R, \tilde T)$ consists of a morphism
$q \colon B \rightarrow \tilde B$ of filtered Lie algebroids covering the identity such
that the induced morphims of graded vector bundles
\begin{gather*}
  q_* \colon \graded(TM)\oplus B^0 \oplus \graded(T^*\!M)
     \rightarrow \graded(TM)\oplus \tilde B^0 \oplus \graded(T^*\!M)\\
  (V, C, Z) \mapsto (V, qC, Z)
\end{gather*}
is: (i) a morphism of Lie algebra bundles, with respect to the brackets $T$ and
$\tilde T$; and (ii) an intertwining of the infinitesimal representations $R$ and
$\tilde R$. Note that (i) implies that $T$ and $\tilde T$ have the same restrictions to
$\graded(TM)$ and $\graded(T^*\!M)$. A {\df morphism} of Levi structures
$({\mathcal H}, R, T)$ and $(\tilde {\mathcal H}, \tilde R, \tilde T)$ is a morphism
$Q \colon {\mathcal H} \rightarrow \tilde {\mathcal H} $ of filtered Lie groupoids such
that: (i) $dQ$ is a morphism of the corresponding infinitesimal Levi structures; and (ii)
$(dQ)_*$ intertwines the {\em global} representations $R$ and $\tilde R$.

The {\df prolongation} of a morphism $q$ of abstract infinitesimal Levi
structures as above is the morphism of firmly filtered Lie algebroids
\begin{gather*}
  B \oplus_R \graded(T^*\!M) \rightarrow \tilde B \oplus_{\tilde R} \graded(T^*\!M)\\
  (X, Y) \mapsto (qX, Y).
\end{gather*}
The {\df prolongation} of a morphism $Q$ of global Levi structures as above is
the morphism of firmly filtered Lie groupoids,
\begin{align*}
  {\mathcal H} \times _R \exp\graded(T^*\!M)
  &\rightarrow \tilde {\mathcal H}  \times_{\tilde R} \exp \graded (T^*\!M)\\
  (h, k) &\mapsto  (Q(h), k).
\end{align*}

With these definitions, one readily establishes the following facts:
\begin{proposition}
  Abstract prolongation is a functor from the category of infinitesimal or global
  Levi geometries to the category of firmly filtered Lie algebroids, resp., Lie
  groupoids.
\end{proposition}

\begin{corollary}
  If two infinitesimal or global Levi structures are isomorphic, then so are their
  corresponding prolongations.
\end{corollary}

\subsection{The equivalence problem}\label{equivalence_}

Recall that we can associate a graded semisimple Lie algebra model ${\mathfrak g} $ with
any parabolic geometry or Levi structure, and that vanishing of
$H({\mathfrak g}_-, {\mathfrak g})^1$ depends only on the isomorphism class in each case.

\begin{theorem}[Equivalence]
  The map that sends a regular normal parabolic geometry over $M$ to its corresponding
  Levi reduction, induces a bijection $\Xi$ between: (i) isomorphism classes of regular
  normal parabolic geometries over $M$ satisfying
  $H({\mathfrak g}_-, {\mathfrak g})^1 = 0$; and (ii) isomorphism classes of regular Levi
  structures over $M$ satisfying $H({\mathfrak g}_-, {\mathfrak g})^1 = 0$.
\end{theorem}

\begin{proof}
  The surjectivity of $\Xi$ follows immediately from the Existence Theorem
  \ref{existence_} and Normalization Theorem \ref{normalization_}. To prove injectivity,
  suppose that $\gamma$ and $\tilde \gamma$ are isomorphism classes of parabolic
  geometries that have representatives $({\mathcal G}, \tau)$ and
  $(\tilde{\mathcal G}, \tilde \tau)$ with isomorphic Levi reductions, ${\mathcal L}$ and
  $\tilde {\mathcal L}$. Our task is to show that $\gamma = \tilde \gamma $.

  By Corollary \ref{functor}, the prolongations $\prolongation ({\mathcal L})$ and
  $\prolongation (\tilde {\mathcal L})$ of ${\mathcal L}$ and $\tilde {\mathcal L}$ are
  isomorphic, as filtered Lie groupoids. So there exists a Lie groupoid isomorphism
  $Q \colon \prolongation(\tilde {\mathcal L}) \rightarrow \prolongation({\mathcal L})$
  such that $q:=dQ$ is filtration-preserving.

  On the other hand, every regular parabolic geometry is isomorphic, as a filtered Lie
  groupoid, to the prolongation of its Levi reduction (Theorem \eqrefs{inflevi}{cch3},
  specialized to the parabolic case) so that
  ${\mathcal G} \cong \prolongation( {\mathcal L})$ and
  $\tilde {\mathcal G} \cong \prolongation( \tilde {\mathcal L})$. We push the model data
  $\tau $ and $\tilde \tau $ to $\prolongation({\mathcal L})$ and
  $\prolongation(\tilde {\mathcal L})$; denoting these by the same symbols $\tau $ and
  $\tilde \tau$, Theorem \ref{transform_} shows that
  $(\prolongation( {\mathcal L}), \tau)$ and
  $(\prolongation( \tilde {\mathcal L}), \tilde \tau)$ are also regular normal parabolic
  geometries. By construction, they are representatives of $\gamma $ and $\tilde \gamma $
  respectively.

  According to Theorem \ref{transform_}, $\tau' := Q_* \tilde \tau $ is regular normal
  model data on $\prolongation({\mathcal L})$ that makes
  $(\prolongation({\mathcal L}), \tau')$ into a parabolic geometry. By the Uniqueness
  Theorem \ref{un}, there exists an infinitesimal Weyl gauge transformation
  $r \colon A \rightarrow A$ such that $\tau' = r_*\tau$. But every infinitesimal Weyl
  gauge transformation is integrated by a global Weyl gauge transformation, i.e.,
  $r = dR$, for some Weyl gauge transformation
  $R \colon {\mathcal G} \rightarrow {\mathcal G} $, which is, in particular, an
  isomorphism $({\mathcal G}, \tau) \rightarrow ({\mathcal G}, \tau')$. But then, by
  construction, $Q^{-1} \circ R$ is an isomorphism
  $(\prolongation({\mathcal L}), \tau) \rightarrow (\prolongation((\tilde {\mathcal L}),
  \tilde \tau)$, which shows $\gamma = \tilde \gamma $.

\end{proof}


\appendix
\refreshpage
\section{Reductive Lie algebras and their parabolic subalgebras}\label{lie_algebra_facts}
The material below is mostly adapted from \cite{Calderbank_Noppakaew_16}, to which the
reader is referred for omitted proofs. The results there are established by rather direct
methods the reader will not readily find in standard texts, which tend to emphasize
semisimple Lie algebras and algebraically closed base fields.

In this appendix all Lie algebras are finite-dimensional over a field of characteristic
zero.

\subsection{Nilpotency}\label{nilpotency}
A subalgebra ${\mathfrak m} \subset {\mathfrak g} $ is a {\df nil subalgebra} if $\rho(X)$
is nilpotent for any representation $\rho \colon {\mathfrak g} \rightarrow \gl(V)$. The
{\df nilpotent radical} of ${\mathfrak g} $, denoted here by $\nil({\mathfrak g})$, is the
largest nil subalgebra that is also an ideal of ${\mathfrak g} $. See
\cite{Calderbank_Noppakaew_16} for other characterizations.\footnote{For perfect Lie
  algebras, such as semisimple ones, the nilpotent radical coincides with the so-called
  {\em nilradical}, sometimes denoted $\nil({\mathfrak g})$ also, but it may be different
  more generally.}

\subsection{Reductive Lie algebras and gradings thereof}\label{par}
Recall that a Lie algebra is {\df reductive} if it satisfies
\eqref{gra3}, \eqref{gra1}, or \eqref{gra2} below.

\begin{proposition}[Theorem 2.20 of \cite{Calderbank_Noppakaew_16}]
  The following are equivalent:
  \begin{conditions}
  \item\label{gra3} $\nil({\mathfrak g})=0$.
  \item\label{gra1}
    ${\mathfrak g} $ admits a faithful, completely reducible representation.
  \item\label{gra2}
    There exists a non-degenerate trace-form $B_\rho$ on ${\mathfrak g}$.
  \end{conditions}
  Moreover, for any Lie algebra ${\mathfrak g} $, the quotient
  ${\mathfrak g}/\nil({\mathfrak g})$ is reductive, and called the {\df reductive Levi
    quotient} of ${\mathfrak g} $.

\end{proposition}
\noindent%
Recall here that a {\df trace-form} $B_\rho$ is defined by
$B_\rho(X, Y)=\trace(\rho_X \circ \rho_Y)$, for some representation
$\rho \colon {\mathfrak g} \rightarrow \gl(V)$, and this is always $\adjoint$-invariant;
$B_{\adjoint}$ is the {\df Killing form}, which is non-degenerate when ${\mathfrak g} $ is
semisimple (a direct sum of simple ideals) by Cartan's criterion \cite[Proposition
2.19]{Calderbank_Noppakaew_16}.

\begin{theorem}[Theorem 2.20 of \cite{Calderbank_Noppakaew_16}]
  If ${\mathfrak g} $ is reductive, then:
  \begin{conditions}
  \item\label{hra1} ${\mathfrak g} = Z({\mathfrak g})\oplus [{\mathfrak g}, {\mathfrak g}]$
    and this decomposition is orthogonal, for any non-degenerate trace-form.
  \item\label{hra2} $[{\mathfrak g}, {\mathfrak g}]$ is semisimple.
  \item\label{hra3} A derivation $D \in \selfmorphism({\mathfrak g}) $ is of the form
    $D(X) = [Y, X]$, for some $Y \in {\mathfrak g} $ (i.e, is inner) if and only if $D$
    vanishes on $Z({\mathfrak g})$, in which case $Y$ is uniquely determined by requiring
    $Y \in [{\mathfrak g}, {\mathfrak g}]$.
  \end{conditions}
\end{theorem}

The $\adjoint$-invariance of a non-degenerate trace-form has strong consequences for the
components in any grading of a reductive Lie algebra, which we need later on:

\begin{lemma}
  Let ${\mathfrak g} $ be a graded reductive Lie algebra
  and $B$ a trace-form. Then:
  \begin{conditions}
  \item\label{ira2} If $B$ is the Killing-form, then its kernel ${\mathfrak g} ^\perp$ is
    exactly $Z({\mathfrak g})$.
  \end{conditions}
  If $Z({\mathfrak g}) \subset {\mathfrak g}_0$, then:
 \begin{conditions}
  \item\label{ira0} There exists a unique grading element
    $E \in {\mathfrak g}_0\cap[{\mathfrak g}, {\mathfrak g}]$.
  \item\label{ira1} With respect to $B$, we have ${\mathfrak g}_j \perp {\mathfrak g}_k$
    whenever $j+k \ne 0$.
  \item\label{ira3} If ${\mathfrak g}^\perp \subset {\mathfrak g}_0$ (e.g., $B$ is the
    Killing form) then ${\mathfrak g}_j$ and ${\mathfrak g}_{-j}$ are $B$-dual, for all
    $j\ne 0$, and in particular $|{\mathfrak g}| = m$ for some $m \ge 0$ (see Notation
    \ref{filtered}).
  \item\label{ira4} If $B$ is non-degenerate, then ${\mathfrak g}_j$ and
    ${\mathfrak g}_{-j}$ are $B$-dual for all $j \in {\mathbb Z}$, and
    $|{\mathfrak g}| = m$, for some $m\ge 0$.
  \end{conditions}
\end{lemma}

\begin{proof}
  \eqref{ira2}: Suppose that $B$ is the Killing form. Then $\adjoint_X = 0$ for any
  $X \in Z({\mathfrak g})$, which shows $Z({\mathfrak g}) \subset {\mathfrak g}^\perp$. To
  prove the reverse inclusion, note that for any $X, Y \in {\mathfrak g}$, the derivations
  $\adjoint_X$, $\adjoint_Y$, and hence $\adjoint_X \circ \adjoint_Y$, send
  $Z({\mathfrak g})$ to $0$ and $[{\mathfrak g} , {\mathfrak g}]$ to itself. It follows
  from \eqref{hra1} that $B(X, Y) = B_\mathrm{ss}(X_{\mathrm{ss}}, Y_{\mathrm{ss}})$,
  where $B_\mathrm{ss}$ is the Killing form on $[{\mathfrak g}, {\mathfrak g}] $, while
  $X_{\mathrm{ss}}$ and $Y_{\mathrm{ss}}$ are the projections of $X$ and $Y$ along
  $Z({\mathfrak g})$ onto $[{\mathfrak g}, {\mathfrak g}]$ , which is semisimple,
  according to \eqref{hra2}. In particular, $B_{\mathrm{ss}}$ is non-degenerate, and
  therefore $X \in {\mathfrak g}^\perp$ only if $X_\mathrm{ss}=0$, i.e.,
  $X \in Z({\mathfrak g})$.

  \eqref{ira0}: Define $D(X) = jX$, for $X \in {\mathfrak g}_j$. Then $D$ is a
  derivation vanishing on ${\mathfrak g}_0\supset Z({\mathfrak g})$. By \eqref{hra3},
  there exists a unique $E \in [{\mathfrak g}, {\mathfrak g}]$ such that $D(X) = [E, X]$,
  and $E \in {\mathfrak g}_0$ because $[E, E]=0$.

  \eqref{ira1}: For any $X \in {\mathfrak g}_j$ and $Y \in {\mathfrak g}_k$, we have
  $(j + k) B(X, Y) = B([E, X], Y) + B(X, [E, Y]) = 0$, by $\adjoint$-invariance of $B$.



  \eqref{ira3} \& \eqref{ira4}: Suppose
  ${\mathfrak g}^\perp \subset {\mathfrak g}_0$.  Let $X \in {\mathfrak g}_j$ and suppose
  $B(X, Y) = 0$ for all $Y \in {\mathfrak g}_{-j}$. Then in fact, $B(X, Y)=0$ for all
  $Y \in {\mathfrak g}$, by \eqref{ira1}, i.e., $X \in {\mathfrak g}^\perp$. So
  \eqref{ira4} is clear. If ${\mathfrak g}^\perp \subset {\mathfrak g}_0$,
  then $X \in {\mathfrak g}_j\cap {\mathfrak g}_0$ and so \eqref{ira3} holds.
\end{proof}

\subsection{Parabolic subalgebras and Levi quotients}
\label{parabolic_characterizations}
Recall that a subalgebra ${\mathfrak p} \subset {\mathfrak g} $ is {\df parabolic} if it
contains the normalizer of a maximial nil subalgebra \cite{Calderbank_Noppakaew_16}.

\begin{theorem}[Theorem 3.4 of \cite{Calderbank_Noppakaew_16}]
  Let ${\mathfrak g} $ be reductive and fix an arbitrary non-degenerate
  trace-form. Then the following are equivalent:
  \begin{conditions}
  \item\label{par1} ${\mathfrak p} \subset {\mathfrak g} $ is parabolic.
  \item\label{par2} ${\mathfrak p}^\perp \subset [{\mathfrak g}, {\mathfrak g}]$ and
    ${\mathfrak g}^\perp$ is nilpotent.
  \item\label{par3} ${\mathfrak g}^\perp$ is a nil subalgebra of ${\mathfrak g} $.
  \item \label{par4} ${\mathfrak p}^\perp \subset {\mathfrak p} $ and
    $N_{\mathfrak g}({\mathfrak p}) = {\mathfrak p}$.
  \item\label{par5} ${\mathfrak p}^\perp=\nil({\mathfrak p})$.
  \end{conditions}
\end{theorem}
\noindent%
In particular, \eqref{par5} shows that ${\mathfrak p}^\perp $ does not depend on the
choice of trace-form.

Proposition \ref{in_terms_of_gradings} characterizes parabolics in terms of gradings.

\begin{remark}
  If ${\mathfrak g} $ is reductive {\em and the base field is algebraically closed}, then
  the normalizers of mimimal subalgebras coincide with the Borel (maximal solvable)
  subalgebras. However, Borel subalgebras play no role here.
\end{remark}

\subsection{Canonical filtrations}\label{can}
When ${\mathfrak g}^1 \subset {\mathfrak g}^0 \subset {\mathfrak g} $ and
${\mathfrak g}^1$ is an ideal of ${\mathfrak g}^0$ then we have the {\df
  pre-filtration} associated with $({\mathfrak g}^0, {\mathfrak g}^1)$, introduced in
\ref{canonical_filtrations_}.

\begin{proposition}
  Fix a non-degenerate trace-form on a reductive Lie algebra ${\mathfrak g}$ and let
  ${\mathfrak p} \subset {\mathfrak g} $ a parabolic subalgebra.
  \begin{conditions}
  \item\label{hosp1} The pre-filtration of ${\mathfrak g} $ associated with
    $({\mathfrak p}, {\mathfrak p}^\perp )$, which is independent of the choice of form,
    is well-defined and is even a bone fide Lie algebra filtration, with
    $|{\mathfrak g}| = m $ for some $m\ge 0$ (see Notation \ref{filtered}). This is the
    {\df canonical filtration} associated with ${\mathfrak p} $.
  \item\label{hosp2} In the canonical filtration,
    $({\mathfrak g}^j)^\perp = {\mathfrak g}^k$, whenever $j + k =1$.
  \end{conditions}
\end{proposition}
\noindent%

\begin{proof}
  Since ${\mathfrak p} $ is parabolic, ${\mathfrak p}^\perp $ is an ideal of
  ${\mathfrak p} $, by Theorem \ref{par}. In particular Lemma \ref{canonical_filtrations_}
  applies with ${\mathfrak g}^0:={\mathfrak p} $ and
  ${\mathfrak g}^1:={\mathfrak p}^\perp$, so that the pre-filtration associated with
  $({\mathfrak p}, {\mathfrak p}^\perp)$ is well-defined.  The triviality
  $({\mathfrak g}^0)^\perp={\mathfrak g}^1$ anchors a straightforward inductive argument
  that establishes \eqref{hosp2}. Since ${\mathfrak p}^\perp $ is nilpotent, there is
  $m \ge 0$ such that ${\mathfrak g}^m\ne 0$ but ${\mathfrak g}^{m+1} = 0$. In that case
  ${\mathfrak g}^{-m} = ({\mathfrak g}^{m+1})^\perp = \{0\}^\perp = {\mathfrak g} $, while
  ${\mathfrak g}^{-m+1}=({\mathfrak g}^m)^\perp \ne {\mathfrak g}$. This shows the
  pre-filtration is a filtration and $|{\mathfrak g}|=m$.
\end{proof}

\begin{theorem}[Proposition 3.9 of \cite{Calderbank_Noppakaew_16}]
  Let ${\mathfrak g} $ be a reductive Lie algebra. Then, with respect to the canonical
  filtration associated with any parabolic subalgebra
  ${\mathfrak p} \subset {\mathfrak g}$, $\graded({\mathfrak g})$ is a reductive Lie
  algebra with centre lying in $\graded({\mathfrak g})_0$.
\end{theorem}

While a proof of the theorem is given in \cite{Calderbank_Noppakaew_16}, some details were
not immediatlely obvious to us, and we accordingly provide them below.
\begin{proof}

  Let $B_\rho $ be a non-degenerate trace form on ${\mathfrak g} $. By \eqref{hosp2}, we
  have ${\mathfrak g}^j \perp {\mathfrak g}^k$, whenever $j + k =1$, which allows us to
  drop $B_\rho$ to an invariant quadratic form $Q$ on $\graded({\mathfrak g})$ satisfying
  $Q(\graded({\mathfrak g}_j), \graded({\mathfrak g}_k)) = 0$ for $j + k \ne 0$ and
  $Q(\graded_j(X), \graded_{-j}(Y)) = B_\rho(X, Y)$ for $X \in {\mathfrak g}^j$ and
  $Y \in {\mathfrak g}^{-j}$, $j \in {\mathbb Z}$. Since
  $({\mathfrak g}^j)^\perp = {\mathfrak g}^k$, whenever $j + k =1$, $Q$ is
  non-degenerate. To show $\graded({\mathfrak g})$ is reductive, it therefore suffices to
  show $Q=B_{\bar \rho}$ for some representation $\bar\rho$ of $\graded({\mathfrak
    g})$. If we can find a filtration of $V$ that makes $\rho $ into a {\em filtered}
  representation, i.e., such that
  \begin{equation}\label{dep}
        \rho_{{\mathfrak g}^j}(V^k) \subset V^{j+k},
  \end{equation}
  for all $j, k \in {\mathbb Z} $, then we can take $\bar \rho $ to be the corresponding
  representation of $\graded({\mathfrak g})$ on $\graded(V)$ \cite[Proposition
  2.14]{Calderbank_Noppakaew_16}.

  To construct such a filtration of $V$, first define $V^j=0$, for $j>0$, and let
  $V^0 = \{v \in V \suchthat \rho_{{\mathfrak g}^1}(v) = 0\}$. Now $V^0\ne 0$, by Engel's
  theorem \cite[Lemma 2.7]{Calderbank_Noppakaew_16}, because
  ${\mathfrak g}^1=\nil({\mathfrak p})$ acts nilpotently under $\rho $. For $j\le -1$, we
  inductively define $V^j=\{v \in V\suchthat \rho_{{\mathfrak g}^1}v \subset
  V^{j+1}\}$. Since ${\mathfrak g}^1$ acts nilpotently on $V$, it acts nilpotently on
  every space $V/V^k$, $k \in {\mathbb Z} $, and so $V^k$ is a proper subset of $V^{k-1}$
  by Engel's theorem, and $\cup_j V^j =V$, by finite-dimensionality.

  By definition, \eqref{dep} holds for $j=1$ and all $k \in {\mathbb Z} $. For $j\ge 2 $,
  we have ${\mathfrak g}^j = [{\mathfrak g}^1, {\mathfrak g}^{j-1}]$, so a simple
  induction shows that \eqref{dep} holds for all $j \ge 2$ and $k \in {\mathbb
    Z}$. Finally, supposing $j \le 0$, we have \eqref{dep} if $k \ge - j + 1$, because
  $V^k = 0$ in that case. So, to deal with the $j \le 0$ case, we proceed with an
  induction, supposing \eqref{dep} holds whenever $k + j \ge m$, for some $m \ge 1$, and
  show it must also hold if $k + j \ge m - 1$.  So, supposing, $X \in {\mathfrak g}^j$ and
  $v \in V^k$, with $j + k \ge m - 1$, we need to show $\rho_{X^j}v \in V^{j+k}$, which
  means showing, for any $X^1 \in {\mathfrak g}^1$, that
  $\rho_{X^1}\rho_{X^j}v \in V^{j+k+1}$. But by the induction hypothesis, we will have
  $\rho_{[X^1, X^j]}v \in V^{j+k+1}$, because $[X^1, X^j] \in {\mathfrak g}^{j +1}$ and
  $(j + 1) + k \ge m $, while $\rho_{X^j}\rho_{X^1}v \in V^{j+k+1}$ because
  $\rho_{X^1}v \in V^{k+1}$ and $j + (k+1) \ge m$. So the desired result follows from the
  identity $\rho_{X^1}\rho_{X^j}v = \rho_{[X^1, X^j]}v + \rho_{X^j}\rho_{X^1}v$.

  If an element of $\graded({\mathfrak g})$ is central, then it's homogeneous components
  must be central. So suppose $\graded_j(X)\ne 0$ is central, for some
  $X \in {\mathfrak g}^j$ and, initially, suppose $j \ge 1$. Then
  \begin{equation}
    \label{pearl}
    {\mathfrak g}^j = [{\mathfrak g}^1, {\mathfrak g}^{j-1}].
  \end{equation}
  In case $j \ge 2$, this follows from the definition of ${\mathfrak g}^j$. In case
  $j =1$, this follows because
  $[{\mathfrak g}^1, {\mathfrak g}^0] = ([{\mathfrak p}^\perp, {\mathfrak
    p}]^\perp)^\perp=N_{\mathfrak g}({\mathfrak p}^\perp)^\perp = N_{\mathfrak
    g}({\mathfrak p})^\perp={\mathfrak p}^\perp={\mathfrak g}^1$. The fourth equality
  holds because parabolic subalgebras are self-normalizing (Theorem
  \eqrefs{par}{par4}). Regarding the rest of the argument, note that $\adjoint$-invariance
  of the trace-form guarantees
  $N_{\mathfrak g} ({\mathfrak p}) \subset [{\mathfrak p}, {\mathfrak p}^\perp]^\perp =
  N_{\mathfrak g}({\mathfrak p}^\perp)$ for {\em any} subspace
  ${\mathfrak p} \subset {\mathfrak g}$, so that the reverse inclusion
  $N_{\mathfrak g}({\mathfrak p}^\perp)\subset N_{\mathfrak g} ({\mathfrak p})$ follows
  from ${\mathfrak p}^{\perp \perp}={\mathfrak p}$, which we have by non-degeneracy. The
  point of \eqref{pearl} is that it shows
  $\graded({\mathfrak g})_j \subset [\graded({\mathfrak g}), \graded({\mathfrak g})]$. By
  Theorem \eqrefs{par}{hra1}, $\graded({\mathfrak g})_j$ must intersects the centre of
  $\graded({\mathfrak g})$ trivially, because $\graded({\mathfrak g})$ is reductive, as we
  have already shown. So $\graded_j(X)=0$, a contradiction, and therefore $j \le 0$.

  Since $\graded_j(X)$ is central, we have, in particular,
  \begin{equation}
    \label{pearl2}
    [X, {\mathfrak g}^1] \subset {\mathfrak g}^{j+2}.
  \end{equation}
  If $j = -1$, then we conclude $X \in N_{\mathfrak g}({\mathfrak g}^1)=N_{\mathfrak g}({\mathfrak p}^\perp)={\mathfrak p}={\mathfrak g}^0$ by preceding arguments. But again this implies the contradiction, $\graded_j(X)=0$.  If $j\ge -2$, then \eqref{pearl2} implies $X \in {\mathfrak g}^{j+1}$, by the definition of ${\mathfrak g}^{j+1}$, and again the disallowed $\graded_j(X)=0$ follows. The only remaining possibility is $j=0$, which proves the stated property of the centre.
\end{proof}
\begin{corollary}
  Let ${\mathfrak g} $ be a reductive Lie algebra filtered canonically by some parabolic
  subalgebra ${\mathfrak p}$. Then the associated graded $\graded({\mathfrak g})$ admits a
  unique grading element $E \in [\graded({\mathfrak g}), \graded({\mathfrak g})]$, so that
  ${\mathfrak g} $ and $\graded({\mathfrak g}) $ are isomorphic Lie algebras, and the
  parabolic ${\mathfrak p} $ contains $Z({\mathfrak g})$.
\end{corollary}
\begin{proof}
  The theorem and Lemma \eqrefs{par}{ira0} establish the existence of the grading element
  $E$. According to arguments recalled in \ref{splittings}, any lift
  $\epsilon \in {\mathfrak p}={\mathfrak g}^0$ of $E$ defines a Lie algebroid isomorphism
  $\Phi_\epsilon \colon \graded({\mathfrak g}) \rightarrow {\mathfrak g} $. Since
  $\graded({\mathfrak g})_0$ contains the centre, by the theorem, so must
  ${\mathfrak p} $, because of the isomorphism.
\end{proof}

\subsection{Parabolics in terms of gradings}\label{in_terms_of_gradings}
\begin{proposition}
  Suppose ${\mathfrak g}$ is reductive. Then a subalgebra ${\mathfrak p} $ is parabolic if
  and only if there exists a grading of ${\mathfrak g} $ such that
  $Z({\mathfrak g}) \subset {\mathfrak g}_0$ and
  ${\mathfrak p} = \oplus_{j\ge 0} {\mathfrak g}_j$. In that case the corresponding
    filtration, defined by ${\mathfrak g}^j:=\oplus_{i\ge j}{\mathfrak g}_i$, is the
    canonical filtration associated with ${\mathfrak p} $ if and only if ${\mathfrak g}_1$
    generates ${\mathfrak g}^1$, or equivalently, if
    ${\mathfrak g}^1 \supset {\mathfrak g}^2 \supset {\mathfrak g}^3 \supset \cdots $ is
    the lower central series of ${\mathfrak g}^1$.
\end{proposition}
\begin{proof}
  Suppose ${\mathfrak p} $ is parabolic and we filter ${\mathfrak g} $ with the canonical
  filtration defined by ${\mathfrak p}$. Then, as in the proof of the preceding corollary,
  we can identify ${\mathfrak g} $ with the associated graded $\graded({\mathfrak g})$ and
  have ${\mathfrak p} = \oplus_{j\ge 0}{\mathfrak g}_j$. Any element of $Z({\mathfrak g})$
  must commute with $E \in {\mathfrak g}_0$, so $Z({\mathfrak g}) \subset {\mathfrak p} $
  already forces $Z({\mathfrak g}) \subset {\mathfrak g}_0$.

  Conversely, suppose ${\mathfrak g} $ is a graded reductive Lie algebra with
  $Z({\mathfrak g}) \subset {\mathfrak g}_0$ and define
  ${\mathfrak p}:=\oplus_{j\ge 0}{\mathfrak g}_j$. Fix an arbitrary non-degenerate
  trace-form. Then, to show that ${\mathfrak p} $ is parabolic, it suffices, according to
  Theorem \ref{parabolic_characterizations}, to show that ${\mathfrak p}^\perp $ is
  nilpotent and ${\mathfrak p}^\perp\subset [{\mathfrak g}, {\mathfrak g}]$. Now suppose
  $j + k =1$. Then, writing ${\mathfrak g}^j := \oplus_{j'\ge j}{\mathfrak g}_{j'}$, we
  claim
  \begin{equation}\label{gluck}
    {\mathfrak g}^j = ({\mathfrak g}^k)^\perp.
  \end{equation}
  Indeed, for any $j'\ge j$ and $k' \ge k$, we have $j' + k' \ne 0$, so that
  ${\mathfrak g}_{j'} \perp {\mathfrak g}_{k'}$, by Lemma \eqrefs{par}{ira1}, and
  consequently ${\mathfrak g}^j \subset ({\mathfrak g}^k)^\perp$. But, counting
  dimensions, it's easy to see that ${\mathfrak g}^j$ and ${\mathfrak g}^k$ have
  complementary dimensions, if
  $\dimension({\mathfrak g}_i)=\dimension({\mathfrak g}_{-i})$ for all $i$, which is true,
  by Lemma \eqrefs{par}{ira4}. So \eqref{gluck} holds. In particular, taking $j=1$ and
  $k=0$, we have ${\mathfrak g}^1={\mathfrak g}^\perp$, which shows that
  ${\mathfrak p}^\perp$ is nilpotent. Also, as ${\mathfrak g}_0 \subset {\mathfrak p} $,
  we have
  ${\mathfrak p}^\perp \subset {\mathfrak g}_0^\perp \subset Z({\mathfrak g})^\perp =
  [{\mathfrak g}, {\mathfrak g}]$, by Theorem \eqrefs{par}{hra1}.

  It remains to show the filtration defined by the grading is the canonical filtration
  associated with ${\mathfrak p} $, under the additional assumption that ${\mathfrak g}_1$
  generates ${\mathfrak g}^1$. We leave it to the reader to establish the characterization
  of this condition in terms of the lower central series. As the canonical filtration also
  satisfies \eqref{gluck} for $j + k = 1$ (Proposition \eqrefs{can}{hosp2}) it suffices to
  show the filtration components of degree $j$ coincide, for $j\ge 0$. For $j=0$, this is
  tautological, and we just established the $j=1$ case. For the canonical filtration,
  ${\mathfrak g}^1 \supset {\mathfrak g}^2 \supset {\mathfrak g}^3 \supset \cdots $ is the
  lower central series, by definition, which finishes the proof.
\end{proof}

\subsection{Parabolic subalgebras are separating}\label{separating_}
The notion of a {\df separating} or {\df infinitesimally separating} subalgebra
${\mathfrak p} \subset {\mathfrak g} $ has been introduced in \ref{separating}.
\begin{proposition}
  Every parabolic subalgebra ${\mathfrak p} $ of a reductive Lie algebra $\mathfrak g$ is
  separating, and hence also infinitesimally separating.
\end{proposition}
The following proof was obtained after David Calderbank pointed out to the author a
similar proof for the infinitesimal case.
\begin{proof}
  Suppose $\phi \in \automorphism({\mathfrak g})$ fixes elements of ${\mathfrak p}$. By
  Theorem \ref{can} and its corollary, we may as well suppose ${\mathfrak g} $ is graded
  with ${\mathfrak p} =\oplus_{j\ge0}{\mathfrak g}_j$ and
  $Z({\mathfrak g}) \subset {\mathfrak g}_0$.  Supposing $j \ge 1$, it suffices to show
  $\phi$ fixes elements of ${\mathfrak g}_{-j}$. By uniqueness of the grading element $E$,
  we must have $\phi(E) = E$, which already shows that $\phi $ must map
  ${\mathfrak g}_{-j}$ to itself. Suppose $Y \in {\mathfrak g}_j$ is arbitrary, and let
  $B$ denote the Killing form. Then as $\phi \in \automorphism({\mathfrak g})$, we must
  have $B(\phi X, \phi Y) = B(X, Y)$, i.e., $B(\phi X, Y) = B(X, Y)$, because $\phi $
  fixes elements of ${\mathfrak g}_j$, as $j\ge 1$. So, by Lemma \eqrefs{par}{ira3}, we
  conclude that $\phi X = X$.
\end{proof}

\section{The space of splittings of a filtered Lie algebra}
\label{appendix_splittings}
In this section we prove Lemma \ref{splittings}, which applies to arbitrary graded Lie
algebras, not just reductive ones. While a known result, we have given a formulation fit
for current purposes. For convenience, here is a restatement:

\begin{lemma}
  Let $\mathfrak g$ be a filtered Lie algebra and let $\epsilon \in {\mathfrak g}^0 $ be a
  lift of some grading element $E \in \graded({\mathfrak g})$. Let $G^0$ be {\em any} Lie
  group integrating ${\mathfrak g}^0 $, and let $G^1 \subset G^0$ be the connected Lie
  subgroup with Lie algebra ${\mathfrak g}^1$. Then:
  \begin{conditions}
  \item Under the adjoint action, $G^1$ acts freely and transitively on the affine space
    $\epsilon + {\mathfrak g}^1\subset {\mathfrak g}^0$, and consequently on $E$-splittings of
    ${\mathfrak g} $. In particular, $G^1$ is simply connected (i.e.,
    $G^1 \cong \exp({\mathfrak g}^1)$) so that the infinitesimal adjoint action of
    ${\mathfrak g}^1$ on ${\mathfrak g} $ has a unique globalization
    $\Adjoint\colon G^1 \rightarrow \automorphism({\mathfrak g})$ extending the adjoint
    action just mentioned.\label{splittings1_}
  % \item For any $g \in G^1$, $\Adjoint_g - \identity$ sends ${\mathfrak g}^j$ to
  %   ${\mathfrak g}^{j+1}$, for any $j \in {\mathbb Z}$, i.e., is homogeneous of degree
  %   one.\label{splittings30}
  % \item The only linear map $\varphi \colon {\mathfrak g} \rightarrow {\mathfrak g} $ that
  %   commutes with $\adjoint_e$ and such that $\varphi - \identity$ is homogeneous of degree
  %   one is the identity.\label{splittings40}
  \item For any $\epsilon_1, \epsilon_2 \in \epsilon + {\mathfrak g}^1$, we have
    $\Phi_{\epsilon_2} = \Adjoint_g\circ \Phi_{\epsilon_1}$, where $g \in G^1$ is the unique element for
    which $\epsilon_2 = \Adjoint_g \epsilon_1$. \label{splittings2_}
  \end{conditions}
\end{lemma}

\begin{proof}
  Note first that the filtration property ensures that the action of ${\mathfrak g}^1$ on
  ${\mathfrak g}^0 $ is filtration-preserving, and the corresponding action on
  $\graded({\mathfrak g}^0)$ is trivial. The same must be true for adjoint action of
  $G^1$, as $G^1$ is connected. In particular $e + {\mathfrak g}^1$ must be
  $G^1$-invariant, for any lift $e \in {\mathfrak g}^0$ of $E$. Suppose that the action of
  $G^1$ on $e + {\mathfrak g}^1$ is infinitesimally free. Then, by a dimension count, this
  action is infinitesimally transitive, and so transitive, since $G^1$ is
  connected. Infinitesimal freeness means the stabilizer subgroup $H$ for the action is
  discrete, so that $G^1 \rightarrow G^1/H \cong e + {\mathfrak g}^1$ is a covering
  space. Since $e + {\mathfrak g}^1$ is simply connected, $H$ is trivial and the remaining
  claims in \eqref{splittings1_} follow.

  To show that the action of $G^1$ on $e + {\mathfrak g}^1$ is infinitesimally free, for
  each $X \in {\mathfrak g}^1$, let $X^\dagger$ denote the infinitesimal generator of $X$,
  a vector field on $e + {\mathfrak g}^1$. We have $X^\dagger(e') = [X, e']$, for
  $e' \in e + {\mathfrak g}^1$. Supposing $X^\dagger(e') = 0$, write $X=\sum_{j>0} X_j$
  for some $X_j \in {\mathfrak g}_j$, where ${\mathfrak g}=\oplus_j {\mathfrak g}_j$ is
  the $E$-splitting corresponding to $e'$. Then we conclude that $\sum_{j>0}jX_j=0$, from
  which it follows that $X=0$.

  To prove \eqref{splittings2_}, observe that $\Phi_e$ is characterized among all
  isomorphisms $\graded({\mathfrak g}) \rightarrow {\mathfrak g}$ by the requirement
  \begin{equation*}
    [\Phi_e(X), e] = j \Phi_e(X)\quad
    \text{for all $X \in \graded_j({\mathfrak g}),\, j \in {\mathbb Z}$}.
  \end{equation*}
  Taking $e = e_1$ and applying $\Adjoint_g$ to both sides, we obtain
  $[\Adjoint_g \Phi_{e_1}X, \Adjoint_g e_1] = j\Adjoint_g e_1$, i.e.,
  \begin{equation*}
    [(\Adjoint_g \circ\, \Phi_{e_1})X, e_2] = je_2.
  \end{equation*}
  So, by the aforementioned characterization, we conclude
  $\Adjoint_g\circ\,\Phi_{e_1} = \Phi_{e_2}$.
\end{proof}

\section{Cartan connections from representations}%
\label{rut}
In this section we prove \ref{cartan}, restated here for convenience:

\begin{proposition}
  Suppose ${\mathcal G} $ is a Lie groupoid with a transitive Lie algebroid $A$. Then for
  every representation $\rho $ of ${\mathcal G} $ on $A$, extending the canonical
  representation of ${\mathcal G} $ on the anchor kernel, there exists a unique Cartan
  connection $D$ on ${\mathcal G} $ such that $\bar D = \rho $.
\end{proposition}

First note that the kernel of the canonical projection
$J^1 {\mathcal G} \rightarrow {\mathcal G} $ is a totally intransitive Lie groupoid whose
form we can show is independent of the particular integration ${\mathcal G} $ of $A$. This
kernel is denoted $\automorphism(TM, A)$ and described further in Section
\ref{deform}. For present purposes, the following properties suffice:

\begin{lemma}
  If the Lie algebroid $A$ of a Lie groupoid ${\mathcal G} $ is transitive, then:
  \begin{conditions}
  \item The adjoint representation of $J^1 {\mathcal G} $ on $A$ restricts to
    representation of $\automorphism(TM, A) \subset J^1 {\mathcal G} $ that is
    faithful.\label{kr1}
  \item For any $m \in M$ and each linear map $L \colon A|_m \rightarrow A|_m$,
    restricting to the identity on the anchor kernel, and whose corresponding factoring
    $T_mM \rightarrow T_mM$ through the anchor $\# \colon A \rightarrow TM$ is an
    isomorphism, there exists a unique $\psi \in \model|_m$ such that
    $\Adjoint_\psi = L$.\label{kr2}
  \end{conditions}
\end{lemma}
\begin{proof}[Proof of lemma]
  Part \eqref{kr1} follows from Proposition \ref{kernel}, while part \eqref{kr2} follows
  from \eqrefs{deformations}{opal2a} and transitivity.
\end{proof}
\begin{proof}[Proof of proposition]
  We seek a Lie groupoid morphism $S \colon {\mathcal G} \rightarrow J^1 {\mathcal G} $
  that is a right-inverse for the projection
  $\pi \colon J^1 {\mathcal G} \rightarrow {\mathcal G} $ and satisfies
  \begin{equation}
    \Adjoint_{S(g)} = \rho_g \qquad g \in {\mathcal G}.\label{kr3}
  \end{equation}
  To that end, let $\tilde S \colon U \rightarrow \pi^{-1}(U)$ be any smooth, local, right
inverse for $\pi $, defined on some open neighborhood $U \subset {\mathcal G}$ (not
necessarily respecting groupoid multiplication).  Then, for each arrow $g \in U$ beginning
at some $m \in M$, $L = \Adjoint_{\tilde S(g)}^{-1}\circ \rho_g $ satisfies the
condition in \eqref{kr2}, because $\rho$ extends the adjoint representation of
${\mathcal G} $ on the anchor kernel of $A$. Accordingly, there exists unique
$\psi(g) \in \model$ such that
$\Adjoint_{\psi(g)} =\Adjoint_{\tilde S(g)}^{-1}\circ \rho_g$, so that \eqref{kr3} holds
if we define $S(g) = \tilde S(g)\psi(g)$. It is not hard to see that
$S \colon U \rightarrow J^1 {\mathcal G} $ is smooth. Moreover, from the uniqueness, it
is clear that $S(g)$ does not actually depend on the choice of local right inverse
$\tilde S$, which means we can collate local definitions of $S$ as just described into a
global map $S \colon {\mathcal G} \rightarrow J^1 {\mathcal G} $. From \eqref{kr3}, we
will have $\Adjoint_{S(g)S(h)}=\Adjoint_{S(gh)}$ for all multipliable
$g, h \in {\mathcal G} $. Using \eqref{kr1} it is not hard to see that $S(gh)=S(g)S(h)$
must follow, because $S(g)S(h)$ and $S(gh)$ share a common image under the projection
$J^1 {\mathcal G} \rightarrow {\mathcal G}$, namely $gh$. A similar argument shows that
$S$ is uniquely determined by requirement \eqref{kr3}.

\end{proof}

\bibliography{dynamics2}

\end{document}



%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
